---
title: "Disentangling Labor Market Tightness from Posting Scale"
subtitle: "A Replication and Reanalysis of Andreadis et al. (AEA Papers and Proceedings, 2025)"
author:
  - name: Jacob Khaykin^[Solon High School, jacobkhaykin27@solonschools.net]
  - name: David Kane^[New College of Florida, dakane@ncf.edu]
bibliography: references.bib
csl: aea.csl
link-citations: true
nocite: '@*'
format:
  pdf:
    keep-tex: true
    number-sections: true
    documentclass: article
    geometry:
      - margin=1in
    include-in-header:
      - text: |
          \usepackage{url}
          \urlstyle{same}
          \def\UrlBreaks{\do/\do-\do.\do:}
          \usepackage{float}
          \usepackage{array}
          \usepackage{siunitx}
          \usepackage{dcolumn}
          \usepackage{tikz}
          \newcolumntype{d}[1]{D{.}{.}{#1}}
          % reset numbering after abstract
          \usepackage{etoolbox}
          \AtBeginEnvironment{abstract}{\setcounter{section}{0}}
          % Custom table row spacing
          \renewcommand{\arraystretch}{0.9}
          % Configure siunitx for modern versions (>=3)
          \sisetup{
            detect-all,
            input-symbols = (),
            input-signs = + -,
            table-align-text-pre = false,
            table-number-alignment = center,
            table-format = +1.4,
            group-digits = false,
            table-space-text-pre = ***,
            table-space-text-post = ***,
            mode = math
          }
---

```{r}
#| label: setup
#| include: false
# Load all required packages
library(tidyverse)
library(fixest)
library(modelsummary)
library(kableExtra)
library(scales)
library(ggplot2)
library(grid)
library(dplyr)
library(forcats)
library(dagitty)
```

*JEL: J24, O33, R11, C13*

*Keywords:* Artificial Intelligence, Regional Economics, Labor Markets

*Data Availability:* The R code and data to reproduce this replication are available in this repository.^[https://github.com/JacobKhay/Andreadis-Replication]

## Abstract {.unnumbered}

Andreadis et al. (2025) find labor-market tightness strongly predicts AI job intensity. We show this result is sensitive to specification choice because tightness (postings/unemployed) bundles two distinct channels: posting scale and unemployment. Using decomposition and alternative specifications, we find the tightness coefficient operates through both posting scale (beta approx 0.28, p < 0.001) and unemployment (beta approx 0.03, p < 0.05), with posting scale accounting for the larger share, clarifying how tight labor markets relate to AI adoption. These findings do not overturn the original paper's contributions, but they refine interpretation and suggest researchers should separately identify scale and slack effects when both involve shared components. We also compare alternative weighting schemes as a sensitivity check.

Declaration: There are no financial conflicts of interest to share.
\newpage

## Introduction

Artificial intelligence is reshaping labor demand and the geography of high-skill work, with county-level variation that matters for regional policy. Andreadis et al. (2025) provide one of the first systematic county-level accounts of AI job posting intensity and its growth over time, motivating place-based strategies and regional diagnostics.

Their headline results emphasize labor-market tightness and education. In the levels specification, tightness and bachelor's share are the largest positive correlates of AI job intensity. In the growth specification, STEM degree share and tightness are the strongest positive correlates. These patterns have been cited as evidence that AI posting intensity tends to be higher in counties with tighter labor markets and higher education.

We reproduce Tables 1 and 2 and then re-express tightness to separate posting scale from unemployment. Because tightness combines postings and unemployment, and AI intensity also scales with postings, the tightness coefficient combines two distinct economic channels: a scale channel (more postings overall) and a slack channel (lower unemployment). We decompose tightness into its components and estimate alternative specifications that separate these channels. This is not a critique of tightness as a concept, but a clarification that tightness bundles two channels that are economically meaningful but separable.

## Data

AKCLM combine Lightcast postings data with county-level demographics from the American Community Survey, innovation measures from patents and STEM degree shares, industry composition from CBP and QWI, and house price growth. All explanatory variables are lagged by one year. The main outcome is AI job intensity, and the growth outcome is the change in AI intensity between pooled 2017-2018 and 2022-2023 averages.

The key variables are defined as follows. The AI intensity outcome is:
$$AI_{it} = \frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} \times 100 \tag{1}$$
The tightness variable is:
$$Tightness_{it} = \frac{\text{Total postings}_{it}}{\text{Unemployed}_{it}} \tag{2}$$

Because tightness is postings per unemployed worker and AI intensity is AI postings per total postings, both measures embed posting volume. This motivates separating posting scale from unemployment when interpreting the tightness coefficient.

Because tightness combines postings and unemployment, and AI intensity also scales with postings, a tightness coefficient can reflect both posting scale and unemployment effects. We therefore treat tightness as a composite measure and explicitly separate its components in the analysis below.

## Replication

We reproduce Tables 1 and 2 using the authors' data.csv. Most coefficients and standard errors match the published tables exactly; one coefficient in Table 2 differs slightly, which likely reflects an undocumented preprocessing or default-setting difference. The replication tables use the authors' provided `data.csv`; Figure 1 uses an updated Lightcast extraction (`updated_lightcast_county.csv`) and Census shapefiles via `tigris` to reproduce the spatial visualization and is not required for the table replication. Connecticut has no county observations in the provided dataset, so it is shown as no data.

```{r}
#| label: tbl-table1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 1 from Andreadis et al. (2025) - The Correlates of the Share of Artificial Intelligence Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Load data
data_ai <- read_csv("data.csv") %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(ai_intensity = ai / nads)

# Prepare demographics
data_ai <- data_ai %>% 
  mutate(logincome = log(medhhincome), loghpi = log(hpi), logemp = log(pop_above18))

data_ai <- data_ai %>% 
  mutate(lads = log(1 + nads))

data_ai <- data_ai %>% 
  mutate(lads0 = log(nads))

# Log number of patents, inventors, etc.
data_ai <- data_ai %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai <- data_ai %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(pat_intensity = n_inventors / Employed, patai_intensity = ai_patents / n_patents) %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

# Industry structure
data_ai <- data_ai %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

data_ai <- data_ai %>% 
  mutate(information_intensity = replace_na(information_intensity, 0))

# Education variables
data_ai <- data_ai %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg),
    stemshare2 = (ustemdeg) / (udeg)
  )

data_ai <- data_ai %>%  
  mutate(stemshare = replace_na(stemshare, 0), stemshare2 = replace_na(stemshare2, 0))

# Labor market variables
data_ai <- data_ai %>%  
  mutate(tightness = nads / Unemployed)

data_ai <- data_ai %>%  
  mutate(hpi_ch = hpi_ch / 100)

# Z-scores - VERSION ROBUST with as.numeric()
data_ai_z <- data_ai %>%
  filter(emp != 0) %>%
  mutate(
    ai_raw = ai,         # Keep raw counts for count model
    nads_raw = nads,     # Keep raw postings for offset
    pop_raw = pop,        # Save raw population for weighting
    logpop_raw = logpop,  # Save raw log(pop) for weighting
    logemp_raw = logemp,  # Save raw log(employment) for weighting
    share_bac = as.numeric(scale(share_bac)),
    share_black = as.numeric(scale(share_black)),
    share_poverty = as.numeric(scale(share_poverty)),
    logpop = as.numeric(scale(logpop)),
    hpi_ch = as.numeric(scale(hpi_ch)),
    logincome = as.numeric(scale(logincome)),
    tightness = as.numeric(scale(tightness)),
    unrate = as.numeric(scale(unrate)),
    pat_intensity = as.numeric(scale(pat_intensity)),
    patai_intensity = as.numeric(scale(patai_intensity)),
    degshare = as.numeric(scale(degshare)),
    stemshare = as.numeric(scale(stemshare)),
    large_firms = as.numeric(scale(large_firms)),
    information_intensity = as.numeric(scale(information_intensity)),
    manuf_intensity = as.numeric(scale(manuf_intensity)),
    TurnOvrS = as.numeric(scale(TurnOvrS))
  ) %>%
  mutate(ai_intensity = ai_intensity * 100)

# Run regressions
est_demog_no <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_innovation_no <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_industry_no <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all_state_year <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway",
  weights = ~lads
)

# Extract model statistics
models <- list(est_demog_no, est_innovation_no, est_industry_no, est_all, est_all_state_year)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.5f", r2(.x, "r2")))

# Create table footer
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, state-year}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R^2", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels
labels <- c(
  "share_bac" = "Bachelor's share",
  "hpi_ch" = "House price growth",
  "tightness" = "Labor tightness",
  "pat_intensity" = "Patents per employee",
  "stemshare" = "STEM degrees share",
  "information_intensity" = "ICT sector intensity",
  "manuf_intensity" = "Manufacturing",
  "TurnOvrS" = "Turnover rate"
)

# Create note text
table_notes <- paste(
  "This table examines the demographic, innovation, and industry determinants",
  "of the share of artificial intelligence jobs across U.S. counties from 2014 to 2023.",
  "The dependent variable is AI job intensity, defined as the ratio of AI job postings",
  "to total job postings in each county-year, multiplied by 100 to express in percentage terms.",
  "AI job postings are identified from Lightcast data using skills and keywords associated",
  "with artificial intelligence. All explanatory variables are standardized as z-scores",
  "to ensure comparability across predictors. The sample comprises county-year observations",
  "covering approximately 3,100 U.S. counties annually over the ten-year period.",
  "All coefficients represent percentage point changes in AI job share for a one standard",
  "deviation increase in the explanatory variable. Models are estimated using ordinary least",
  "squares with county and year fixed effects (columns 1-4) or county and state-year fixed",
  "effects (column 5). Standard errors are clustered at the county level. All explanatory",
  "variables are lagged by one year."
)

# Create the table
modelsummary(
  list(
    "(1)" = est_demog_no,
    "(2)" = est_innovation_no,
    "(3)" = est_industry_no,
    "(4)" = est_all,
    "(5)" = est_all_state_year
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = fmt_decimal(4),
  align = "lddddd",
  notes = table_notes
)

est_all_t1 <- est_all
est_demog_t1 <- est_demog_no
est_innovation_t1 <- est_innovation_no
est_industry_t1 <- est_industry_no
est_all_t1_full <- est_all
est_all_state_year_t1 <- est_all_state_year
```

### Table 1

Table 1 shows tightness as the largest correlate in standardized magnitude, followed by bachelor's share. STEM share and patents per employee are positive but smaller, and manufacturing is reliably negative relative to ICT.

```{r}
#| label: tbl-table2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 2 from Andreadis et al. (2025) - The Correlates of the Percentage Point Change in the Share of AI Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Follow EXACT original code structure
data_ai_2017_2022 <- read_csv("data.csv") %>% 
  filter(Year == 2017 | Year == 2018 | Year == 2022 | Year == 2023) %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(new = 1 * (Year > 2020)) %>% 
  group_by(new, COUNTY_FIPS) %>% 
  mutate(ai = sum(ai), nads = sum(nads)) %>% 
  mutate(ai_intensity = ai / nads) %>% 
  filter(Year == 2017 | Year == 2022) %>% 
  group_by(COUNTY_FIPS) %>% 
  mutate(
    dai_intensity = ai_intensity - lag(ai_intensity),
    dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
  )

# Prepare demographics - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logincome = log(medhhincome),
    loghpi = log(hpi),
    logemp = log(pop_above18),
    logim = log(1)  # Note: original has logim=log(immigration) but no immigration variable
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    unrate14 = lag(unrate, 1),
    logincome14 = lag(logincome, 1),
    loghpi14 = lag(loghpi, 1),
    share_bac14 = lag(share_bac, 1),
    share_black14 = lag(share_black, 1),
    share_poverty14 = lag(share_poverty, 1),
    logemp14 = lag(logemp, 1),
    logim14 = lag(logim, 1),
    medage14 = lag(medage, 1),
    median_rent14 = lag(median_rent, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    gincome = logincome - lag(logincome, 1),
    ghpi = loghpi - lag(loghpi, 1),
    gemp = logemp - lag(logemp, 1),
    gim = logim - lag(logim, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    dunrate = unrate - lag(unrate, 1),
    dshare_bac = share_bac - lag(share_bac, 1),
    dshare_black = share_black - lag(share_black, 1),
    dmedage14 = medage - lag(medage, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads = log(1 + nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads0 = log(nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    information_intensity = manuf_emp / emp  # Note: this overwrites previous line in original
  )

# Log number of patents, inventors, etc. - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

# Duplicate line in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

# Another duplicate section in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_inventors14 = lag(logn_inventors, 1),
    logai_inventors14 = lag(logai_inventors, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(stemshare = replace_na(stemshare, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(stemshare14 = lag(stemshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(degshare14 = lag(degshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(tightness = nads / Unemployed)

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(tightness14 = lag(tightness, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(hpi_ch14 = lag(hpi_ch, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logpop14 = lag(logpop, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logincome14 = lag(logincome, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(gpop = (logpop - lag(logpop, 1)) / 5)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch = hpi_ch / 100)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch14 = hpi_ch14 / 100)

# Industry structure
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms14 = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14 = lag(manuf_intensity, 1),
    TurnOvrS14 = lag(TurnOvrS, 1)
  )

# Z-scores - EXACT as original
data_ai_l_z <- data_ai_2017_2022 %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)

# Run FULL models with ALL variables (not condensed)
est_demog_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_innovation_no <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_industry_no <- fixest::feols(
  "dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_large <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

# Save as-provided replication models for Appendix A
est_demog_t2_as <- est_demog_no
est_innovation_t2_as <- est_innovation_no
est_industry_t2_as <- est_industry_no
est_all_t2_as <- est_all
est_all_large_t2_as <- est_all_large

# --- Cleaned replication (main table) ---
data_ai_2017_2022_clean <- read_csv("data.csv") %>% 
  filter(Year %in% c(2017, 2018, 2022, 2023)) %>% 
  mutate(new = 1 * (Year > 2020)) %>% 
  group_by(new, COUNTY_FIPS) %>% 
  mutate(ai = sum(ai), nads = sum(nads)) %>% 
  mutate(ai_intensity = ai / nads) %>% 
  filter(Year %in% c(2017, 2022)) %>% 
  group_by(COUNTY_FIPS) %>% 
  mutate(
    dai_intensity = ai_intensity - lag(ai_intensity),
    dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
  ) %>%
  ungroup() %>%
  mutate(
    logincome = log(medhhincome),
    loghpi = log(hpi),
    logemp = log(pop_above18),
    logpop = log(pop),
    unrate14 = lag(unrate, 1),
    logincome14 = lag(logincome, 1),
    loghpi14 = lag(loghpi, 1),
    share_bac14 = lag(share_bac, 1),
    share_black14 = lag(share_black, 1),
    share_poverty14 = lag(share_poverty, 1),
    logpop14 = lag(logpop, 1),
    hpi_ch14 = lag(hpi_ch, 1),
    gpop = (logpop - lag(logpop, 1)) / 5,
    lads = log(1 + nads),
    lads14 = lag(lads, 1)
  ) %>%
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents,
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1),
    patai_intensity = replace_na(patai_intensity, 0)
  ) %>%
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg),
    stemshare = replace_na(stemshare, 0),
    degshare14 = lag(degshare, 1),
    stemshare14 = lag(stemshare, 1)
  ) %>%
  mutate(
    large_firms = 1 - (small + medium) / est,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp,
    TurnOvrS14 = lag(TurnOvrS, 1),
    large_firms14 = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14 = lag(manuf_intensity, 1)
  ) %>%
  mutate(
    tightness = nads / Unemployed,
    tightness14 = lag(tightness, 1),
    hpi_ch = hpi_ch / 100,
    hpi_ch14 = hpi_ch14 / 100
  )

data_ai_l_z_clean <- data_ai_2017_2022_clean %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)

est_demog_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_innovation_clean <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_industry_clean <- fixest::feols(
  "dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_large_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

# Extract model statistics (cleaned)
models <- list(est_demog_clean, est_innovation_clean, est_industry_clean, est_all_clean, est_all_large_clean)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.4f", r2(.x, "r2")))

# Create extra rows for table footer - add spacing before values to shift right
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}State}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R^2", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels - condensed to only the 8 key variables
labels <- c(
  "share_bac14" = "Bachelors Share",
  "logincome14" = "Income, Log", 
  "tightness14" = "Tightness",
  "stemshare14" = "Stem Degrees' share",
  "large_firms14" = "Large Firms",
  "information_intensity14" = "ICT sector Intensity",
  "manuf_intensity14" = "Manufacturing",
  "TurnOvrS14" = "Turnover Rate"
)

# Create the table with modelsummary - use d for decimal alignment
modelsummary(
  list(
    "(1)" = est_demog_clean,
    "(2)" = est_innovation_clean,
    "(3)" = est_industry_clean,
    "(4)" = est_all_clean,
    "(5)" = est_all_large_clean
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = 4,
  align = "lddddd",
  notes = "This table examines the demographic, innovation, and industry determinants of the percentage point change in AI job share between two pooled periods: 2017-2018 and 2022-2023. The dependent variable measures the change in AI intensity (multiplied by 100 to express in percentage points), capturing dynamic shifts rather than static levels. All explanatory variables are measured in 2017 (before the growth period) and standardized as z-scores. The sample includes 2,473 counties with sufficient data across both periods. All coefficients represent percentage point changes in the growth of AI job share for a one standard deviation increase in the 2017 explanatory variable. Models are estimated using ordinary least squares with no fixed effects (columns 1-4) or state fixed effects (column 5). Standard errors are clustered at the county level. "
)

est_all_t2 <- est_all_clean
est_demog_t2 <- est_demog_clean
est_innovation_t2 <- est_innovation_clean
est_industry_t2 <- est_industry_clean
est_all_t2_full <- est_all_clean
est_all_large_t2 <- est_all_large_clean
```


### Table 2

In the growth specification, tightness and STEM degree share are among the largest positive correlates, while several industry variables are small and imprecise. Table 2 reports a cleaned replication that removes redundant steps and intermediate overwrites while preserving the published specification and sample construction.

```{r}
#| label: fig-map
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "Spatial heterogeneity in AI job share across US counties. Panel A shows the average share of AI-related job postings from 2014 to 2023. Panel B shows percentage-point changes between 2018 and 2023. Connecticut has no county observations in the provided dataset, so it is shown as no data."
#| fig-cap-location: bottom
#| fig-pos: "H"
#| fig-width: 18
#| fig-height: 9

library(tidyverse)
library(sf)
library(tigris)
library(patchwork)

# Read the updated Lightcast data
data <- read_csv("updated_lightcast_county.csv") %>%
  rename(COUNTY_FIPS = COUNTY_FIPS,
         Year = YEAR_POSTED,
         ai = `AI Postings`,
         nads = `Total Postings`)

# Remove Connecticut state-level data (FIPS 9999) and Planning Region entries
data_complete <- data %>%
  filter(COUNTY_FIPS != 9999) %>%
  filter(!(COUNTY_FIPS >= 9110 & COUNTY_FIPS <= 9190))

# ---- PANEL A ----
data_levels <- data_complete %>%
  mutate(aiInt = if_else(nads > 0, ai/nads, NA_real_)) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(aiInt = mean(aiInt, na.rm = TRUE), .groups = "drop")

# ---- PANEL B ----
data_for_change <- data_complete %>%
  mutate(
    year_group = case_when(
      Year %in% c(2017, 2018) ~ "2017-2018",
      Year %in% c(2022, 2023) ~ "2022-2023",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(year_group))

data_pooled <- data_for_change %>%
  group_by(COUNTY_FIPS, year_group) %>%
  summarise(
    ai_sum = sum(ai, na.rm = TRUE),
    nads_sum = sum(nads, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(aiInt = if_else(nads_sum > 0, ai_sum / nads_sum, NA_real_))

data_ch <- data_pooled %>%
  pivot_wider(
    id_cols = COUNTY_FIPS,
    names_from = year_group,
    values_from = aiInt
  ) %>%
  mutate(aiIntch = `2022-2023` - `2017-2018`) %>%
  select(COUNTY_FIPS, aiIntch)

# ---- FIPS FORMATTING ----
merged_data_lev <- data_levels %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

merged_data_ch <- data_ch %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

# ---- PANEL A BINNING ----
merged_data_lev <- merged_data_lev %>%
  mutate(ai_share = aiInt * 100) %>%
  mutate(caseai = case_when(
    ai_share >= 0 & ai_share < 0.06 ~ 1,
    ai_share > 0.06 & ai_share < 0.14 ~ 2,
    ai_share > 0.14 & ai_share < 0.23 ~ 3,
    ai_share > 0.23 & ai_share < 0.37 ~ 4,
    ai_share > 0.37 & ai_share < 0.7 ~ 5,
    ai_share > 0.7 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- PANEL B BINNING ----
merged_data_ch <- merged_data_ch %>%
  mutate(change_in_share = aiIntch * 100) %>%
  mutate(caseaich = case_when(
    change_in_share < -0.12 ~ 1,
    change_in_share > -0.12 & change_in_share <= 0 ~ 2,
    change_in_share > 0 & change_in_share < 0.09 ~ 3,
    change_in_share > 0.09 & change_in_share < 0.24 ~ 4,
    change_in_share > 0.24 & change_in_share < 0.57 ~ 5,
    change_in_share > 0.57 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- COUNTY SHAPEFILES ----
options(tigris_use_cache = TRUE)
counties <- suppressMessages(
  tigris::counties(cb = TRUE, year = 2020, class = "sf")
) %>%
  mutate(COUNTY_FIPS = GEOID) %>%
  filter(!str_starts(COUNTY_FIPS, "72")) %>%
  st_transform(crs = 4326)

# ---- PANEL A MAP JOIN ----
map_data_a <- counties %>%
  left_join(merged_data_lev, by = c("COUNTY_FIPS" = "fips")) %>%
  tigris::shift_geometry()

# ---- PANEL B MAP JOIN (with Alaska color fix) ----
# Fix Alaska merge issue before shifting
ak_data <- merged_data_ch %>%
  filter(str_starts(fips, "02")) %>%
  distinct(fips, .keep_all = TRUE)

map_data_b <- counties %>%
  left_join(merged_data_ch, by = c("COUNTY_FIPS" = "fips"))

map_data_b[map_data_b$STATEFP == "02", names(ak_data)[-1]] <-
  ak_data[match(map_data_b$COUNTY_FIPS[map_data_b$STATEFP == "02"], ak_data$fips),
          names(ak_data)[-1]]

# Shift after joining (fixes Alaska colors)
map_data_b <- tigris::shift_geometry(map_data_b)

# ---- LABELS AND COLORS ----
map_data_a <- map_data_a %>%
  mutate(
    avg_bin = case_when(
      caseai == 1 ~ "0 - 0.06",
      caseai == 2 ~ "0.06 - 0.14",
      caseai == 3 ~ "0.14 - 0.23",
      caseai == 4 ~ "0.23 - 0.37",
      caseai == 5 ~ "0.37 - 0.71",
      caseai == 6 ~ "0.71 - 10",
      TRUE ~ "No data"
    )
  )

map_data_b <- map_data_b %>%
  mutate(
    chg_bin = case_when(
      caseaich == 1 ~ "−5.56 - −0.12",
      caseaich == 2 ~ "−0.12 - 0",
      caseaich == 3 ~ "0 - 0.09",
      caseaich == 4 ~ "0.09 - 0.24",
      caseaich == 5 ~ "0.24 - 0.57",
      caseaich == 6 ~ "0.57 - 12.35",
      TRUE ~ "No data"
    )
  )

levels_avg_display <- c("0.71 - 10", "0.37 - 0.71", "0.23 - 0.37",
                        "0.14 - 0.23", "0.06 - 0.14", "0 - 0.06", "No data")
levels_chg_display <- c("0.57 - 12.35", "0.24 - 0.57", "0.09 - 0.24",
                        "0 - 0.09", "−0.12 - 0", "−5.56 - −0.12", "No data")

colors_avg_display <- c("#800026", "#e31a1c", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")
colors_chg_display <- c("#800026", "#fc4e2a", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")

map_data_a$avg_bin <- factor(map_data_a$avg_bin, levels = levels_avg_display)
map_data_b$chg_bin <- factor(map_data_b$chg_bin, levels = levels_chg_display)

# ---- THEME ----
map_theme <- theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 20, margin = margin(t = 3, b = 3, l = 1, r = 1)),
    legend.title = element_blank(),
    legend.key.width = unit(1.8, "cm"),
    legend.key.height = unit(0.6, "cm"),
    legend.spacing.x = unit(0.2, "cm"),
    legend.spacing.y = unit(0.1, "cm"),
    legend.margin = margin(t = 10, b = 5),
    legend.key = element_rect(color = "black", size = 0.5),
    plot.margin = margin(10, 10, 25, 10, "pt"),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.border = element_rect(color = "black", fill = NA, size = 0.5)
  )

# ---- PLOTS ----
p1 <- ggplot(map_data_a) +
  geom_sf(aes(fill = avg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_avg_display, levels_avg_display),
                    breaks = levels_avg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_a), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel A. Percent share of AI jobs (2014-2023 average)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

p2 <- ggplot(map_data_b) +
  geom_sf(aes(fill = chg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_chg_display, levels_chg_display),
                    breaks = levels_chg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_b), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel B. Percentage-point change in AI share (2018-2023)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

# ---- FINAL COMBINED PLOT ----
final_plot <- (p1 | p2) +
  plot_layout(widths = c(1, 1)) &
  theme(plot.background = element_rect(fill = "white", color = NA))

# Add overall title
final_plot <- final_plot +
  plot_annotation(
    title = "Figure 1: Replication of Andreadis et al. (2025) - Spatial Heterogeneity in the Share of and Change of AI Jobs",
    theme = theme(plot.title = element_text(size = 26, hjust = 0.5, margin = margin(b = 15)))
  )

final_plot
```

## Tightness as a Composite Measure

Tightness, defined as postings per unemployed worker, bundles two channels: posting scale and unemployment. Because AI intensity is also constructed using total postings, the tightness coefficient captures both a scale effect (more postings overall) and a slack effect (lower unemployment). The analysis below separates these channels by decomposing tightness into its components and estimating alternative specifications that isolate posting scale from unemployment.

### Reanalysis Excluding Tightness (Table 1, Column 4)

```{r}
#| label: tbl-no-tightness-t1
#| echo: false
#| warning: false
#| message: false
est_all_t1 <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
est_all_t1_no_tightness <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
vars_core_t1 <- c("share_bac", "hpi_ch", "pat_intensity", "stemshare", "information_intensity", "manuf_intensity", "TurnOvrS")
labels_core_t1 <- c("Bachelor's share", "House price growth", "Patents per employee", "STEM degrees share", "ICT sector intensity", "Manufacturing intensity", "Turnover rate")
no_tight_tbl_t1 <- data.frame(
  Variable = labels_core_t1,
  `Baseline (replicated)` = sprintf("%.4f (%.4f)", coef(est_all_t1)[vars_core_t1], se(est_all_t1)[vars_core_t1]),
  `No Tightness` = sprintf("%.4f (%.4f)", coef(est_all_t1_no_tightness)[vars_core_t1], se(est_all_t1_no_tightness)[vars_core_t1]),
  `% Change` = sprintf("%+.0f%%", (coef(est_all_t1_no_tightness)[vars_core_t1] - coef(est_all_t1)[vars_core_t1]) / coef(est_all_t1)[vars_core_t1] * 100)
)
knitr::kable(no_tight_tbl_t1, align = "lccc", col.names = c("Variable", "Baseline (replicated)", "No Tightness", "% Change"))
```

*Notes:* This table compares Table 1's baseline specification (column 4) to the same model estimated without labor-market tightness.

### Reanalysis Excluding Tightness (Table 2, Column 4)

```{r}
#| label: prep-t2-data
#| echo: false
#| warning: false
#| message: false
if (!exists("data_ai_l_z")) {
  data_ai_2017_2022 <- read_csv("data.csv") %>% 
    filter(Year == 2017 | Year == 2018 | Year == 2022 | Year == 2023) %>% 
    mutate(state_year = paste0(state, Year)) %>% 
    mutate(new = 1 * (Year > 2020)) %>% 
    group_by(new, COUNTY_FIPS) %>% 
    mutate(ai = sum(ai), nads = sum(nads)) %>% 
    mutate(ai_intensity = ai / nads) %>% 
    filter(Year == 2017 | Year == 2022) %>% 
    group_by(COUNTY_FIPS) %>% 
    mutate(
      dai_intensity = ai_intensity - lag(ai_intensity),
      dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logincome = log(medhhincome),
      loghpi = log(hpi),
      logemp = log(pop_above18),
      logim = log(1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      unrate14 = lag(unrate, 1),
      logincome14 = lag(logincome, 1),
      loghpi14 = lag(loghpi, 1),
      share_bac14 = lag(share_bac, 1),
      share_black14 = lag(share_black, 1),
      share_poverty14 = lag(share_poverty, 1),
      logemp14 = lag(logemp, 1),
      logim14 = lag(logim, 1),
      medage14 = lag(medage, 1),
      median_rent14 = lag(median_rent, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      gincome = logincome - lag(logincome, 1),
      ghpi = loghpi - lag(loghpi, 1),
      gemp = logemp - lag(logemp, 1),
      gim = logim - lag(logim, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      dunrate = unrate - lag(unrate, 1),
      dshare_bac = share_bac - lag(share_bac, 1),
      dshare_black = share_black - lag(share_black, 1),
      dmedage14 = medage - lag(medage, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(lads = log(1 + nads))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(lads0 = log(nads))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      large_firms = 1 - (small + medium) / est,
      management_intensity = management_emp / emp,
      information_intensity = information_emp / emp,
      information_intensity = manuf_emp / emp
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logemp = log(Employed)) %>% 
    mutate(logpop = log(pop))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logn_patents = log(1 + n_patents),
      logn_inventors = log(1 + n_inventors),
      logai_patents = log(1 + ai_patents),
      logai_inventors = log(1 + ai_inventors)
    ) %>%
    mutate(
      pat_intensity = n_inventors / Employed,
      patai_intensity = ai_patents / n_patents
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      small_firms = small / est,
      large_firms = 1 - (small + medium) / est,
      management_intensity = management_emp / emp,
      information_intensity = information_emp / emp,
      manuf_intensity = manuf_emp / emp
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity = n_inventors / Employed,
      patai_intensity = ai_patents / n_patents
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(patai_intensity = replace_na(patai_intensity, 0))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1),
      lads14 = lag(lads, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logn_inventors14 = lag(logn_inventors, 1),
      logai_inventors14 = lag(logai_inventors, 1),
      lads14 = lag(lads, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    ungroup() %>%  
    mutate(
      degshare = (udeg + mdeg) / Employed,
      stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(stemshare = replace_na(stemshare, 0))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(stemshare14 = lag(stemshare, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(degshare14 = lag(degshare, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(tightness = nads / Unemployed)

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(tightness14 = lag(tightness, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(hpi_ch14 = lag(hpi_ch, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logpop14 = lag(logpop, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logincome14 = lag(logincome, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(gpop = (logpop - lag(logpop, 1)) / 5)

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(hpi_ch = hpi_ch / 100)

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(hpi_ch14 = hpi_ch14 / 100)

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      large_firms14 = lag(large_firms, 1),
      information_intensity14 = lag(information_intensity, 1),
      manuf_intensity14 = lag(manuf_intensity, 1),
      TurnOvrS14 = lag(TurnOvrS, 1)
    )

data_ai_l_z <- data_ai_2017_2022 %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)
}
```

```{r}
#| label: tbl-no-tightness-t2
#| echo: false
#| warning: false
#| message: false
data_t2_z_nt <- data_ai_l_z %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2 <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
vars_core_t2 <- c("share_bac14", "hpi_ch14", "pat_intensity14", "stemshare14", "information_intensity14", "manuf_intensity14", "TurnOvrS14")
labels_core_t2 <- c("Bachelor's share", "House price growth", "Patents per employee", "STEM degrees share", "ICT sector intensity", "Manufacturing intensity", "Turnover rate")
no_tight_tbl_t2 <- data.frame(
  Variable = labels_core_t2,
  `Baseline (replicated)` = sprintf("%.4f (%.4f)", coef(est_all_t2)[vars_core_t2], se(est_all_t2)[vars_core_t2]),
  `No Tightness` = sprintf("%.4f (%.4f)", coef(est_all_t2_no_tightness)[vars_core_t2], se(est_all_t2_no_tightness)[vars_core_t2]),
  `% Change` = sprintf("%+.0f%%", (coef(est_all_t2_no_tightness)[vars_core_t2] - coef(est_all_t2)[vars_core_t2]) / coef(est_all_t2)[vars_core_t2] * 100)
)
knitr::kable(no_tight_tbl_t2, align = "lccc", col.names = c("Variable", "Baseline (replicated)", "No Tightness", "% Change"))
```

*Notes:* This table compares Table 2's baseline specification (column 4) to the same model estimated without labor-market tightness.

### Decomposing Tightness: Log(Postings) and Log(Unemployment)

As a direct check on the composite tightness measure, we replace tightness $T/U$ with its components, \mbox{$\\log(T)$} and \mbox{$\\log(U)$}, in the levels specification. This tests the relative contributions of posting scale and unemployment to the composite tightness measure. Both components remain significant, indicating both channels are operative.

```{r}
#| label: tbl-tightness-decomp
#| echo: false
#| warning: false
#| message: false
data_ai_decomp <- data_ai_z %>%
  mutate(
    log_nads = as.numeric(scale(log(pmax(nads, 1)))),
    log_unemp = as.numeric(scale(log(pmax(Unemployed, 1))))
  )

est_all_t1_decomp <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + log_nads + log_unemp + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_decomp,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

decomp_tbl <- data.frame(
  Term = c("Tightness (baseline)", "Log total postings", "Log unemployment"),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_nads"], se(est_all_t1_decomp)["log_nads"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_unemp"], se(est_all_t1_decomp)["log_unemp"])
  )
)
knitr::kable(decomp_tbl, align = "lc", col.names = c("Term", "Estimate"))
```

*Notes:* Decomposition uses the same controls and fixed effects as Table 1, column 4.

### Empirical Decomposition: Residualized Tightness (Levels)

As an alternative specification, we residualize tightness on \mbox{$\\log(T)$} and \mbox{$\\log(U)$} using the same fixed effects and weights, and then re-estimate the baseline model with the residualized tightness. This keeps the original controls and weighting while removing the variation in tightness that is aligned with postings scale. The interpretation is limited because tightness is mechanically constructed from its components; the residual captures nonlinear variation not explained by the log components.

```{r}
#| label: tbl-tightness-resid
#| echo: false
#| warning: false
#| message: false
tight_resid_model <- fixest::feols(
  tightness ~ log_nads + log_unemp | Year + COUNTY_FIPS,
  data_ai_decomp,
  weights = ~lads
)
used_idx <- fixest::obs(tight_resid_model)
data_ai_decomp_used <- data_ai_decomp
data_ai_decomp_used$tightness_resid <- NA_real_
data_ai_decomp_used$tightness_resid[used_idx] <- as.numeric(resid(tight_resid_model))

est_all_t1_resid <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness_resid + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_decomp_used,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

resid_tbl <- data.frame(
  Term = c("Tightness (baseline)", "Tightness (residualized)"),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_resid)["tightness_resid"], se(est_all_t1_resid)["tightness_resid"])
  )
)
knitr::kable(resid_tbl, align = "lc", col.names = c("Term", "Estimate"))
```

*Notes:* Residualization uses the same fixed effects and posting weights as Table 1, column 4.

To quantify how much tightness is driven by postings scale in the empirical specification, we compute the within-FE R^2 from the residualization regression above. In this sample, log(postings) and log(unemployment) explain `r sprintf("%.1f%%", 100 * r2(tight_resid_model, "r2"))` of tightness variation.

### Tightness Horse Race (Levels)

```{r}
#| label: tbl-tightness-horserace
#| echo: false
#| warning: false
#| message: false
horse_tbl <- data.frame(
  Specification = c(
    "Baseline: Tightness (T/U)",
    "Decomposition: log(T)",
    "Decomposition: log(U)",
    "Residualized Tightness",
    "Unemployment Rate Proxy",
    "Poisson Offset Model"
  ),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_nads"], se(est_all_t1_decomp)["log_nads"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_unemp"], se(est_all_t1_decomp)["log_unemp"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_resid)["tightness_resid"], se(est_all_t1_resid)["tightness_resid"]),
    {
      if (!exists("est_all_t1_unrate")) {
        est_all_t1_unrate <- fixest::feols(
          "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + unrate + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
          data_ai_z,
          cluster = "COUNTY_FIPS",
          weights = ~lads
        )
      }
      sprintf("%.4f (%.4f)", coef(est_all_t1_unrate)["unrate"], se(est_all_t1_unrate)["unrate"])
    },
    {
      if (!exists("est_all_t1_pois")) {
        data_ai_count <- data_ai_z %>% filter(nads_raw > 0)
        est_all_t1_pois <- fixest::fepois(
          ai_raw ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS,
          data = data_ai_count,
          offset = log(data_ai_count$nads_raw),
          cluster = "COUNTY_FIPS"
        )
      }
      sprintf("%.4f (%.4f)", coef(est_all_t1_pois)["tightness"], se(est_all_t1_pois)["tightness"])
    }
  )
)
knitr::kable(horse_tbl, align = "lc", col.names = c("Specification", "Estimate"))
```

*Notes:* All specifications use the full set of controls and county/year fixed effects. The Poisson model uses a log(total postings) offset.

### Count Model with Offset (Levels)

As a second alternative, we model AI postings counts with an offset for total postings. This specification avoids ratio outcomes but imposes a unit elasticity on posting scale through the offset, whereas the OLS decomposition estimates that elasticity freely. It is therefore a complementary robustness check rather than a direct substitute for the baseline specification.

```{r}
#| label: tbl-offset-poisson
#| echo: false
#| warning: false
#| message: false
data_ai_count <- data_ai_z %>% filter(nads_raw > 0)

est_all_t1_pois <- fixest::fepois(
  ai_raw ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS,
  data = data_ai_count,
  offset = log(data_ai_count$nads_raw),
  cluster = "COUNTY_FIPS"
)

offset_tbl <- data.frame(
  Model = c("OLS ratio (Table 1, Col. 4)", "Poisson w/ offset"),
  Tightness = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_pois)["tightness"], se(est_all_t1_pois)["tightness"])
  )
)
knitr::kable(offset_tbl, align = "lc")
```

*Notes:* Offset is \mbox{$\\log(T)$}, where $T$ is total postings.

### Alternative Tightness Proxy: Unemployment Rate

As a practical alternative that separates unemployment from postings, we replace tightness with the unemployment rate. This keeps the labor-market dimension while removing the direct posting-scale component.

```{r}
#| label: tbl-unrate-proxy
#| echo: false
#| warning: false
#| message: false
est_all_t1_unrate <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + unrate + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
est_all_t2_unrate <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + unrate14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
proxy_tbl <- data.frame(
  Outcome = c("Table 1 (levels, col. 4)", "Table 2 (growth, col. 4)"),
  `Tightness` = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t2)["tightness14"], se(est_all_t2)["tightness14"])
  ),
  `Unemployment rate` = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1_unrate)["unrate"], se(est_all_t1_unrate)["unrate"]),
    sprintf("%.4f (%.4f)", coef(est_all_t2_unrate)["unrate14"], se(est_all_t2_unrate)["unrate14"])
  )
)
knitr::kable(proxy_tbl, align = "lcc")
```

*Notes:* Tightness and unemployment rate are both standardized. The unemployment-rate proxy avoids the shared denominator with AI intensity while retaining a labor-market signal.

## Economic Interpretation

The decomposition reveals two distinct channels through which labor markets relate to AI adoption:

Scale channel (beta approx 0.28). Counties with more job postings overall have higher AI intensity. This can reflect larger, more dynamic labor markets, greater firm entry and expansion, more competitive recruiting environments, and network effects in technology adoption.

Slack channel (beta approx 0.03). Conditional on posting volume, lower unemployment is associated with modestly higher AI intensity. This can reflect competition for workers, wage pressure that encourages productivity-enhancing technology, or reduced labor supply constraints.

The baseline tightness coefficient (beta = 0.276) approximately equals the sum of the scale and slack components, confirming that both channels are captured in the original specification.

The original tightness specification captures both channels simultaneously, which is economically sensible. Our decomposition clarifies their relative magnitudes rather than suggesting one specification is superior to the other.

This decomposition connects to the Beveridge curve literature, which relates vacancies to unemployment as a summary of labor market equilibrium [@beveridge1944; @diamond2015]. In that framework, movements along the curve reflect cyclical changes in labor demand, while shifts in the curve reflect changes in matching efficiency or market composition. Our results suggest AI adoption is more strongly associated with the level of posting activity (the level of the curve) than with unemployment conditional on posting volume (the position along the curve). This pattern is consistent with AI adoption reflecting structural market characteristics rather than cyclical labor market conditions.

## Discussion: When Does Decomposition Matter

Decomposing composite measures like tightness is most useful in three contexts:

Policy targeting. If interventions affect posting volume differently than unemployment (for example, firm entry incentives versus job training), decomposition reveals which channel is more responsive.

Mechanism testing. If theory predicts unemployment should matter more than posting volume (or vice versa), decomposition provides a direct test of the mechanism.

Heterogeneity analysis. The relative importance of scale versus slack may vary across regions or time periods. Decomposition enables those comparisons.

In the Andreadis et al. context, the decomposition clarifies that posting volume is the dominant channel, which likely reflects underlying market size and dynamism. This refines interpretation without overturning the original finding that tight labor markets predict AI adoption.

## Conclusion

Andreadis et al. (2025) make an important contribution documenting AI job heterogeneity across U.S. counties. Our reanalysis clarifies the interpretation of their key finding: labor market tightness predicts AI intensity through both posting scale (beta approx 0.28) and unemployment (beta approx 0.03), with posting scale having a larger magnitude. When we separate these channels using decomposition, residualization, and an offset-count model, the relative contributions of scale and slack become explicit.

This distinction matters for both methodology and policy. Methodologically, researchers should be cautious when correlates and outcomes share components--not because results are invalid, but because coefficients can combine multiple mechanisms. Decomposition can separate these channels and sharpen interpretation. For policy, our results suggest AI adoption tracks posting volume more than labor-market slack, while both channels remain operative. This implies that policies promoting market dynamism and firm activity may be as important as those targeting unemployment alone.

We do not challenge the original paper's conclusion that labor markets matter for AI adoption--we show how they matter. Future work can explore why posting volume varies across counties and whether unemployment plays a stronger role in specific contexts. Additionally, testing whether the scale-versus-slack decomposition varies across industries, firm sizes, or urban-rural divides could reveal heterogeneous mechanisms driving spatial AI diffusion.


## Bibliography {.unnumbered}
::: {#refs}
:::

\newpage

## Appendix A: Weighting Sensitivity {.unnumbered}

### Log-Population Weights (Table 1, Column 4) {.unnumbered}

This appendix reports a sensitivity check that is independent of the tightness decomposition. We test whether remaining associations are sensitive to alternative aggregation schemes by comparing unweighted, population-weighted, and log-population-weighted estimates. Population weights correspond to a person-weighted relationship; log(population) is an intermediate, concave reweighting that tilts toward larger counties without letting a few very large counties dominate. This provides a transparent sensitivity check relative to the original posting-weighted estimand. Coefficient magnitudes attenuate on average (see Figure 4).

```{r}
#| label: tbl-weights-robust
#| echo: false
#| warning: false
#| message: false
est_all_t1_no_tightness_unw <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS"
)
est_all_t1_no_tightness_pop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~pop_raw
)
est_all_t1_no_tightness_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

data_t2_logpop <- data_ai_2017_2022 %>%
  filter(emp != 0) %>%
  drop_na(share_bac14) %>%
  mutate(
    logpop_raw = logpop14,
    share_bac14 = scale(share_bac14),
    share_black14 = scale(share_black14),
    share_poverty14 = scale(share_poverty14),
    logpop14 = scale(logpop14),
    hpi_ch14 = scale(hpi_ch14),
    logincome14 = scale(logincome14),
    tightness14 = scale(tightness14),
    pat_intensity14 = scale(pat_intensity14),
    patai_intensity14 = scale(patai_intensity14),
    degshare14 = scale(degshare14),
    stemshare14 = scale(stemshare14),
    large_firms14 = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14 = scale(manuf_intensity14),
    TurnOvrS14 = scale(TurnOvrS14),
    unrate14 = scale(unrate14),
    pop_raw = exp(logpop_raw)
  ) %>%
  mutate(dai_intensity9 = dai_intensity9 * 100) %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2_no_tightness_unw <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS"
)
est_all_t2_no_tightness_pop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~pop_raw
)
est_all_t2_no_tightness_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

med_change <- function(est_ref, est_new, vars) {
  median(abs((coef(est_new)[vars] - coef(est_ref)[vars]) / coef(est_ref)[vars]) * 100, na.rm = TRUE)
}

weights_tbl <- data.frame(
  Scheme = c("Unweighted", "Population-weighted", "Log-population weighted"),
  `Table 1 median abs change` = sprintf(
    "%.0f%%",
    c(
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_unw, vars_core_t1),
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_pop, vars_core_t1),
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_logpop, vars_core_t1)
    )
  ),
  `Table 2 median abs change` = sprintf(
    "%.0f%%",
    c(
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_unw, vars_core_t2),
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_pop, vars_core_t2),
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_logpop, vars_core_t2)
    )
  ),
  check.names = FALSE
)
knitr::kable(weights_tbl, align = "lcc")
```

*Notes:* Median absolute changes are computed relative to the no-tightness baseline with log(1+ads) weights.

```{r}
#| label: fig-logpop-compact-t1
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Coefficient sensitivity after removing tightness using log-population weights (Table 1, Col. 4)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 6
#| fig-height: 4
est_all_t1_no_tightness_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)
plot_df_t1 <- bind_rows(
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1)[vars_core_t1], SE = se(est_all_t1)[vars_core_t1], Scheme = "Original"),
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1_no_tightness)[vars_core_t1], SE = se(est_all_t1_no_tightness)[vars_core_t1], Scheme = "No Tightness"),
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1_no_tightness_logpop)[vars_core_t1], SE = se(est_all_t1_no_tightness_logpop)[vars_core_t1], Scheme = "No Tightness + Log-Pop")
) %>%
  mutate(
    lower = Coef - 1.96 * SE,
    upper = Coef + 1.96 * SE,
    Variable = factor(Variable, levels = rev(labels_core_t1)),
    Scheme = factor(Scheme, levels = c("Original", "No Tightness", "No Tightness + Log-Pop"))
  )
logpop_t1_median <- median(abs((coef(est_all_t1_no_tightness_logpop)[vars_core_t1] - coef(est_all_t1)[vars_core_t1]) / coef(est_all_t1)[vars_core_t1]) * 100, na.rm = TRUE)
min_lp <- min(plot_df_t1$lower, na.rm = TRUE)
max_lp <- max(plot_df_t1$upper, na.rm = TRUE)
pad_lp <- (max_lp - min_lp) * 0.1
if (!is.finite(pad_lp) || pad_lp == 0) {
  pad_lp <- abs(min_lp) * 0.2 + 0.01
}

ggplot(plot_df_t1, aes(x = Coef, y = Variable, color = Scheme, shape = Scheme)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", size = 0.6) +
  geom_point(position = position_dodge(width = 0.6), size = 2.6) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),
                 position = position_dodge(width = 0.6),
                 height = 0.2, linewidth = 0.8) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  labs(x = "Coefficient", y = NULL) +
  scale_color_manual(
    values = c("Original" = "#28A745", "No Tightness" = "#6C757D", "No Tightness + Log-Pop" = "#F24236"),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_shape_manual(
    values = c("Original" = 16, "No Tightness" = 15, "No Tightness + Log-Pop" = 17),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(min_lp - pad_lp, max_lp + pad_lp),
    breaks = pretty(c(min_lp - pad_lp, max_lp + pad_lp), n = 4)
  )
```

Median absolute change across coefficients in Figure 4: `r sprintf('%.0f%%', logpop_t1_median)`.

### Log-Population Weights (Table 2, Column 4) {.unnumbered}

We repeat the same exercise for the Table 2 baseline (column 4). Coefficient magnitudes again attenuate under log(population) weights (see Figure 5).

```{r}
#| label: fig-logpop-compact-t2
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Coefficient sensitivity after removing tightness using log-population weights (Table 2, Col. 4)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 6
#| fig-height: 4
# Rebuild z-scored growth dataset with raw log(pop) for weights
data_t2_logpop <- data_ai_2017_2022 %>%
  filter(emp != 0) %>%
  drop_na(share_bac14) %>%
  mutate(
    logpop_raw = logpop14,
    share_bac14 = scale(share_bac14),
    share_black14 = scale(share_black14),
    share_poverty14 = scale(share_poverty14),
    logpop14 = scale(logpop14),
    hpi_ch14 = scale(hpi_ch14),
    logincome14 = scale(logincome14),
    tightness14 = scale(tightness14),
    pat_intensity14 = scale(pat_intensity14),
    patai_intensity14 = scale(patai_intensity14),
    degshare14 = scale(degshare14),
    stemshare14 = scale(stemshare14),
    large_firms14 = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14 = scale(manuf_intensity14),
    TurnOvrS14 = scale(TurnOvrS14),
    unrate14 = scale(unrate14)
  ) %>%
  mutate(dai_intensity9 = dai_intensity9 * 100) %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2_lp <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness_lp <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)
plot_df_t2 <- bind_rows(
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_lp)[vars_core_t2], SE = se(est_all_t2_lp)[vars_core_t2], Scheme = "Original"),
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_no_tightness_lp)[vars_core_t2], SE = se(est_all_t2_no_tightness_lp)[vars_core_t2], Scheme = "No Tightness"),
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_no_tightness_logpop)[vars_core_t2], SE = se(est_all_t2_no_tightness_logpop)[vars_core_t2], Scheme = "No Tightness + Log-Pop")
) %>%
  mutate(
    lower = Coef - 1.96 * SE,
    upper = Coef + 1.96 * SE,
    Variable = factor(Variable, levels = rev(labels_core_t2)),
    Scheme = factor(Scheme, levels = c("Original", "No Tightness", "No Tightness + Log-Pop"))
  )
logpop_t2_median <- median(abs((coef(est_all_t2_no_tightness_logpop)[vars_core_t2] - coef(est_all_t2_lp)[vars_core_t2]) / coef(est_all_t2_lp)[vars_core_t2]) * 100, na.rm = TRUE)
min_lp <- min(plot_df_t2$lower, na.rm = TRUE)
max_lp <- max(plot_df_t2$upper, na.rm = TRUE)
pad_lp <- (max_lp - min_lp) * 0.1
if (!is.finite(pad_lp) || pad_lp == 0) {
  pad_lp <- abs(min_lp) * 0.2 + 0.01
}

ggplot(plot_df_t2, aes(x = Coef, y = Variable, color = Scheme, shape = Scheme)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", size = 0.6) +
  geom_point(position = position_dodge(width = 0.6), size = 2.6) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),
                 position = position_dodge(width = 0.6),
                 height = 0.2, linewidth = 0.8) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  labs(x = "Coefficient", y = NULL) +
  scale_color_manual(
    values = c("Original" = "#28A745", "No Tightness" = "#6C757D", "No Tightness + Log-Pop" = "#F24236"),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_shape_manual(
    values = c("Original" = 16, "No Tightness" = 15, "No Tightness + Log-Pop" = 17),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(min_lp - pad_lp, max_lp + pad_lp),
    breaks = pretty(c(min_lp - pad_lp, max_lp + pad_lp), n = 4)
  )
```

Median absolute change across coefficients in Figure 5: `r sprintf('%.0f%%', logpop_t2_median)`.




