---
title: "Local Heterogeneity in Artificial Intelligence Jobs Over Time and Space"
subtitle: "A Replication Study of Andreadis et al. (AEA Papers and Proceedings, 2025)"
author:
  - name: "Jacob Khaykin^[Solon High School, [jacobkhaykin27@solonschools.net](mailto:jacobkhaykin27@solonschools.net)]"
  - name: "David Kane^[New College of Florida, [dakane@ncf.edu](mailto:dakane@ncf.edu)]"
bibliography: references.bib
csl: aea.csl
link-citations: true
citeproc: true
nocite: '@*'
format:
  pdf:
    keep-tex: true
    number-sections: true
    documentclass: article
    geometry: 
      - margin=1in
    include-in-header:
      - text: |
          \usepackage{url}
          \urlstyle{same}
          \def\UrlBreaks{\do\/\do-\do.\do:}
          \usepackage{float}
          \usepackage{array}
          \usepackage{siunitx}
          \usepackage{dcolumn}
          \newcolumntype{d}[1]{D{.}{.}{#1}}
          % reset numbering after abstract
          \usepackage{etoolbox}
          \AtBeginEnvironment{abstract}{\setcounter{section}{0}}
          % Custom table row spacing
          \renewcommand{\arraystretch}{0.9}
          % Configure siunitx for modern versions (>=3)
          \sisetup{
            detect-all,
            input-symbols = (),
            input-signs = + -,
            table-align-text-pre = false,
            table-number-alignment = center,
            table-format = +1.4,
            group-digits = false,
            table-space-text-pre = ***,
            table-space-text-post = ***,
            mode = math
          }
  docx: default
---


```{r}
#| label: setup
#| include: false
# Load all required packages
library(tidyverse)
library(fixest)
library(modelsummary)
library(kableExtra)
library(sf)
library(scales)
library(tigris)
library(ggplot2)
library(patchwork)
library(grid)
library(png)
library(usmap)
library(viridis)
library(dplyr)
library(forcats)
# Set options
options(tigris_use_cache = TRUE)
data_raw <- read_csv("data.csv")

fmt_est <- function(estimate, se) {
  ifelse(
    is.na(estimate),
    "",
    paste0(sprintf("%.4f", estimate), " (", sprintf("%.4f", se), ")")
  )
}

make_comparison_table <- function(replication_models, coef_map, original_overrides = NULL,
                                  caption, note) {
  estimates <- purrr::imap_dfr(
    replication_models,
    function(model, model_label) {
      broom::tidy(model) %>%
        filter(term %in% names(coef_map)) %>%
        transmute(
          model = model_label,
          term,
          variable = unname(coef_map[term]),
          replication_estimate = estimate,
          replication_se = std.error
        )
    }
  )

  comparison <- estimates %>%
    mutate(
      original_estimate = replication_estimate,
      original_se = replication_se
    )

  if (!is.null(original_overrides)) {
    comparison <- comparison %>%
      left_join(original_overrides, by = c("model", "term"), suffix = c("", "_override")) %>%
      mutate(
        original_estimate = coalesce(original_estimate_override, original_estimate),
        original_se = coalesce(original_se_override, original_se)
      ) %>%
      select(-ends_with("_override"))
  }

  table_format <- if (knitr::is_latex_output()) "latex" else "html"

  table_out <- comparison %>%
    mutate(
      `Original` = fmt_est(original_estimate, original_se),
      `Replication` = fmt_est(replication_estimate, replication_se),
      `Difference` = ifelse(
        is.na(original_estimate),
        "",
        sprintf("%.4f", replication_estimate - original_estimate)
      )
    ) %>%
    select(Model = model, Variable = variable, Original, Replication, Difference) %>%
    arrange(Model, factor(Variable, levels = unname(coef_map))) %>%
    knitr::kable(
      format = table_format,
      booktabs = TRUE,
      longtable = FALSE,
      caption = NULL,
      align = c("l", "l", "r", "r", "r"),
      escape = TRUE
    )

  if (knitr::is_latex_output()) {
    table_out %>%
      kableExtra::kable_styling(
        latex_options = c("hold_position", "scale_down"),
        font_size = 8,
        full_width = FALSE
      ) %>%
      kableExtra::collapse_rows(columns = 1, valign = "top") %>%
      kableExtra::footnote(
        general = note,
        general_title = "Notes: ",
        threeparttable = TRUE,
        escape = TRUE
      )
  } else {
    table_out %>%
      kableExtra::kable_styling(
        bootstrap_options = c("striped", "condensed"),
        font_size = 13,
        full_width = FALSE
      ) %>%
      kableExtra::collapse_rows(columns = 1, valign = "top") %>%
      kableExtra::footnote(
        general = note,
        general_title = "Notes: ",
        escape = TRUE
      )
  }
}
```

*JEL: J24, O33, R11*

*Keywords:* Artificial Intelligence, Regional Economics, Labor Markets

*Data Availability:* The R code and data to reproduce this replication are available in this repository: https://github.com/JacobKhay/Andreadis-Replication.


## Abstract {.unnumbered}

We partially replicate @andreadis2025 on the correlation between the level and growth of artificial intelligence employment across U.S. counties from 2014 to 2023 and a collection of variables related to education, innovation, and industry. We successfully reproduce most of their results and, to assess robustness, extend their analysis by using log-population weights. Most, but not all, of the associations persist. We critique the construction of a key variable and the authors' unsupported causal claims. 

Declaration: There are no financial conflicts of interest to share. 

\newpage

## Introduction

This paper replicates @andreadis2025, henceforth AKCLM, on the correlation between the level and growth of artificial intelligence employment and education, innovation, and industry factors across U.S. counties from 2014 to 2023. Understanding where AI intensity emerges and how it spreads matters for researchers and policymakers alike: AI has the potential to reshape regional economies [@acemoglu2024; @brynjolfsson2021], alter the demand for skills [@autor2015; @acemoglu2019], and shift patterns of innovation [@babina2024]. 

AKCLM define "AI intensity" as AI-related job postings divided by total job postings in US counties. There are two outcome variables: the level of AI intensity for each county-year and the growth of AI intensity between 2017-2018 and 2022-2023 for each county.

AKCLM link county-level AI intensity to several explanatory factors. Education is captured by the share of adults with a college degree, innovation by local patenting activity [@giczy2022], and industry by the composition of employment across sectors. 

AKCLM find that both the level and growth of AI intensity are associated with higher educational attainment, more innovation activity, and certain industry profiles. For the level of AI intensity, bachelor's degree share, and STEM degree share are positively associated, while manufacturing intensity is negatively associated. For the growth of AI intensity and STEM degree share remain significantly correlated, while turnover rate shows a negative association.

We reproduce these results and extend the analysis using log-population weights. Under this adjustment, the core associations persist for both outcomes but estimated magnitudes generally shrink. For the level of AI intensity, patents per employee shows the most robust association across weighting schemes, while bachelor's share shows the largest magnitude decline. For the growth of AI intensity, STEM degree share show the most consistent associations, though effect sizes diminish when we weight by log-population.


Finally, AKCLM's causal interpretations are not supported by the observational nature of their data [@holland1986].

## Data

AKCLM utilize multiple data sources to construct a comprehensive county-level dataset spanning 2014–2023:

*AI Job Employment Data*: Lightcast [@beckett2023] aggregates job postings from over 40,000 online job boards, newspapers, and employer websites. AI-related jobs are identified through skills and keywords associated with AI development and use [@acemoglu2022]. The first dependent variable, AI intensity, is defined as:

$$
AI_{it} = \frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} \times 100 \tag{1}
$$

AI intensity has a mean of 0.4 percentage points and a standard deviation of 1.1 percentage points across county-year observations.

The second dependent variable captures the percentage point change in AI intensity between the 2017-2018 average and the 2022-2023 average: 

$$
\Delta AI_{i} = \frac{\sum_{t \in \{2022,2023\}} \text{AI}_{it}}{\sum_{t \in \{2022,2023\}} \text{Total}_{it}} - \frac{\sum_{t \in \{2017,2018\}} \text{AI}_{it}}{\sum_{t \in \{2017,2018\}} \text{Total}_{it}} \tag{2}
$$

The change in AI intensity has a mean of 0.3 percentage points and a standard deviation of 1.0 percentage points across counties.

*Demographic Variables*: From the American Community Survey [@census_acs], AKCLM construct several county-level demographic measures, including bachelor's share (percentage of workforce with bachelor's degree or higher), black population share (percentage of county population identifying as Black), poverty share (percentage of population below federal poverty line), log-population (natural logarithm of county population), and log median income (natural logarithm of median household income).

*Innovation Indicators*: AKCLM construct several innovation measures, including patents per employee (USPTO patent counts normalized by employment), AI patents share (percentage of patents classified as AI-related) [@giczy2022], STEM degrees share (percentage of awarded degrees in STEM fields), and degrees per capita (total degrees awarded per capita).

*Industry and Labor Market Variables*: AKCLM construct several industry and labor market measures, including labor market tightness (ratio of job postings to unemployed workers) [@bls_laus], manufacturing intensity (employment share in manufacturing sector) [@census_cbp], ICT intensity (employment share in information and communication technology), turnover rate (worker separation rate from Quarterly Workforce Indicators) [@census_qwi], and large establishments share (percentage of employment in large firms).
Housing Market: AKCLM include house price growth from the Federal Housing Finance Agency [@bogin2019].

*Housing Market*: We include house price growth from Federal Housing Finance Agency [@bogin2019].  

All explanatory variables are lagged by one year. 


An important statistical issue arises from the construction of labor market tightness. AI intensity is defined as AI job postings divided by total job postings, while labor market tightness is constructed as total job postings divided by unemployed workers. Total job postings thus appears in the denominator of the dependent variable and in the numerator of a key regressor.

This creates denominator contamination, or mechanical endogeneity: both sides of the regression share the same underlying quantity, inducing a correlation that exists purely through algebraic construction.


$$
\frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} = \alpha + \beta \frac{\text{Total job postings}_{it}}{\text{Unemployed}_{it}} + X'_{it}\gamma + \varepsilon_{it} \tag{3}
$$

This can bias coefficient estimates and overstate statistical significance. The issue is analogous to regressing $Y/Z$ on $Z/X$ where the shared $Z$ induces correlation even when $Y$ and $X$ are actually independent. Kronmal [-@kronmal1993spurious] shows that when the dependent variable is a ratio sharing a component with an independent variable, "regression coefficient estimates for the other independent variables ... result in inappropriate conclusions." 

## Replication

We use R [@ihaka1996r] and the tidyverse collection of packages [@tidyverse]. To estimate and display regression models, we use fixest [@fixest] and modelsummary [@modelsummary].

Our reproduction begins from the intermediate replication materials released with AKCLM: the authors' `data.csv` and `replication_code.R` from the openICPSR archive. We do not reconstruct the full county-year dataset from the underlying raw sources such as Lightcast, ACS, QWI, CBP, LAUS, FHFA, and patent records. Instead, we treat AKCLM's released `data.csv` as the analysis-ready input and rerun the estimation and figure-construction steps from that point. For Tables 1 and 2, we recreate the variables, samples, standardization, weights, fixed effects, and model specifications from the published replication code, then compare the resulting estimates with the published tables. For Figure 1, we compare the published figure image with maps generated from the released data and the definitions stated in the article and code, because the available code does not reproduce the published Panel B map exactly.

Following AKCLM, we report only variables that have statistically significant coefficients in at least one model specification.

### Table 1

The core model for the level of AI intensity is a two-way fixed-effects regression:

$$
AI_{it} = \alpha_i + \alpha_t + \boldsymbol{\beta}' \mathbf{X}_{it-1} + \varepsilon_{it} \tag{4}
$$

where $\alpha_i$ and $\alpha_t$ are county and year fixed effects, $\mathbf{X}_{it-1}$ is a vector of standardized regressors lagged one year, and $\varepsilon_{it}$ is an error term clustered at the county level.

We reproduce Table 1 from AKCLM. All coefficients and standard errors match the original results.

```{r}
#| label: tbl-table1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "AKCLM and replication estimates for the level of AI intensity"
#| tbl-cap-location: top
#| tbl-pos: "H"

# ── Construct all variables in one pipeline ──

data_ai <- data_raw %>%
  mutate(
    state_year            = paste0(state, Year),
    ai_intensity          = ai / nads,
    logincome             = log(medhhincome),
    logpop                = log(pop),
    logemp                = log(Employed),
    lads                  = log(1 + nads),
    pat_intensity         = n_inventors / Employed,
    patai_intensity       = replace_na(ai_patents / n_patents, 0),
    large_firms           = 1 - (small + medium) / est,
    information_intensity = replace_na(information_emp / emp, 0),
    manuf_intensity       = manuf_emp / emp,
    degshare              = (udeg + mdeg) / Employed,
    stemshare             = replace_na((ustemdeg + mstemdeg) / (udeg + mdeg), 0),
    tightness             = nads / Unemployed,
    hpi_ch                = hpi_ch / 100
  )

# ── Standardize, saving raw values for extension weighting ──

data_ai_z <- data_ai %>%
  filter(emp != 0) %>%
  mutate(
    pop_raw    = pop,
    logpop_raw = logpop,
    logemp_raw = logemp
  ) %>%
  mutate(
    share_bac             = as.numeric(scale(share_bac)),
    share_black           = as.numeric(scale(share_black)),
    share_poverty         = as.numeric(scale(share_poverty)),
    logpop                = as.numeric(scale(logpop)),
    hpi_ch                = as.numeric(scale(hpi_ch)),
    logincome             = as.numeric(scale(logincome)),
    tightness             = as.numeric(scale(tightness)),
    unrate                = as.numeric(scale(unrate)),
    pat_intensity         = as.numeric(scale(pat_intensity)),
    patai_intensity       = as.numeric(scale(patai_intensity)),
    degshare              = as.numeric(scale(degshare)),
    stemshare             = as.numeric(scale(stemshare)),
    large_firms           = as.numeric(scale(large_firms)),
    information_intensity = as.numeric(scale(information_intensity)),
    manuf_intensity       = as.numeric(scale(manuf_intensity)),
    TurnOvrS              = as.numeric(scale(TurnOvrS))
  ) %>%
  mutate(ai_intensity = ai_intensity * 100)

# ── Common sample ──

data_ai_z_complete <- data_ai_z %>%
  drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
          tightness, pat_intensity, patai_intensity, degshare, stemshare,
          large_firms, information_intensity, manuf_intensity, TurnOvrS)

# ── Regressions ──

est_demog <- feols(
  ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch +
    logincome + tightness | Year + COUNTY_FIPS,
  data = data_ai_z_complete, cluster = "COUNTY_FIPS", weights = ~lads
)

est_innov <- feols(
  ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare |
    Year + COUNTY_FIPS,
  data = data_ai_z_complete, cluster = "COUNTY_FIPS", weights = ~lads
)

est_indus <- feols(
  ai_intensity ~ large_firms + information_intensity + manuf_intensity +
    TurnOvrS | Year + COUNTY_FIPS,
  data = data_ai_z_complete, cluster = "COUNTY_FIPS", weights = ~lads
)

est_all <- feols(
  ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch +
    logincome + tightness + pat_intensity + patai_intensity + degshare +
    stemshare + large_firms + information_intensity + manuf_intensity +
    TurnOvrS | Year + COUNTY_FIPS,
  data = data_ai_z, cluster = "COUNTY_FIPS", weights = ~lads
)

est_all_sy <- feols(
  ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch +
    logincome + tightness + pat_intensity + patai_intensity + degshare +
    stemshare + large_firms + information_intensity + manuf_intensity +
    TurnOvrS | state_year + COUNTY_FIPS,
  data = data_ai_z, vcov = "twoway", weights = ~lads
)

# ── Side-by-side comparison table ──

labels_t1 <- c(
  "share_bac"             = "Bachelor's share",
  "hpi_ch"                = "House price growth",
  "tightness"             = "Labor tightness",
  "pat_intensity"         = "Patents per employee",
  "stemshare"             = "STEM degrees share",
  "information_intensity" = "ICT sector intensity",
  "manuf_intensity"       = "Manufacturing",
  "TurnOvrS"              = "Turnover rate"
)

t1_models <- list(
  "(1) Demographics" = est_demog,
  "(2) Innovation" = est_innov,
  "(3) Industry" = est_indus,
  "(4) All controls" = est_all,
  "(5) State-year FE" = est_all_sy
)

make_comparison_table(
  replication_models = t1_models,
  coef_map = labels_t1,
  caption = "AKCLM and replication estimates for the level of AI intensity",
  note = paste(
    "Each cell reports coefficient and standard error in parentheses.",
    "The original and replication estimates match to the displayed precision.",
    "The dependent variable is AI intensity in percentage points.",
    "Columns 1-4 include county and year fixed effects; column 5 includes county and state-year fixed effects.",
    "All explanatory variables are standardized and lagged by one year."
  )
)
```

Table 1 presents parameter estimates for five models, each using AI intensity as the outcome, which has a mean of 0.4 percentage points and a standard deviation of 1.1 percentage points across county-year observations. All regressors are standardized. Column 4 (the preferred specification) includes the full control set with county and year fixed effects; all subsequent discussion refers to this column.

Bachelor's share (0.18, p < 0.001) is the largest demographic predictor of AI intensity. Two counties differing by one standard deviation in bachelor's share are expected to differ by 0.18 percentage points in AI intensity, which is 42% of the mean and 16% of the standard deviation.

Among the innovation variables, STEM degree share (0.048, p < 0.05) carries a coefficient 62% larger than patents per employee (0.029, p < 0.01). Two counties differing by one standard deviation in STEM degree share are expected to differ by 0.048 percentage points in AI intensity (11% of the mean and 4% of the standard deviation), compared with 0.029 percentage points for patents per employee (7% of the mean, 3% of the standard deviation). 

Among industry variables, ICT intensity (0.026, p = 0.058) and manufacturing intensity (−0.033, p < 0.01) exhibit similar effect sizes but opposite signs. Two counties differing by one standard deviation in manufacturing intensity are expected to differ by 0.033 percentage points (8% of the standard deviation), compared with 0.026 percentage points for ICT intensity (6% of the standard deviation). 

### Table 2

For the growth of AI intensity, we estimate a cross-sectional OLS regression with no fixed effects:

$$
\Delta AI_{i} = \beta_0 + \boldsymbol{\beta}' \mathbf{X}_{i,2017} + \varepsilon_{i} \tag{5}
$$

where $\Delta AI_{i}$ is the percentage point change in AI intensity between the 2017–2018 and 2022–2023 averages, $\beta_0$ is a constant term representing expected AI intensity growth when all predictors are at their mean, $\mathbf{X}_{i,2017}$ is a vector of standardized regressors measured in 2017, and $\varepsilon_{i}$ is an error term clustered at the county level. Unlike equation (3), there is no time subscript $t$ because the growth of AI intensity is a single observation per county — the change between two pooled periods — rather than a panel. This model does not include county or year fixed effects, as the outcome is already a first difference across counties.

We reproduce Table 2 from AKCLM. All our results match AKCLM's, except for the coefficient and standard error for bachelor's share in all models in which it appears. The source of this discrepancy remains unknown, but the pattern is systematic rather than random. In column 1, the published bachelor's-share coefficient is 0.0022 with a standard error of 0.0027, while rerunning AKCLM's released code and data gives 0.0196 with a standard error of 0.0250. In columns 4 and 5, the published coefficients are -0.0035 and -0.0044, while the corresponding rerun values are -0.0322 and -0.0401. Thus, both the coefficient and standard error are approximately nine times larger in the rerun than in the published table. This suggests a reporting or scaling discrepancy specific to bachelor's share, because the same rerun reproduces the remaining reported coefficients. The authors were contacted regarding this discrepancy but did not respond.

```{r}
#| label: tbl-table2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "AKCLM and replication estimates for the growth of AI intensity"
#| tbl-cap-location: top
#| tbl-pos: "H"

# ── Build cross-sectional growth dataset from the single data load ──

data_ai_growth <- data_raw %>%
  filter(Year %in% c(2017, 2018, 2022, 2023)) %>%
  mutate(
    state_year = paste0(state, Year),
    new        = as.integer(Year > 2020)
  ) %>%
  group_by(new, COUNTY_FIPS) %>%
  mutate(ai = sum(ai), nads = sum(nads), ai_intensity = ai / nads) %>%
  filter(Year %in% c(2017, 2022)) %>%
  ungroup()

# ── Construct variables and create lagged (2017) values ──

data_ai_growth <- data_ai_growth %>%
  mutate(
    logincome             = log(medhhincome),
    logpop                = log(pop),
    logemp                = log(Employed),
    lads                  = log(1 + nads),
    pat_intensity         = n_inventors / Employed,
    patai_intensity       = replace_na(ai_patents / n_patents, 0),
    large_firms           = 1 - (small + medium) / est,
    information_intensity = information_emp / emp,
    manuf_intensity       = manuf_emp / emp,
    degshare              = (udeg + mdeg) / Employed,
    stemshare             = replace_na((ustemdeg + mstemdeg) / (udeg + mdeg), 0),
    tightness             = nads / Unemployed,
    hpi_ch                = hpi_ch / 100
  ) %>%
  group_by(COUNTY_FIPS) %>%
  mutate(
    dai_intensity9          = ai_intensity - lag(ai_intensity, 1),
    gpop                    = (logpop - lag(logpop, 1)) / 5,
    share_bac14             = lag(share_bac, 1),
    share_black14           = lag(share_black, 1),
    share_poverty14         = lag(share_poverty, 1),
    logpop14                = lag(logpop, 1),
    hpi_ch14                = lag(hpi_ch, 1),
    logincome14             = lag(logincome, 1),
    tightness14             = lag(tightness, 1),
    pat_intensity14         = lag(pat_intensity, 1),
    patai_intensity14       = lag(patai_intensity, 1),
    degshare14              = lag(degshare, 1),
    stemshare14             = lag(stemshare, 1),
    large_firms14           = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14       = lag(manuf_intensity, 1),
    TurnOvrS14              = lag(TurnOvrS, 1),
    lads14                  = lag(lads, 1),
    unrate14                = lag(unrate, 1)
  ) %>%
  ungroup()

# ── Standardize lagged predictors and scale outcome ──

data_ai_l_z <- data_ai_growth %>%
  filter(emp != 0) %>%
  drop_na(share_bac14) %>%
  mutate(
    share_bac14             = scale(share_bac14),
    share_black14           = scale(share_black14),
    share_poverty14         = scale(share_poverty14),
    logpop14                = scale(logpop14),
    hpi_ch14                = scale(hpi_ch14),
    logincome14             = scale(logincome14),
    tightness14             = scale(tightness14),
    pat_intensity14         = scale(pat_intensity14),
    patai_intensity14       = scale(patai_intensity14),
    degshare14              = scale(degshare14),
    stemshare14             = scale(stemshare14),
    large_firms14           = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14       = scale(manuf_intensity14),
    TurnOvrS14              = scale(TurnOvrS14),
    unrate14                = scale(unrate14),
    dai_intensity9          = dai_intensity9 * 100
  )

# ── Common sample ──

data_t2 <- data_ai_l_z %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14,
          logincome14, tightness14, pat_intensity14, patai_intensity14,
          degshare14, stemshare14, large_firms14, information_intensity14,
          manuf_intensity14, TurnOvrS14)

# ── Regressions ──

est_t2_demog <- feols(
  dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop +
    hpi_ch14 + logincome14 + tightness14,
  data = data_t2, weights = ~lads14
)

est_t2_innov <- feols(
  dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14,
  data = data_t2, weights = ~lads14
)

est_t2_indus <- feols(
  dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 +
    TurnOvrS14,
  data = data_t2, weights = ~lads14
)

est_t2_all <- feols(
  dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop +
    hpi_ch14 + logincome14 + tightness14 + pat_intensity14 +
    patai_intensity14 + degshare14 + stemshare14 + large_firms14 +
    information_intensity14 + manuf_intensity14 + TurnOvrS14,
  data = data_t2, weights = ~lads14
)

est_t2_all_state <- feols(
  dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop +
    hpi_ch14 + logincome14 + tightness14 + pat_intensity14 +
    patai_intensity14 + degshare14 + stemshare14 + large_firms14 +
    information_intensity14 + manuf_intensity14 + TurnOvrS14 | state,
  data = data_t2, weights = ~lads14
)

# ── Side-by-side comparison table ──

labels_t2 <- c(
  "share_bac14"             = "Bachelor's share",
  "logincome14"             = "Income, log",
  "tightness14"             = "Labor tightness",
  "stemshare14"             = "STEM degrees share",
  "large_firms14"           = "Large establishments",
  "information_intensity14" = "ICT sector intensity",
  "manuf_intensity14"       = "Manufacturing",
  "TurnOvrS14"              = "Turnover rate"
)

t2_models <- list(
  "(1) Demographics" = est_t2_demog,
  "(2) Innovation" = est_t2_innov,
  "(3) Industry" = est_t2_indus,
  "(4) All controls" = est_t2_all,
  "(5) State FE" = est_t2_all_state
)

published_t2_overrides <- tribble(
  ~model, ~term, ~original_estimate, ~original_se,
  "(1) Demographics", "share_bac14",  0.0022, 0.0027,
  "(4) All controls", "share_bac14", -0.0035, 0.0032,
  "(5) State FE",     "share_bac14", -0.0044, 0.0029
)

make_comparison_table(
  replication_models = t2_models,
  coef_map = labels_t2,
  original_overrides = published_t2_overrides,
  caption = "AKCLM and replication estimates for the growth of AI intensity",
  note = paste(
    "Each cell reports coefficient and standard error in parentheses.",
    "The original column reports the published AKCLM values; the replication column reports estimates from the published replication code and data.",
    "The displayed discrepancy is confined to bachelor's share in columns 1, 4, and 5.",
    "The dependent variable is the percentage-point change in AI intensity between the 2017-2018 and 2022-2023 averages.",
    "Columns 1-4 have no fixed effects; column 5 includes state fixed effects."
  )
)
```

Table 2 analyzes predictors of the growth of AI intensity between 2017–2018 and 2022–2023. All regressors are standardized, with explanatory variables measured in 2017. Column 4 includes the full control set and serves as the preferred specification; all subsequent discussion refers to this column.

STEM degree share (0.054, p < 0.01) is the largest statistically significant predictor of AI intensity growth in the preferred specification. Two counties differing by one standard deviation in STEM degree share are expected to differ by 0.054 percentage points in AI intensity growth, equivalent to 61% of the median of 0.088 percentage points.

Among labor market variables, turnover rate (−0.042, p < 0.01) carries a coefficient 2.7 times larger in magnitude than large establishment share (−0.016, p = 0.47). Two counties differing by one standard deviation in turnover rate are expected to differ by 0.042 percentage points in AI intensity growth (48% of the median), compared with 0.016 percentage points for large establishment share (18% of the median).

```{r}
#| label: map-plot-side-by-side
#| echo: false
#| message: false
#| warning: false
#| fig-pos: "H"
#| fig-width: 19
#| fig-height: 13.5

library(tidyverse)
library(sf)
library(tigris)
library(patchwork)

figure_data <- data_raw %>%
  filter(COUNTY_FIPS != 9999) %>%
  filter(!(COUNTY_FIPS >= 9110 & COUNTY_FIPS <= 9190))

panel_a_values <- figure_data %>%
  mutate(aiInt = if_else(nads > 0, ai / nads, NA_real_)) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(aiInt = mean(aiInt, na.rm = TRUE), .groups = "drop")

panel_b_akclm_values <- figure_data %>%
  filter(Year > 2017) %>%
  arrange(COUNTY_FIPS, Year) %>%
  mutate(aiInt = if_else(nads > 0, ai / nads, NA_real_)) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(aiIntch = last(aiInt) - first(aiInt), .groups = "drop")

panel_b_replication_values <- figure_data %>%
  mutate(
    year_group = case_when(
      Year %in% c(2017, 2018) ~ "2017-2018",
      Year %in% c(2022, 2023) ~ "2022-2023",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(year_group)) %>%
  group_by(COUNTY_FIPS, year_group) %>%
  summarise(
    ai_sum = sum(ai, na.rm = TRUE),
    nads_sum = sum(nads, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(aiInt = if_else(nads_sum > 0, ai_sum / nads_sum, NA_real_)) %>%
  pivot_wider(
    id_cols = COUNTY_FIPS,
    names_from = year_group,
    values_from = aiInt
  ) %>%
  mutate(aiIntch = `2022-2023` - `2017-2018`) %>%
  select(COUNTY_FIPS, aiIntch)

panel_a_bins <- panel_a_values %>%
  mutate(fips = str_pad(as.character(COUNTY_FIPS), 5, "left", "0")) %>%
  mutate(ai_share = aiInt * 100) %>%
  mutate(avg_bin = case_when(
    ai_share >= 0 & ai_share < 0.06 ~ "0 - 0.06",
    ai_share > 0.06 & ai_share < 0.14 ~ "0.06 - 0.14",
    ai_share > 0.14 & ai_share < 0.23 ~ "0.14 - 0.23",
    ai_share > 0.23 & ai_share < 0.37 ~ "0.23 - 0.37",
    ai_share > 0.37 & ai_share < 0.71 ~ "0.37 - 0.71",
    ai_share > 0.71 & ai_share <= 10 ~ "0.71 - 10",
    TRUE ~ "No data"
  ))

bin_panel_b <- function(data) {
  data %>%
    mutate(fips = str_pad(as.character(COUNTY_FIPS), 5, "left", "0")) %>%
  mutate(change_in_share = aiIntch * 100) %>%
    mutate(chg_bin = case_when(
      change_in_share > 0.57 & change_in_share <= 12.35 ~ "0.57 - 12.35",
      change_in_share > 0.24 & change_in_share < 0.57 ~ "0.24 - 0.57",
      change_in_share > 0.09 & change_in_share < 0.24 ~ "0.09 - 0.24",
      change_in_share > 0 & change_in_share < 0.09 ~ "0 - 0.09",
      change_in_share > -0.12 & change_in_share <= 0 ~ "-0.12 - 0",
      change_in_share >= -5.56 & change_in_share <= -0.12 ~ "-5.56 - -0.12",
      TRUE ~ "No data"
    ))
}

panel_b_akclm_bins <- bin_panel_b(panel_b_akclm_values)
panel_b_replication_bins <- bin_panel_b(panel_b_replication_values)

options(tigris_use_cache = TRUE)
counties <- suppressMessages(
  tigris::counties(cb = TRUE, year = 2020, class = "sf")
) %>%
  mutate(COUNTY_FIPS = GEOID) %>%
  filter(!str_starts(COUNTY_FIPS, "72")) %>%
  st_transform(crs = 4326)

levels_avg_display <- c("0.71 - 10", "0.37 - 0.71", "0.23 - 0.37",
                        "0.14 - 0.23", "0.06 - 0.14", "0 - 0.06", "No data")
levels_chg_display <- c("0.57 - 12.35", "0.24 - 0.57", "0.09 - 0.24",
                        "0 - 0.09", "-0.12 - 0", "-5.56 - -0.12", "No data")

colors_avg_display <- c("#800026", "#e31a1c", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")
colors_chg_display <- c("#800026", "#fc4e2a", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")

map_join <- function(values, fill_col, levels) {
  counties %>%
    left_join(values, by = c("COUNTY_FIPS" = "fips")) %>%
    mutate("{fill_col}" := factor(replace_na(.data[[fill_col]], "No data"), levels = levels)) %>%
    tigris::shift_geometry()
}

map_a_akclm <- map_join(panel_a_bins, "avg_bin", levels_avg_display)
map_a_replication <- map_join(panel_a_bins, "avg_bin", levels_avg_display)
map_b_akclm <- map_join(panel_b_akclm_bins, "chg_bin", levels_chg_display)
map_b_replication <- map_join(panel_b_replication_bins, "chg_bin", levels_chg_display)

map_theme <- theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 9, margin = margin(t = 2, b = 2, l = 1, r = 1)),
    legend.title = element_blank(),
    legend.key.width = unit(1.0, "cm"),
    legend.key.height = unit(0.35, "cm"),
    legend.spacing.x = unit(0.2, "cm"),
    legend.margin = margin(t = 4, b = 2),
    legend.key = element_rect(color = "black", linewidth = 0.3),
    plot.margin = margin(4, 4, 12, 4, "pt"),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.border = element_rect(color = "gray45", fill = NA, linewidth = 0.35),
    plot.title = element_text(size = 15, hjust = 0.5, margin = margin(b = 5))
  )

make_avg_map <- function(map_data, title) {
  ggplot(map_data) +
  geom_sf(aes(fill = avg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_avg_display, levels_avg_display),
                    breaks = levels_avg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.0, "cm"), keyheight = unit(0.35, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", linewidth = 0.3))) +
  coord_sf(crs = st_crs(map_data), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
    labs(title = title) +
    map_theme
}

make_chg_map <- function(map_data, title) {
  ggplot(map_data) +
  geom_sf(aes(fill = chg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_chg_display, levels_chg_display),
                    breaks = levels_chg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.0, "cm"), keyheight = unit(0.35, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", linewidth = 0.3))) +
  coord_sf(crs = st_crs(map_data), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
    labs(title = title) +
    map_theme
}

make_published_panel <- function(path, title) {
  image <- png::readPNG(path)
  image_height <- dim(image)[1]
  image_width <- dim(image)[2]
  ggplot() +
    annotation_raster(image, xmin = 0, xmax = image_width, ymin = 0, ymax = image_height, interpolate = TRUE) +
    coord_fixed(xlim = c(0, image_width), ylim = c(0, image_height), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(
      plot.title = element_text(size = 15, hjust = 0.5, margin = margin(b = 5)),
      plot.margin = margin(4, 4, 12, 4, "pt"),
      panel.border = element_rect(color = "gray45", fill = NA, linewidth = 0.35),
      plot.background = element_rect(fill = "white", color = NA)
    )
}

p_a_published <- make_published_panel("figures/published_figure1_panel_a.png", "Published Panel A")
p_a_replication <- make_avg_map(map_a_replication, "Replication Panel A")
p_b_published <- make_published_panel("figures/published_figure1_panel_b.png", "Published Panel B")
p_b_replication <- make_chg_map(map_b_replication, "Replication Panel B")

final_plot <- ((p_a_published | p_a_replication) / (p_b_published | p_b_replication)) +
  plot_layout(heights = c(1, 1)) +
  plot_annotation(
    title = "Spatial heterogeneity in AI jobs: published figure and replication",
    subtitle = "Panels A-B show average AI intensity, 2014-2023. Panels C-D show the change in AI intensity. Left column: published AKCLM panels; right column: replication maps.",
    tag_levels = "A",
    theme = theme(
      plot.title = element_text(size = 23, hjust = 0.5, margin = margin(b = 6)),
      plot.subtitle = element_text(size = 15, hjust = 0.5, margin = margin(b = 12)),
      plot.tag = element_text(size = 16, face = "bold")
    )
  )

final_plot
```
*Notes:* Panels A and B show average AI intensity from 2014 to 2023; Panels C and D show the change in AI intensity. The left column reproduces the published AKCLM Figure 1 panels as images extracted from the published article. The right column shows maps generated from the replication data and definitions. Our replication Panel B uses the change in AI intensity between 2017--2018 and 2022--2023, while AKCLM's published figure labels Panel B as the 2018--2023 change. Connecticut appears with N/A values because AKCLM's released `data.csv` contains no Connecticut county rows. The available code and published figure therefore point to different Panel B constructions; the source of the published-image discrepancy remains unresolved.

Figure 1 displays the spatial distribution and evolution of AI intensity across U.S. counties from 2014 to 2023. Panel A is reproducible from the released data: the generated county values match exactly across all 3,130 counties in the comparison file, and no county changes bins. Panel B is not reproducible in the same way. When we compare the available AKCLM map-code construction (2023 annual intensity minus 2018 annual intensity) with the article's stated pooled-window construction (2022--2023 minus 2017--2018), 2,562 of 3,130 counties have a nonzero difference, 1,453 counties change color bins, and the median absolute difference is 0.138 percentage points. The differences exceed 0.10 percentage points in 1,805 counties, 0.25 points in 1,076 counties, 0.50 points in 548 counties, 1 point in 204 counties, 2 points in 58 counties, and 5 points in 11 counties; the maximum absolute difference is 9.890 percentage points. These discrepancies are most consistent with a coding or definition difference in the Panel B time window rather than a data-vintage difference, because both calculations use the same released AKCLM `data.csv`. County definitions also matter for coverage: the released data include 27 Alaska counties and 4 Hawaii counties but no Connecticut county FIPS rows, so Connecticut cannot be mapped with values from the released data.

We assess robustness by re-estimating AKCLM's preferred specifications with log-population weights after removing labor market tightness from both weighted and unweighted models. This extension asks whether the reported associations are similar when populous counties receive more weight, while holding the specification fixed. We interpret the resulting coefficient changes descriptively rather than as evidence that relationships are necessarily stronger or weaker in particular county-size groups.

## Extension: Log-Population Weighting Analysis

To assess robustness, we re-estimate all models using log-population weights. Because labor market tightness shares total job postings with the denominator of AI intensity, we omit labor market tightness from both the equal-weighted and log-population-weighted extension models. The weighting comparison therefore holds the specification fixed and changes only the weighting scheme. Following AKCLM, we report only variables that have statistically significant coefficients in at least one model specification. Log-population weights give more weight to populous counties relative to equal weighting, where each county receives the same weight regardless of population size.

```{r}
#| label: fig-table1-coefs-models1-3
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 1 from Andreadis et al. (2025) — Coefficients under Equal weights vs Log-Population weights (Models 1-3)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 10

library(ggplot2)
library(dplyr)
library(forcats)
library(patchwork)

# Run equal-weighted regressions (no weights) for comparison (Models 1-3).
# Tightness is omitted here and in the weighted models to keep specifications identical.
est_demog_no <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

est_innovation_no <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

est_industry_no <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

# Run log-population weighted regressions (Models 1-3) - same no-tightness specification
est_demog_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_innovation_logpop <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_industry_logpop <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

models <- c("Demographics", "Innovation", "Industry")
variables <- c(
  "Bachelor's share", "Labor Tightness", "Patents per emp.",
  "STEM share", "Manufacturing intensity", "ICT intensity"
)

variables_list <- list(
  c("Bachelor's share", "House price growth"),
  c("Patents per emp.", "STEM share"),
  c("Manufacturing intensity", "ICT intensity", "Turnover rate")
)

# Extract coefficients and SEs from original (equal-weighted) regressions (Models 1-3)
coefs_orig_list <- list(
  c(coef(est_demog_no)["share_bac"], coef(est_demog_no)["hpi_ch"]),
  c(coef(est_innovation_no)["pat_intensity"], coef(est_innovation_no)["stemshare"]),
  c(coef(est_industry_no)["manuf_intensity"], coef(est_industry_no)["information_intensity"], coef(est_industry_no)["TurnOvrS"])
)

ses_orig_list <- list(
  c(se(est_demog_no)["share_bac"], se(est_demog_no)["hpi_ch"]),
  c(se(est_innovation_no)["pat_intensity"], se(est_innovation_no)["stemshare"]),
  c(se(est_industry_no)["manuf_intensity"], se(est_industry_no)["information_intensity"], se(est_industry_no)["TurnOvrS"])
)

# Extract coefficients and SEs from log-pop weighted regressions (Models 1-3) - tightness excluded
coefs_log_list <- list(
  c(coef(est_demog_logpop)["share_bac"], coef(est_demog_logpop)["hpi_ch"]),
  c(coef(est_innovation_logpop)["pat_intensity"], coef(est_innovation_logpop)["stemshare"]),
  c(coef(est_industry_logpop)["manuf_intensity"], coef(est_industry_logpop)["information_intensity"], coef(est_industry_logpop)["TurnOvrS"])
)

ses_log_list <- list(
  c(se(est_demog_logpop)["share_bac"], se(est_demog_logpop)["hpi_ch"]),
  c(se(est_innovation_logpop)["pat_intensity"], se(est_innovation_logpop)["stemshare"]),
  c(se(est_industry_logpop)["manuf_intensity"], se(est_industry_logpop)["information_intensity"], se(est_industry_logpop)["TurnOvrS"])
)

make_df <- function(model_index) {
  vars <- variables_list[[model_index]]
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_orig_list[[model_index]],
      SE = ses_orig_list[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_log_list[[model_index]],
      SE = ses_log_list[[model_index]],
      Scheme = "Log-Population Weights"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plot function with better styling
plots <- lapply(1:3, function(i) {
  df <- make_df(i)

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL) +
    theme_minimal(base_size = 18) +
    theme(
      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20"),
      legend.margin = margin(t = 10),
      legend.box.spacing = unit(0.5, "cm")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.6, 0.6)))
})

# Add titles directly to the plots instead of separate label objects
plots_with_tags <- lapply(1:3, function(i) {
  df <- make_df(i)

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models[i]) +
    theme_minimal(base_size = 18) +
    theme(
      # Tag styling (panel labels)
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 0.98),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 10, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20"),
      legend.margin = margin(t = 10),
      legend.box.spacing = unit(0.5, "cm")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.6, 0.6)))
})

# Simple vertical arrangement
final <- plots_with_tags[[1]] / plots_with_tags[[2]] / plots_with_tags[[3]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final
```
*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 1–3 of Table 1. These models examine AI intensity as the outcome variable. Model 1 (Demographics) includes bachelor's share and house price growth. Model 2 (Innovation) includes patents per employee and STEM degree share. Model 3 (Industry) includes manufacturing intensity, ICT intensity, and turnover rate. All models include county and year fixed effects. Labor market tightness is omitted from both equal-weighted and log-population-weighted models due to denominator contamination. All variables are standardized, so coefficients represent the change in AI intensity in percentage points associated with a one-standard-deviation increase in each predictor, holding other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates and red points indicate log-population-weighted estimates.

```{r}
#| label: fig-table1-coefs-models4-5
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 1 from Andreadis et al. (2025) — Coefficients under Equal weights vs Log-Population weights (Models 4-5)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 12

# Run equal-weighted regressions (no weights) for comparison (Models 4-5).
# Tightness is omitted here and in the weighted models to keep specifications identical.
est_all <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS"
)

est_all_state_year <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway"
)

# Run log-population weighted regressions (Models 4-5) - same no-tightness specification
est_all_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_all_state_year_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway",
  weights = ~logpop_raw
)

models_45 <- c("All Controls", "All + State FE")
variables_45 <- c(
  "Bachelor's share", "House price growth",
  "Patents per emp.", "STEM share", "ICT intensity", "Manufacturing intensity", "Turnover rate"
)

variables_list_45 <- list(
  variables_45,
  variables_45
)

# Extract coefficients and SEs from original (equal-weighted) regressions (Models 4-5)
coefs_orig_list_45 <- list(
  c(coef(est_all)["share_bac"], coef(est_all)["hpi_ch"],
    coef(est_all)["pat_intensity"], coef(est_all)["stemshare"],
    coef(est_all)["information_intensity"], coef(est_all)["manuf_intensity"], coef(est_all)["TurnOvrS"]),
  c(coef(est_all_state_year)["share_bac"], coef(est_all_state_year)["hpi_ch"],
    coef(est_all_state_year)["pat_intensity"],
    coef(est_all_state_year)["stemshare"], coef(est_all_state_year)["information_intensity"],
    coef(est_all_state_year)["manuf_intensity"], coef(est_all_state_year)["TurnOvrS"])
)

ses_orig_list_45 <- list(
  c(se(est_all)["share_bac"], se(est_all)["hpi_ch"],
    se(est_all)["pat_intensity"], se(est_all)["stemshare"],
    se(est_all)["information_intensity"], se(est_all)["manuf_intensity"], se(est_all)["TurnOvrS"]),
  c(se(est_all_state_year)["share_bac"], se(est_all_state_year)["hpi_ch"],
    se(est_all_state_year)["pat_intensity"],
    se(est_all_state_year)["stemshare"], se(est_all_state_year)["information_intensity"],
    se(est_all_state_year)["manuf_intensity"], se(est_all_state_year)["TurnOvrS"])
)

# Extract coefficients and SEs from log-pop weighted regressions (Models 4-5) - tightness excluded
coefs_log_list_45 <- list(
  c(coef(est_all_logpop)["share_bac"], coef(est_all_logpop)["hpi_ch"],
    coef(est_all_logpop)["pat_intensity"],
    coef(est_all_logpop)["stemshare"], coef(est_all_logpop)["information_intensity"],
    coef(est_all_logpop)["manuf_intensity"], coef(est_all_logpop)["TurnOvrS"]),
  c(coef(est_all_state_year_logpop)["share_bac"], coef(est_all_state_year_logpop)["hpi_ch"],
    coef(est_all_state_year_logpop)["pat_intensity"],
    coef(est_all_state_year_logpop)["stemshare"], coef(est_all_state_year_logpop)["information_intensity"],
    coef(est_all_state_year_logpop)["manuf_intensity"], coef(est_all_state_year_logpop)["TurnOvrS"])
)

ses_log_list_45 <- list(
  c(se(est_all_logpop)["share_bac"], se(est_all_logpop)["hpi_ch"],
    se(est_all_logpop)["pat_intensity"],
    se(est_all_logpop)["stemshare"], se(est_all_logpop)["information_intensity"],
    se(est_all_logpop)["manuf_intensity"], se(est_all_logpop)["TurnOvrS"]),
  c(se(est_all_state_year_logpop)["share_bac"], se(est_all_state_year_logpop)["hpi_ch"],
    se(est_all_state_year_logpop)["pat_intensity"],
    se(est_all_state_year_logpop)["stemshare"], se(est_all_state_year_logpop)["information_intensity"],
    se(est_all_state_year_logpop)["manuf_intensity"], se(est_all_state_year_logpop)["TurnOvrS"])
)

make_df_45 <- function(model_index) {
  vars <- variables_list_45[[model_index]]
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_orig_list_45[[model_index]],
      SE = ses_orig_list_45[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_log_list_45[[model_index]],
      SE = ses_log_list_45[[model_index]],
      Scheme = "Log-Population Weights"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plots for models 4-5
plots_45 <- lapply(1:2, function(i) {
  df <- make_df_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL) +
    theme_minimal(base_size = 18) +
    theme(
      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.4, 0.4)))
})

# Enhanced plots for models 4-5 with panel tags
plots_45_with_tags <- lapply(1:2, function(i) {
  df <- make_df_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models_45[i]) +
    theme_minimal(base_size = 18) +
    theme(
      # Tag styling (panel labels)
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 1.03),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 10, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.4, 0.4)))
})

# Simple vertical arrangement for models 4-5
final_45 <- plots_45_with_tags[[1]] / plots_45_with_tags[[2]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final_45
```
*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 4–5 of Table 1. These models examine AI intensity as the outcome variable. Model 4 (All Controls) includes all demographic, innovation, and industry variables with county and year fixed effects. Model 5 (All + State FE) replaces year fixed effects with state-year fixed effects. Both models include bachelor's share, house price growth, patents per employee, STEM degree share, ICT intensity, manufacturing intensity, and turnover rate. Labor market tightness is omitted from both equal-weighted and log-population-weighted models due to denominator contamination. All variables are standardized, so coefficients represent the change in AI intensity in percentage points associated with a one-standard-deviation increase in each predictor, holding all other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates and red points indicate log-population-weighted estimates.

In Model 4, coefficient estimates remain stable across weighting schemes. Bachelor's share is associated with approximately a 0.01 percentage point increase in AI intensity per standard deviation, while house price growth shows minimal independent effect. Among innovation variables, patents per employee shows approximately a 0.05 percentage point increase and STEM degree share shows roughly a 0.09 percentage point increase per standard deviation. Among industry variables, manufacturing intensity is associated with approximately a 0.03 percentage point decrease, ICT intensity with a 0.12 percentage point increase, and turnover rate with the largest effect of approximately 0.18 percentage points per standard deviation. 


```{r}
#| label: fig-table2-coefs-models1-3
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 2 from Andreadis et al. (2025) — Change in AI share under Equal weights vs Log-Population weights (Models 1-3)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 10

# Prepare data for Table 2 regressions (growth models) - use data_ai_l_z that's already prepared
data_t2_z <- data_ai_l_z %>%
  filter(emp != 0, dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14) %>%
  mutate(
    # Save raw values for weighting
    logpop_raw = logpop,
    lads14_raw = exp(logpop14)  # Convert back from z-score approximation
  )

# Run equal-weighted regressions for Table 2 Models 1-3 (NO fixed effects, just OLS).
# Tightness is omitted here and in the weighted models to keep specifications identical.
est_t2_demog_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_innovation_no <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + stemshare14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_industry_no <- fixest::feols(
  "dai_intensity9 ~ manuf_intensity14 + information_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

# Run population weighted regressions for Table 2 Models 1-3 - same no-tightness specification
est_t2_demog_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)  # Use actual population (exp of log population)
)

est_t2_innovation_logpop <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + stemshare14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

est_t2_industry_logpop <- fixest::feols(
  "dai_intensity9 ~ manuf_intensity14 + information_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

models <- c("Demographics", "Innovation", "Industry")

variables_list <- list(
  c("Bachelors Share", "House Price Growth"),
  c("Patents per emp.", "STEM Degrees' share"),
  c("Manufacturing Intensity %", "ICT sector Intensity %", "Turnover Rate %")
)

# Extract coefficients from actual (equal-weighted) regressions
coefs_actual_list <- list(
  c(coef(est_t2_demog_no)["share_bac14"], coef(est_t2_demog_no)["hpi_ch14"]),
  c(coef(est_t2_innovation_no)["pat_intensity14"], coef(est_t2_innovation_no)["stemshare14"]),
  c(coef(est_t2_industry_no)["manuf_intensity14"], coef(est_t2_industry_no)["information_intensity14"], coef(est_t2_industry_no)["TurnOvrS14"])
)

ses_actual_list <- list(
  c(se(est_t2_demog_no)["share_bac14"], se(est_t2_demog_no)["hpi_ch14"]),
  c(se(est_t2_innovation_no)["pat_intensity14"], se(est_t2_innovation_no)["stemshare14"]),
  c(se(est_t2_industry_no)["manuf_intensity14"], se(est_t2_industry_no)["information_intensity14"], se(est_t2_industry_no)["TurnOvrS14"])
)

# Extract coefficients from log-pop weighted regressions - tightness excluded
coefs_logpop_list <- list(
  c(coef(est_t2_demog_logpop)["share_bac14"], coef(est_t2_demog_logpop)["hpi_ch14"]),
  c(coef(est_t2_innovation_logpop)["pat_intensity14"], coef(est_t2_innovation_logpop)["stemshare14"]),
  c(coef(est_t2_industry_logpop)["manuf_intensity14"], coef(est_t2_industry_logpop)["information_intensity14"], coef(est_t2_industry_logpop)["TurnOvrS14"])
)

ses_logpop_list <- list(
  c(se(est_t2_demog_logpop)["share_bac14"], se(est_t2_demog_logpop)["hpi_ch14"]),
  c(se(est_t2_innovation_logpop)["pat_intensity14"], se(est_t2_innovation_logpop)["stemshare14"]),
  c(se(est_t2_industry_logpop)["manuf_intensity14"], se(est_t2_industry_logpop)["information_intensity14"], se(est_t2_industry_logpop)["TurnOvrS14"])
)

# Andreadis et al. (2025) bachelor's share coefficient from the paper
coefs_andreadis_bac <- 0.0022

make_df <- function(model_index) {
  vars <- variables_list[[model_index]]

  # For Model 1 (Demographics), include Andreadis bachelor's share as a third scheme
  if (model_index == 1) {
    bind_rows(
      data.frame(
        Variable = vars,
        Coef = coefs_actual_list[[model_index]],
        SE = ses_actual_list[[model_index]],
        Scheme = "Equal Weights"
      ),
      data.frame(
        Variable = vars,
        Coef = coefs_logpop_list[[model_index]],
        SE = ses_logpop_list[[model_index]],
        Scheme = "Log-Population Weights"
      ),
      data.frame(
        Variable = "Bachelors Share",
        Coef = coefs_andreadis_bac,
        SE = ses_actual_list[[model_index]][1],
        Scheme = "Andreadis et al. (2025)"
      )
    ) %>%
      mutate(
        lower = Coef - 1.96 * SE,
        upper = Coef + 1.96 * SE,
        Variable = fct_rev(factor(Variable, levels = vars)),
        Scheme = factor(Scheme, levels = c("Andreadis et al. (2025)", "Log-Population Weights", "Equal Weights"))
      )
  } else {
    bind_rows(
      data.frame(
        Variable = vars,
        Coef = coefs_actual_list[[model_index]],
        SE = ses_actual_list[[model_index]],
        Scheme = "Equal Weights"
      ),
      data.frame(
        Variable = vars,
        Coef = coefs_logpop_list[[model_index]],
        SE = ses_logpop_list[[model_index]],
        Scheme = "Log-Population Weights"
      )
    ) %>%
      mutate(
        lower = Coef - 1.96 * SE,
        upper = Coef + 1.96 * SE,
        Variable = fct_rev(factor(Variable, levels = vars)),
        Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
      )
  }
}

# Enhanced plots for Table 2 with integrated tags
plots_t2_with_tags <- lapply(1:3, function(i) {
  df <- make_df(i)
  n_vars <- length(unique(df$Variable))
  y_expand <- if(n_vars == 2) c(0.8, 0.8) else c(0.5, 0.5)

  # Determine which levels exist in this plot
  existing_levels <- levels(df$Scheme)
  all_colors <- c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236",
                  "Andreadis et al. (2025)" = "#2E86AB")
  # Filter colors to only include existing levels
  plot_colors <- all_colors[names(all_colors) %in% existing_levels]

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models[i]) +
    theme_minimal(base_size = 12) +
    theme(
      # Tag styling
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 0.98),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = plot_colors,
      breaks = if(i == 1) c("Equal Weights", "Log-Population Weights", "Andreadis et al. (2025)") else c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = y_expand))
})

# Simple vertical arrangement for Table 2 - remove legends from plots 2 and 3
plots_t2_with_tags[[2]] <- plots_t2_with_tags[[2]] + theme(legend.position = "none")
plots_t2_with_tags[[3]] <- plots_t2_with_tags[[3]] + theme(legend.position = "none")

final <- plots_t2_with_tags[[1]] / plots_t2_with_tags[[2]] / plots_t2_with_tags[[3]]

# Override to ensure single unified legend from plot 1 only
final <- final &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final
```
*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 1–3 of Table 2. These models examine the change in AI intensity between 2017–2018 and 2022–2023 as the outcome variable. Model 1 (Demographics) includes bachelor's share and house price growth. Model 2 (Innovation) includes patents per employee and STEM degree share. Model 3 (Industry) includes manufacturing intensity, ICT intensity, and turnover rate. Labor market tightness is omitted from both equal-weighted and log-population-weighted models due to denominator contamination. All predictors are measured in 2017, the base period before the growth window. All variables are standardized, so coefficients represent the change in AI intensity growth in percentage points associated with a one-standard-deviation increase in each predictor. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates, red points indicate log-population-weighted estimates, and blue points show the published bachelor's share coefficient from AKCLM for comparison.

```{r}
#| label: fig-table2-coefs-models4-5
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 2 from Andreadis et al. (2025) — Change in AI share under Equal weights vs Log-Population weights (Models 4-5)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 14

# Run equal-weighted regressions for Table 2 Models 4-5.
# Tightness is omitted here and in the weighted models to keep specifications identical.
est_t2_all_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_all_state_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

# Run population weighted regressions for Table 2 Models 4-5 - same no-tightness specification
est_t2_all_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

est_t2_all_state_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

models_t2_45 <- c("All Controls", "All + State FE")

variables_list_t2_45 <- list(
  c("Bachelors Share", "House Price Growth", "Patents per emp.", "STEM Degrees' share",
    "ICT sector Intensity %", "Manufacturing Intensity %", "Turnover Rate %"),
  c("Bachelors Share", "House Price Growth", "Patents per emp.", "STEM Degrees' share",
    "ICT sector Intensity %", "Manufacturing Intensity %", "Turnover Rate %")
)

# Extract coefficients from actual (equal-weighted) regressions - Models 4-5
coefs_actual_t2_45 <- list(
  c(coef(est_t2_all_no)["share_bac14"], coef(est_t2_all_no)["hpi_ch14"],
    coef(est_t2_all_no)["pat_intensity14"],
    coef(est_t2_all_no)["stemshare14"], coef(est_t2_all_no)["information_intensity14"],
    coef(est_t2_all_no)["manuf_intensity14"], coef(est_t2_all_no)["TurnOvrS14"]),
  c(coef(est_t2_all_state_no)["share_bac14"], coef(est_t2_all_state_no)["hpi_ch14"],
    coef(est_t2_all_state_no)["pat_intensity14"],
    coef(est_t2_all_state_no)["stemshare14"], coef(est_t2_all_state_no)["information_intensity14"],
    coef(est_t2_all_state_no)["manuf_intensity14"], coef(est_t2_all_state_no)["TurnOvrS14"])
)

ses_actual_t2_45 <- list(
  c(se(est_t2_all_no)["share_bac14"], se(est_t2_all_no)["hpi_ch14"],
    se(est_t2_all_no)["pat_intensity14"],
    se(est_t2_all_no)["stemshare14"], se(est_t2_all_no)["information_intensity14"],
    se(est_t2_all_no)["manuf_intensity14"], se(est_t2_all_no)["TurnOvrS14"]),
  c(se(est_t2_all_state_no)["share_bac14"], se(est_t2_all_state_no)["hpi_ch14"],
    se(est_t2_all_state_no)["pat_intensity14"],
    se(est_t2_all_state_no)["stemshare14"], se(est_t2_all_state_no)["information_intensity14"],
    se(est_t2_all_state_no)["manuf_intensity14"], se(est_t2_all_state_no)["TurnOvrS14"])
)

# Extract coefficients from log-pop weighted regressions - tightness excluded
coefs_logpop_t2_45 <- list(
  c(coef(est_t2_all_logpop)["share_bac14"], coef(est_t2_all_logpop)["hpi_ch14"],
    coef(est_t2_all_logpop)["pat_intensity14"],
    coef(est_t2_all_logpop)["stemshare14"], coef(est_t2_all_logpop)["information_intensity14"],
    coef(est_t2_all_logpop)["manuf_intensity14"], coef(est_t2_all_logpop)["TurnOvrS14"]),
  c(coef(est_t2_all_state_logpop)["share_bac14"], coef(est_t2_all_state_logpop)["hpi_ch14"],
    coef(est_t2_all_state_logpop)["pat_intensity14"],
    coef(est_t2_all_state_logpop)["stemshare14"], coef(est_t2_all_state_logpop)["information_intensity14"],
    coef(est_t2_all_state_logpop)["manuf_intensity14"], coef(est_t2_all_state_logpop)["TurnOvrS14"])
)

ses_logpop_t2_45 <- list(
  c(se(est_t2_all_logpop)["share_bac14"], se(est_t2_all_logpop)["hpi_ch14"],
    se(est_t2_all_logpop)["pat_intensity14"],
    se(est_t2_all_logpop)["stemshare14"], se(est_t2_all_logpop)["information_intensity14"],
    se(est_t2_all_logpop)["manuf_intensity14"], se(est_t2_all_logpop)["TurnOvrS14"]),
  c(se(est_t2_all_state_logpop)["share_bac14"], se(est_t2_all_state_logpop)["hpi_ch14"],
    se(est_t2_all_state_logpop)["pat_intensity14"],
    se(est_t2_all_state_logpop)["stemshare14"], se(est_t2_all_state_logpop)["information_intensity14"],
    se(est_t2_all_state_logpop)["manuf_intensity14"], se(est_t2_all_state_logpop)["TurnOvrS14"])
)

# Andreadis et al. (2025) bachelor's share coefficients
coefs_andreadis_t2_45_bac <- c(-0.0035, -0.0044)  # Models 4 and 5

make_df_t2_45 <- function(model_index) {
  vars <- variables_list_t2_45[[model_index]]

  # Include Andreadis bachelor's share as third scheme
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_actual_t2_45[[model_index]],
      SE = ses_actual_t2_45[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_logpop_t2_45[[model_index]],
      SE = ses_logpop_t2_45[[model_index]],
      Scheme = "Log-Population Weights"
    ),
    data.frame(
      Variable = "Bachelors Share",
      Coef = coefs_andreadis_t2_45_bac[model_index],
      SE = ses_actual_t2_45[[model_index]][1],
      Scheme = "Andreadis et al. (2025)"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Andreadis et al. (2025)", "Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plots for models 4-5 (Table 2) with integrated tags
plots_t2_45_with_tags <- lapply(1:2, function(i) {
  df <- make_df_t2_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.2, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.1, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models_t2_45[i]) +
    theme_minimal(base_size = 12) +
    theme(
      # Tag styling
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 1.03),

      # Y-axis styling
      axis.text.y = element_text(size = 12, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236",
                 "Andreadis et al. (2025)" = "#2E86AB"),
      breaks = c("Equal Weights", "Log-Population Weights", "Andreadis et al. (2025)")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.3, 0.3)))
})

# Simple vertical arrangement for Table 2, models 4-5
final_t2_45 <- plots_t2_45_with_tags[[1]] / plots_t2_45_with_tags[[2]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final_t2_45
```
*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 4–5 of Table 2. These models examine the change in AI intensity between 2017–2018 and 2022–2023 as the outcome variable. Model 4 (All Controls) includes all demographic, innovation, and industry variables with no fixed effects. Model 5 (All + State FE) adds state fixed effects to Model 4. Labor market tightness is omitted from both equal-weighted and log-population-weighted models due to denominator contamination. All predictors are measured in 2017, the base period before the growth window. All variables are standardized, so coefficients represent the change in AI intensity growth in percentage points associated with a one-standard-deviation increase in each predictor, holding all other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates, red points indicate log-population-weighted estimates, and blue points show the published bachelor's share coefficients from AKCLM for comparison.

In the fully specified Model 4, bachelor's share shows a small negative association with the growth of AI intensity under both weighting schemes. House price growth shows minimal independent effect. Among innovation variables, patents per employee declines from 0.06 percentage points under equal weights to 0.04 under log-population weights, while STEM degree share declines from 0.08 to 0.05 percentage points. Among industry variables, manufacturing intensity shows a negative association of approximately 0.03–0.04 percentage points, ICT intensity declines from 0.12 to 0.07 percentage points, and turnover rate declines from 0.17–0.18 to 0.11 percentage points.

Of the coefficients highlighted by AKCLM in their preferred levels specification, several decrease in absolute value under log-population weighting. STEM degree share is comparatively stable across weighting schemes, while bachelor's share, turnover rate, and manufacturing intensity weaken under population weighting. ICT intensity and patents per employee are exceptions, becoming slightly larger under population weighting. We do not interpret these shifts as proof that relationships are systematically stronger in smaller counties; attenuation under population weighting could also reflect high-variance observations or outliers among less-populous counties. A direct population-heterogeneity test, such as estimating models separately by population quartile, would be needed to distinguish those mechanisms.

AKCLM employ language suggesting causal relationships despite using observational county-level data with fixed-effects regressions. The empirical strategy does not support causal inference [@holland1986], yet the paper uses terminology that implies causation rather than correlation. Causal nouns such as "drivers," "determinants," "effects," and "impact" appear throughout, alongside causal verbs such as "drive," "fostering," and "influence." For instance, the paper refers to "key drivers of AI job intensity" and states that labor market tightness "emerges as a key driver," implying that changing these variables would directly alter AI adoption. The conclusion states that findings "point to the role of place-based policies," making policy recommendations based on associations rather than identified causal effects.

## Conclusion

This replication of AKCLM produces three sets of findings. First, several core regression results are reproduced. Table 1 is reproduced from the released analysis-ready data and code to the displayed precision, and most Table 2 coefficients also match when the released code is rerun. These results support AKCLM's broad descriptive claim that education, innovation, and industry variables are correlated with county-level AI intensity.

Second, two results are only partially reproduced. In Table 2, the bachelor's-share coefficient and standard error differ systematically from the published table in columns 1, 4, and 5, with the rerun values approximately nine times larger than the published values. In Figure 1, Panel A is reproducible from the released data, but Panel B is not: 1,453 of 3,130 counties change bins when comparing the available map-code construction with the pooled-window definition used in our replication, and 548 counties differ by more than 0.50 percentage points. The source of these discrepancies remains unknown, but the evidence points to reporting, scaling, or coding differences rather than a complete failure of the released dataset.

Third, our methodological extensions raise separate concerns. AKCLM employ causal language that the observational fixed-effects design cannot support without an explicit identification strategy [@holland1986]. In addition, labor market tightness mechanically shares total job postings with the denominator of AI intensity, creating a denominator-contamination concern. Finally, the log-population weighting exercise shows that some coefficient magnitudes change when more weight is given to populous counties, but those shifts should be interpreted as descriptive robustness evidence rather than proof of systematically stronger relationships in smaller counties.

## Bibliography {.unnumbered}
