---
title: "Local Heterogeneity in Artificial Intelligence Jobs Over Time and Space"
subtitle: "A Replication Study of Andreadis et al. (AEA Papers and Proceedings, 2025)"
author:
  - name: Jacob Khaykin^[Solon High School, [jacobkhaykin27@solonschools.net](mailto:jacobkhaykin27@solonschools.net)]
  - name: David Kane^[New College of Florida, [dakane@ncf.edu](mailto:dakane@ncf.edu)]
bibliography: references.bib
csl: aea.csl
link-citations: true
nocite: '@*'
format:
  pdf:
    keep-tex: true
    number-sections: true
    documentclass: article
    geometry: 
      - margin=1in
    include-in-header:
      - text: |
          \usepackage{url}
          \urlstyle{same}
          \def\UrlBreaks{\do\/\do-\do.\do:}
          \usepackage{float}
          \usepackage{array}
          \usepackage{siunitx}
          \usepackage{dcolumn}
          \newcolumntype{d}[1]{D{.}{.}{#1}}
          % reset numbering after abstract
          \usepackage{etoolbox}
          \AtBeginEnvironment{abstract}{\setcounter{section}{0}}
          % Custom table row spacing
          \renewcommand{\arraystretch}{0.9}
          % Configure siunitx for modern versions (>=3)
          \sisetup{
            detect-all,
            input-symbols = (),
            input-signs = + -,
            table-align-text-pre = false,
            table-number-alignment = center,
            table-format = +1.4,
            group-digits = false,
            table-space-text-pre = ***,
            table-space-text-post = ***,
            mode = math
          }
  docx: default
---


```{r}
#| label: setup
#| include: false
# Load all required packages
library(tidyverse)
library(fixest)
library(modelsummary)
library(kableExtra)
library(sf)
library(scales)
library(tigris)
library(ggplot2)
library(patchwork)
library(grid)
library(usmap)
library(viridis)
library(dplyr)
library(forcats)

# Set options
options(tigris_use_cache = TRUE)
```

<!-- TODO:  -->

<!-- DO NOT ASSUME OTHER PEOPLE ARE CORRECT! ASK AI! -->

<!-- Understand what the code is doing. AI can help! Also, the code for your extensions, should be clean and understandable. For example, you only download data.csv once, even though they download it lots of times. -->

<!-- Consider: "Most, but not all, of the associations persist." Is that reasonable? It is reasonable To examine, we first need the total number of significant coefficients with equal weights. Call it 15, perhaps only considering Model 4 for Tables 1 and 2. Then, of those 15, how many are still signficant? If that is 12, then sure, "Most, but not all" would be a reasonable description. But if only 7 do, then more than half are no longer significant. So, count them up and then we discuss. -->

<!-- Also, we need a sentence or two, maybe at the end of the Replication section, which describes this calculation, using the same sort of language as we do above. Actually, we should also have a sentence in the second to last paragraph of the introduction which covers this. Example: "Of the reported 15 significant regression coefficients in AKCLM's preferred models, only 8 remain signficant when the regressions are weighted by the log of county population." I the write up, this becomes a paragraph. "There is no single standard method for measuring how different two regression specifications are. AKCLM focus on their Model 4 for both dependendent variables: AI intensity and the change in AI intensity. With equal weighting, they estimate that the coefficients of &, *, *, ... are all statistically signficant. With log-weighted regressions, only . . .. " -->

<!-- Do not do this! "though effect sizes diminish when larger counties receive less weight." Instead of just saying log-weighted, as you should, you are coming up with different English words for no good reason. Maybe "though effect sizes diminish when we weight by the logaroithm of county population." Fixed-->

<!-- Print out the paper and have a friends read it aloud to you. Or, at least, read it aloud yourself. WIP -->

<!-- All write up in terms of comparing two groups, e.g., counties with average home price compared with counties with home price growth one standard deviation higher. The second group of counties has AI job percentage with is  1.5% (?) lower. Put in section 3. -->

<!-- Is there a good reason why Tables 1 and 2 differ in the width? -->

<!-- TO CONSIDER: -->

<!-- Open issue: Is their method for getting down to 24,000 rows for the regressions sensible? How much do results change if we fix this process? Worth doing? -->


*JEL: J24, O33, R11*

*Keywords:* Artificial Intelligence, Regional Economics, Labor Markets

*Data Availability:* The R code and data to reproduce this replication are available in this repository: https://github.com/JacobKhay/Andreadis-Replication.


## Abstract {.unnumbered}

We partially replicate @andreadis2025 on the correlation between the level and growth of artificial intelligence employment across U.S. counties from 2014 to 2023 and a collection of variables related to education, innovation, and industry. We successfully reproduce most of their results and, to assess robustness, extend their analysis by using log-population weights. Most, but not all, of the associations persist. We critique the construction of a key variable and their unsupported causal claims. 

Declaration: There are no financial conflicts of interest to share. 

\newpage

## Introduction

This paper replicates @andreadis2025, henceforth AKCLM, on the correlation between the level and growth of artificial intelligence employment and education, innovation, and industry factors across U.S. counties from 2014 to 2023. Understanding where AI intensity emerges and how it spreads matters for researchers and policymakers alike: AI has the potential to reshape regional economies [@acemoglu2024; @brynjolfsson2021], alter the demand for skills [@autor2015; @acemoglu2019], and shift patterns of innovation [@babina2024]. County-level variation offers a granular view of how these transformations unfold across the United States.

<!-- DK: Either years described explicitly in both or in neither. Should be both! And mention the US! -->

There are two outcome variables, both measures of AI intensity — the share of AI-related job postings in total job postings at the county-year level. The first is the level of AI intensity. The second is the percentage point change in AI intensity between 2017–2018 and 2022–2023. Together, these outcomes distinguish between where AI jobs are concentrated and where AI adoption is accelerating most rapidly. Tracking both provides insight into which regions gain early access to AI intensity and which experience the fastest growth.

AKCLM link county-level AI intensity to several explanatory factors. Education is captured by the share of adults with a college degree, innovation by local patenting activity [@giczy2022], and industry by the composition of employment across sectors. Together, these variables represent structural characteristics that may determine whether a region becomes a hub for AI employment.

AKCLM find that both the level and growth of AI intensity are associated with higher educational attainment, more innovation activity, and certain industry profiles. For the level of AI intensity, bachelor's degree share, labor market tightness, and STEM degree share are positively associated, while manufacturing intensity is negatively associated. For the growth of AI intensity, STEM degree share and labor market tightness remain significantly correlated, while turnover rate shows a negative association. These associations are robust across specifications, suggesting that counties with strong human capital, innovative capacity, and aligned industries experience both higher AI intensity and faster AI adoption. The results highlight structural divides in access to AI employment across the country.

<!-- DK: More room to add stuff in this paragraph. Which variables? Which matter most? Added that here-->

We reproduce these results and extend the analysis using log-population weights. Under this adjustment, the core associations persist for both outcomes but estimated magnitudes generally shrink. For the level of AI intensity, labor market tightness shows the most robust association across weighting schemes, while bachelor's share shows the largest magnitude decline. For the growth of AI intensity, STEM degree share and labor market tightness show the most consistent associations, though effect sizes diminish when we weight by the logarithim of county population.


Finally, AKCLM's causal interpretations are not supported by the observational nature of their data [@holland1986]. The associations documented do not establish that education, innovation, or industry factors directly cause higher AI intensity. Our replication underscores the value of the evidence while emphasizing the limits of what can be inferred from the design.

## Data

AKCLM utilize multiple data sources to construct a comprehensive county-level dataset spanning 2014–2023:

*AI Job Employment Data*: Lightcast [@beckett2023] aggregates job postings from over 40,000 online job boards, newspapers, and employer websites. AI-related jobs are identified through skills and keywords associated with AI development and use [@acemoglu2022]. The first dependent variable, AI intensity, is defined as:

$$
AI_{it} = \frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} \times 100 \tag{1}
$$

AI intensity has a mean of 0.4 percentage points and a standard deviation of 1.1 percentage points across county-year observations.

The second dependent variable captures the percentage point change in AI intensity between the 2017-2018 average and the 2022-2023 average: 

$$
\Delta AI_{i} = \overline{AI}_{i,2022-2023} - \overline{AI}_{i,2017-2018} \tag{2}
$$

The change in AI intensity has a mean of 0.3 percentage points and a standard deviation of 1.0 percentage points across counties.

*Demographic Variables*: From the American Community Survey [@census_acs], AKCLM construct several county-level demographic measures, including bachelor's share (percentage of workforce with bachelor's degree or higher), black population share (percentage of county population identifying as Black), poverty share (percentage of population below federal poverty line), log population (natural logarithm of county population), and log median income (natural logarithm of median household income).

*Innovation Indicators*: AKCLM construct several innovation measures, including patents per employee (USPTO patent counts normalized by employment), AI patents share (percentage of patents classified as AI-related) [@giczy2022], STEM degrees share (percentage of awarded degrees in STEM fields), and degrees per capita (total degrees awarded per capita).

*Industry and Labor Market Variables*: AKCLM construct several industry and labor market measures, including labor market tightness (ratio of job postings to unemployed workers) [@bls_laus], manufacturing intensity (employment share in manufacturing sector) [@census_cbp], ICT intensity (employment share in information and communication technology), turnover rate (worker separation rate from Quarterly Workforce Indicators) [@census_qwi], and large establishments share (percentage of employment in large firms).
Housing Market: AKCLM include house price growth from the Federal Housing Finance Agency [@bogin2019].

*Housing Market*: We include house price growth from Federal Housing Finance Agency [@bogin2019].  

All explanatory variables are lagged by one year. 


A significant statistical issue arises from the construction of the variables. AI intensity is defined as AI job postings divided by total job postings. Labor market tightness, one of the key variables, is constructed as total job postings divided by unemployed workers. Thus, total job postings appears in the denominator of the dependent variable and in the numerator of one of the independent variables.

This creates denominator contamination, or mechanical endogeneity: both sides of the regression share the same underlying quantity, inducing a correlation that exists purely through algebraic construction.


$$
\frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} = \alpha + \beta \frac{\text{Total job postings}_{it}}{\text{Unemployed}_{it}} + X'_{it}\gamma + \varepsilon_{it} \tag{3}
$$

This can bias coefficient estimates and overstate statistical significance. The issue is analogous to regressing $Y/Z$ on $Z/X$ where the shared $Z$ induces correlation even when $Y$ and $X$ are actually independent. Kronmal [-@kronmal1993spurious] shows that when the dependent variable is a ratio sharing a component with an independent variable, "regression coefficient estimates for the other independent variables ... result in inappropriate conclusions." 

## Replication

We use R [@ihaka1996r] and the tidyverse collection of packages [@tidyverse]. To estimate and display regression models, we use fixest [@fixest] and modelsummary [@modelsummary].

Following AKCLM, we report only variables that have statistically significant coefficients in at least one model specification; rows with insignificant coefficients are omitted for brevity.

### Table 1

The core model for the level of AI intensity is a two-way fixed-effects regression:

$$
AI_{it} = \alpha_i + \alpha_t + \boldsymbol{\beta}' \mathbf{X}_{it-1} + \varepsilon_{it} \tag{4}
$$

where $\alpha_i$ and $\alpha_t$ are county and year fixed effects, $\mathbf{X}_{it-1}$ is a vector of standardized regressors lagged one year, and $\varepsilon_{it}$ is an error term clustered at the county level.

We reproduce Table 1 from AKCLM. All coefficients and standard errors match the original results.

```{r}
#| label: tbl-table1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 1 from Andreadis et al. (2025) - The Correlates of the Share of Artificial Intelligence Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Load data
data_ai <- read_csv("data.csv") %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(ai_intensity = ai / nads)

# Prepare demographics
data_ai <- data_ai %>% 
  mutate(logincome = log(medhhincome), loghpi = log(hpi), logemp = log(pop_above18))

data_ai <- data_ai %>% 
  mutate(lads = log(1 + nads))

data_ai <- data_ai %>% 
  mutate(lads0 = log(nads))

# Log number of patents, inventors, etc.
data_ai <- data_ai %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai <- data_ai %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(pat_intensity = n_inventors / Employed, patai_intensity = ai_patents / n_patents) %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

# Industry structure
data_ai <- data_ai %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

data_ai <- data_ai %>% 
  mutate(information_intensity = replace_na(information_intensity, 0))

# Education variables
data_ai <- data_ai %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg),
    stemshare2 = (ustemdeg) / (udeg)
  )

data_ai <- data_ai %>%  
  mutate(stemshare = replace_na(stemshare, 0), stemshare2 = replace_na(stemshare2, 0))

# Labor market variables
data_ai <- data_ai %>%  
  mutate(tightness = nads / Unemployed)

data_ai <- data_ai %>%  
  mutate(hpi_ch = hpi_ch / 100)

# Z-scores - VERSION ROBUST with as.numeric()
data_ai_z <- data_ai %>%
  filter(emp != 0) %>%
  mutate(
    pop_raw = pop,        # Save raw population for weighting
    logpop_raw = logpop,  # Save raw log(pop) for weighting
    logemp_raw = logemp,  # Save raw log(employment) for weighting
    share_bac = as.numeric(scale(share_bac)),
    share_black = as.numeric(scale(share_black)),
    share_poverty = as.numeric(scale(share_poverty)),
    logpop = as.numeric(scale(logpop)),
    hpi_ch = as.numeric(scale(hpi_ch)),
    logincome = as.numeric(scale(logincome)),
    tightness = as.numeric(scale(tightness)),
    unrate = as.numeric(scale(unrate)),
    pat_intensity = as.numeric(scale(pat_intensity)),
    patai_intensity = as.numeric(scale(patai_intensity)),
    degshare = as.numeric(scale(degshare)),
    stemshare = as.numeric(scale(stemshare)),
    large_firms = as.numeric(scale(large_firms)),
    information_intensity = as.numeric(scale(information_intensity)),
    manuf_intensity = as.numeric(scale(manuf_intensity)),
    TurnOvrS = as.numeric(scale(TurnOvrS))
  ) %>%
  mutate(ai_intensity = ai_intensity * 100)

# Run regressions
est_demog_no <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_innovation_no <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_industry_no <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all_state_year <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway",
  weights = ~lads
)

# Extract model statistics
models <- list(est_demog_no, est_innovation_no, est_industry_no, est_all, est_all_state_year)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.5f", r2(.x, "r2")))

# Create table footer
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, state-year}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R²", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels
labels <- c(
  "share_bac" = "Bachelor's share",
  "hpi_ch" = "House price growth",
  "tightness" = "Labor tightness",
  "pat_intensity" = "Patents per employee",
  "stemshare" = "STEM degrees share",
  "information_intensity" = "ICT sector intensity",
  "manuf_intensity" = "Manufacturing",
  "TurnOvrS" = "Turnover rate"
)

# Create note text
table_notes <- paste(
  "This table replicates Table 1 from Andreadis et al. (2025).",
  "The dependent variable is AI intensity, defined as the share of AI-related job postings",
  "in total job postings in each county-year, multiplied by 100 to express in percentage terms.",
  "AI intensity has a mean of 0.4 percentage points and a standard deviation of 1.1 percentage points.",
  "All explanatory variables are standardized as z-scores.",
  "Coefficients represent the expected difference in AI intensity in percentage points",
  "between two counties differing by one standard deviation in the given predictor,",
  "holding all other variables constant.",
  "Models are estimated using OLS with county and year fixed effects (columns 1-4)",
  "or county and state-year fixed effects (column 5).",
  "Standard errors are clustered at the county level.",
  "All explanatory variables are lagged by one year."
)

# Create the table
modelsummary(
  list(
    "(1)" = est_demog_no,
    "(2)" = est_innovation_no,
    "(3)" = est_industry_no,
    "(4)" = est_all,
    "(5)" = est_all_state_year
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = fmt_decimal(4),
  align = "lddddd",
  notes = table_notes
)
```

Table 1 presents parameter estimates for five models, each using AI intensity as the outcome, which has a mean of 0.4 percentage points and a standard deviation of 1.1 percentage points across county-year observations. All regressors are standardized. Column 4 (the preferred specification) includes the full control set with county and year fixed effects; all subsequent discussion refers to this column.

Bachelor's share (0.18, p < 0.001) is the largest demographic predictor of AI intensity. Two counties differing by one standard deviation in bachelor's share are expected to differ by 0.18 percentage points in AI intensity, which is 42% of the mean and 16% of the standard deviation.

Within the innovation variables, STEM degree share (0.048, p < 0.05) carries a coefficient 62% larger than patents per employee (0.029, p < 0.01). Two counties differing by one standard deviation in STEM degree share are expected to differ by 0.048 percentage points in AI intensity (11% of the mean and 4% of the standard deviation), compared with 0.029 percentage points for patents per employee (7% of the mean, 3% of the standard deviation). Statistical precision favors patents, significant at the 1% level versus 5% for STEM degree share. STEM degree share thus exhibits larger magnitude while patents per employee exhibits greater precision.

Among industry variables, ICT intensity (0.026, p = 0.058) and manufacturing intensity (−0.033, p < 0.01) exhibit similar effect sizes but opposite signs. Two counties differing by one standard deviation in manufacturing intensity are expected to differ by 0.033 percentage points (8% of the standard deviation), compared with 0.026 percentage points for ICT intensity (6% of the standard deviation). Manufacturing is significant at the 1% level, whereas ICT intensity is significant only at the 10% level. Manufacturing thus exhibits both a larger point estimate and greater precision.

Comparing education variables, bachelor's share (0.18, p < 0.001) carries a coefficient 3.8 times larger than STEM degree share (0.048, p < 0.05). Two counties differing by one standard deviation in bachelor's share are expected to differ by 0.18 percentage points in AI intensity (16% of the standard deviation), compared with 0.048 percentage points for STEM degree share (4% of the standard deviation). Bachelor's share is also more precisely estimated, significant at the 0.1% level versus 5% for STEM degree share. Bachelor's share thus dominates on both magnitude and statistical precision.

### Table 2

For the growth outcome, we estimate a cross-sectional OLS regression with no fixed effects:

$$
\Delta AI_{i} = \beta_0 + \boldsymbol{\beta}' \mathbf{X}_{i,2017} + \varepsilon_{i} \tag{5}
$$

where $\Delta AI_{i}$ is the percentage point change in AI intensity between the 2017–2018 and 2022–2023 averages, $\beta_0$ is a constant term representing expected AI intensity growth when all predictors are at their mean, $\mathbf{X}_{i,2017}$ is a vector of standardized regressors measured in 2017, and $\varepsilon_{i}$ is an error term clustered at the county level. Unlike equation (3), there is no time subscript $t$ because the growth outcome is a single observation per county — the change between two pooled periods — rather than a panel. This model does not include county or year fixed effects, as the outcome is already a first difference across counties.

We reproduce Table 2 from AKCLM for all variables except bachelor's share, whose coefficient and standard error differ systematically across all five model specifications. The source of this discrepancy is unclear; the authors were contacted but did not respond.


```{r}
#| label: tbl-table2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 2 from Andreadis et al. (2025) - The Correlates of the Percentage Point Change in the Share of AI Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Follow EXACT original code structure
data_ai_2017_2022 <- read_csv("data.csv") %>% 
  filter(Year == 2017 | Year == 2018 | Year == 2022 | Year == 2023) %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(new = 1 * (Year > 2020)) %>% 
  group_by(new, COUNTY_FIPS) %>% 
  mutate(ai = sum(ai), nads = sum(nads)) %>% 
  mutate(ai_intensity = ai / nads) %>% 
  filter(Year == 2017 | Year == 2022) %>% 
  group_by(COUNTY_FIPS) %>% 
  mutate(
    dai_intensity = ai_intensity - lag(ai_intensity),
    dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
  )

# Prepare demographics - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logincome = log(medhhincome),
    loghpi = log(hpi),
    logemp = log(pop_above18),
    logim = log(1)  # Note: original has logim=log(immigration) but no immigration variable
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    unrate14 = lag(unrate, 1),
    logincome14 = lag(logincome, 1),
    loghpi14 = lag(loghpi, 1),
    share_bac14 = lag(share_bac, 1),
    share_black14 = lag(share_black, 1),
    share_poverty14 = lag(share_poverty, 1),
    logemp14 = lag(logemp, 1),
    logim14 = lag(logim, 1),
    medage14 = lag(medage, 1),
    median_rent14 = lag(median_rent, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    gincome = logincome - lag(logincome, 1),
    ghpi = loghpi - lag(loghpi, 1),
    gemp = logemp - lag(logemp, 1),
    gim = logim - lag(logim, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    dunrate = unrate - lag(unrate, 1),
    dshare_bac = share_bac - lag(share_bac, 1),
    dshare_black = share_black - lag(share_black, 1),
    dmedage14 = medage - lag(medage, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads = log(1 + nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads0 = log(nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    information_intensity = manuf_emp / emp  # Note: this overwrites previous line in original
  )

# Log number of patents, inventors, etc. - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

# Duplicate line in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

# Another duplicate section in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_inventors14 = lag(logn_inventors, 1),
    logai_inventors14 = lag(logai_inventors, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(stemshare = replace_na(stemshare, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(stemshare14 = lag(stemshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(degshare14 = lag(degshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(tightness = nads / Unemployed)

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(tightness14 = lag(tightness, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(hpi_ch14 = lag(hpi_ch, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logpop14 = lag(logpop, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logincome14 = lag(logincome, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(gpop = (logpop - lag(logpop, 1)) / 5)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch = hpi_ch / 100)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch14 = hpi_ch14 / 100)

# Industry structure
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms14 = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14 = lag(manuf_intensity, 1),
    TurnOvrS14 = lag(TurnOvrS, 1)
  )

# Z-scores - EXACT as original
data_ai_l_z <- data_ai_2017_2022 %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = scale(share_bac14),
    share_black14 = scale(share_black14),
    share_poverty14 = scale(share_poverty14),
    logpop14 = scale(logpop14),
    hpi_ch14 = scale(hpi_ch14),
    logincome14 = scale(logincome14),
    tightness14 = scale(tightness14),
    pat_intensity14 = scale(pat_intensity14),
    patai_intensity14 = scale(patai_intensity14),
    degshare14 = scale(degshare14),
    stemshare14 = scale(stemshare14),
    large_firms14 = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14 = scale(manuf_intensity14),
    TurnOvrS14 = scale(TurnOvrS14),
    unrate14 = scale(unrate14)
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)

# Run FULL models with ALL variables (not condensed)
est_demog_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14" %>% as.formula(),
  data_ai_l_z %>% 
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>% 
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  weights = ~lads14
) 

est_innovation_no <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14" %>% as.formula(),
  data_ai_l_z %>% 
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>% 
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  weights = ~lads14
) 

est_industry_no <- fixest::feols(
  "dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>% 
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>% 
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  weights = ~lads14
)

est_all <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>% 
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>% 
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  weights = ~lads14
)

est_all_large <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_ai_l_z %>% 
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>% 
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  weights = ~lads14
)

# Extract model statistics
models <- list(est_demog_no, est_innovation_no, est_industry_no, est_all, est_all_large)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.4f", r2(.x, "r2")))

# Create extra rows for table footer - add spacing before values to shift right
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}State}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R²", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels - condensed to only the 8 key variables
labels <- c(
  "share_bac14" = "Bachelors Share",
  "logincome14" = "Income, Log", 
  "tightness14" = "Tightness",
  "stemshare14" = "Stem Degrees' share",
  "large_firms14" = "Large Firms",
  "information_intensity14" = "ICT sector Intensity",
  "manuf_intensity14" = "Manufacturing",
  "TurnOvrS14" = "Turnover Rate"
)

# Create the table with modelsummary - use d for decimal alignment
modelsummary(
  list(
    "(1)" = est_demog_no,
    "(2)" = est_innovation_no,
    "(3)" = est_industry_no,
    "(4)" = est_all,
    "(5)" = est_all_large
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = 4,
  align = "lddddd",
  notes = "This table replicates Table 2 from AKCLM. The dependent variable is the change in AI intensity between the 2017–2018 and 2022–2023 averages, multiplied by 100 to express in percentage points. The change in AI intensity has a mean of 0.3 percentage points and a standard deviation of 1.0 percentage points. All explanatory variables are measured in 2017 and standardized as z-scores. Coefficients represent the expected difference in AI intensity growth in percentage points between two counties differing by one standard deviation in the given predictor, holding all other variables constant. Models are estimated using OLS with no fixed effects (columns 1–4) or state fixed effects (column 5). Standard errors are clustered at the county level. We reproduce all coefficients except bachelor's share, which differs systematically across all five model specifications from the published values. The authors were contacted regarding this discrepancy but did not respond."
)
```

Table 2 analyzes predictors of the growth of AI intensity between 2017–2018 and 2022–2023. All regressors are standardized, with explanatory variables measured in 2017. Column 4 includes the full control set and serves as the preferred specification; all subsequent discussion refers to this column.

Labor market tightness (0.073, p < 0.05) carries a coefficient 36% larger than STEM degree share (0.054, p < 0.01). Two counties differing by one standard deviation in tightness are expected to differ by 0.073 percentage points in AI intensity growth (83% of the median of 0.088 percentage points), compared with 0.054 percentage points for STEM degree share (61% of the median). Both coefficients are significant. Tightness thus exhibits a larger point estimate, though the gap is considerably narrower than in the levels specification of Table 1.

Among labor market variables, turnover rate (−0.042, p < 0.01) carries a coefficient 2.7 times larger in magnitude than large establishment share (−0.016, p = 0.47). Two counties differing by one standard deviation in turnover rate are expected to differ by 0.042 percentage points in AI intensity growth (48% of the median), compared with 0.016 percentage points for large establishment share (18% of the median). Turnover rate is significant at the 1% level, while large establishment share shows no statistical evidence.

Among industry variables, manufacturing intensity (−0.013, p = 0.48) and ICT intensity (0.014, p = 0.42) show nearly identical effect sizes but opposite signs. Two counties differing by one standard deviation in manufacturing intensity are expected to differ by only 0.013 percentage points in AI intensity growth (15% of the median), with ICT intensity showing a similarly small expected difference of 0.014 percentage points. Neither coefficient approaches statistical significance. This contrasts sharply with the levels specification of Table 1, where manufacturing intensity is significant at the 1% level with a coefficient of −0.033. Both effect sizes and statistical precision collapse in the growth specification of Table 2.


```{r}
#| label: fig-map
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "This figure shows the spatial heterogeneity in AI intensity across U.S. counties. Panel A shows average AI intensity from 2014 to 2023. Panel B shows the change in AI intensity between 2017–2018 and 2022–2023. Connecticut appears with N/A values because AKCLM's data does not include Connecticut counties. Hundreds of counties have different values in our replication, especially in Panel B. The authors were contacted regarding these discrepancies but did not respond."
#| fig-cap-location: bottom
#| fig-pos: "H"
#| fig-width: 18
#| fig-height: 9

library(tidyverse)
library(sf)
library(tigris)
library(patchwork)

# Read the updated Lightcast data
data <- read_csv("updated_lightcast_county.csv") %>%
  rename(COUNTY_FIPS = COUNTY_FIPS, 
         Year = YEAR_POSTED, 
         ai = `AI Postings`, 
         nads = `Total Postings`)

# Remove Connecticut state-level data (FIPS 9999) and Planning Region entries
data_complete <- data %>%
  filter(COUNTY_FIPS != 9999) %>%
  filter(!(COUNTY_FIPS >= 9110 & COUNTY_FIPS <= 9190))

# ---- PANEL A ----
data_levels <- data_complete %>%
  mutate(aiInt = if_else(nads > 0, ai/nads, NA_real_)) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(aiInt = mean(aiInt, na.rm = TRUE), .groups = "drop")

# ---- PANEL B ----
data_for_change <- data_complete %>%
  mutate(
    year_group = case_when(
      Year %in% c(2017, 2018) ~ "2017-2018",
      Year %in% c(2022, 2023) ~ "2022-2023",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(year_group))

data_pooled <- data_for_change %>%
  group_by(COUNTY_FIPS, year_group) %>%
  summarise(
    ai_sum = sum(ai, na.rm = TRUE),
    nads_sum = sum(nads, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(aiInt = if_else(nads_sum > 0, ai_sum / nads_sum, NA_real_))

data_ch <- data_pooled %>%
  pivot_wider(
    id_cols = COUNTY_FIPS,
    names_from = year_group,
    values_from = aiInt
  ) %>%
  mutate(aiIntch = `2022-2023` - `2017-2018`) %>%
  select(COUNTY_FIPS, aiIntch)

# ---- FIPS FORMATTING ----
merged_data_lev <- data_levels %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

merged_data_ch <- data_ch %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

# ---- PANEL A BINNING ----
merged_data_lev <- merged_data_lev %>%
  mutate(ai_share = aiInt * 100) %>%
  mutate(caseai = case_when(
    ai_share >= 0 & ai_share < 0.06 ~ 1,
    ai_share > 0.06 & ai_share < 0.14 ~ 2,
    ai_share > 0.14 & ai_share < 0.23 ~ 3,
    ai_share > 0.23 & ai_share < 0.37 ~ 4,
    ai_share > 0.37 & ai_share < 0.7 ~ 5,
    ai_share > 0.7 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- PANEL B BINNING ----
merged_data_ch <- merged_data_ch %>%
  mutate(change_in_share = aiIntch * 100) %>%
  mutate(caseaich = case_when(
    change_in_share < -0.12 ~ 1,
    change_in_share > -0.12 & change_in_share <= 0 ~ 2,
    change_in_share > 0 & change_in_share < 0.09 ~ 3,
    change_in_share > 0.09 & change_in_share < 0.24 ~ 4,
    change_in_share > 0.24 & change_in_share < 0.57 ~ 5,
    change_in_share > 0.57 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- COUNTY SHAPEFILES ----
options(tigris_use_cache = TRUE)
counties <- suppressMessages(
  tigris::counties(cb = TRUE, year = 2020, class = "sf")
) %>%
  mutate(COUNTY_FIPS = GEOID) %>%
  filter(!str_starts(COUNTY_FIPS, "72")) %>%
  st_transform(crs = 4326)

# ---- PANEL A MAP JOIN ----
map_data_a <- counties %>%
  left_join(merged_data_lev, by = c("COUNTY_FIPS" = "fips")) %>%
  tigris::shift_geometry()

# ---- PANEL B MAP JOIN (with Alaska color fix) ----
# Fix Alaska merge issue before shifting
ak_data <- merged_data_ch %>%
  filter(str_starts(fips, "02")) %>%
  distinct(fips, .keep_all = TRUE)

map_data_b <- counties %>%
  left_join(merged_data_ch, by = c("COUNTY_FIPS" = "fips"))

map_data_b[map_data_b$STATEFP == "02", names(ak_data)[-1]] <- 
  ak_data[match(map_data_b$COUNTY_FIPS[map_data_b$STATEFP == "02"], ak_data$fips),
          names(ak_data)[-1]]

# Shift after joining (fixes Alaska colors)
map_data_b <- tigris::shift_geometry(map_data_b)

# ---- LABELS AND COLORS ----
map_data_a <- map_data_a %>%
  mutate(
    avg_bin = case_when(
      caseai == 1 ~ "0 – 0.06",
      caseai == 2 ~ "0.06 – 0.14",
      caseai == 3 ~ "0.14 – 0.23",
      caseai == 4 ~ "0.23 – 0.37",
      caseai == 5 ~ "0.37 – 0.71",
      caseai == 6 ~ "0.71 – 10",
      TRUE ~ "No data"
    )
  )

map_data_b <- map_data_b %>%
  mutate(
    chg_bin = case_when(
      caseaich == 1 ~ "−5.56 – −0.12",
      caseaich == 2 ~ "−0.12 – 0",
      caseaich == 3 ~ "0 – 0.09",
      caseaich == 4 ~ "0.09 – 0.24",
      caseaich == 5 ~ "0.24 – 0.57",
      caseaich == 6 ~ "0.57 – 12.35",
      TRUE ~ "No data"
    )
  )

levels_avg_display <- c("0.71 – 10", "0.37 – 0.71", "0.23 – 0.37",
                        "0.14 – 0.23", "0.06 – 0.14", "0 – 0.06", "No data")
levels_chg_display <- c("0.57 – 12.35", "0.24 – 0.57", "0.09 – 0.24",
                        "0 – 0.09", "−0.12 – 0", "−5.56 – −0.12", "No data")

colors_avg_display <- c("#800026", "#e31a1c", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")
colors_chg_display <- c("#800026", "#fc4e2a", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")

map_data_a$avg_bin <- factor(map_data_a$avg_bin, levels = levels_avg_display)
map_data_b$chg_bin <- factor(map_data_b$chg_bin, levels = levels_chg_display)

# ---- THEME ----
map_theme <- theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 20, margin = margin(t = 3, b = 3, l = 1, r = 1)),
    legend.title = element_blank(),
    legend.key.width = unit(1.8, "cm"),
    legend.key.height = unit(0.6, "cm"),
    legend.spacing.x = unit(0.2, "cm"),
    legend.spacing.y = unit(0.1, "cm"),
    legend.margin = margin(t = 10, b = 5),
    legend.key = element_rect(color = "black", size = 0.5),
    plot.margin = margin(10, 10, 25, 10, "pt"),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.border = element_rect(color = "black", fill = NA, size = 0.5)
  )

# ---- PLOTS ----
p1 <- ggplot(map_data_a) +
  geom_sf(aes(fill = avg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_avg_display, levels_avg_display),
                    breaks = levels_avg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_a), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel A. Average AI Intensity (2014-2023)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

p2 <- ggplot(map_data_b) +
  geom_sf(aes(fill = chg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_chg_display, levels_chg_display),
                    breaks = levels_chg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_b), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel B. Percentage point change in AI Intensity (2018–2023)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

# ---- FINAL COMBINED PLOT ----
final_plot <- (p1 | p2) +
  plot_layout(widths = c(1, 1)) &
  theme(plot.background = element_rect(fill = "white", color = NA))

# Add overall title
final_plot <- final_plot +
  plot_annotation(
    title = "Figure 1: Replication of Andreadis et al. (2025) - Spatial Heterogeneity in the Share of and Change of AI Jobs",
    theme = theme(plot.title = element_text(size = 26, hjust = 0.5, margin = margin(b = 15)))
  )

final_plot
```

### Figure 1
Figure 1 displays the spatial distribution and evolution of AI intensity across U.S. counties from 2014 to 2023. Panel A shows that AI intensity is highly concentrated in a small number of coastal metropolitan counties, with most rural and inland counties falling in the 0–0.14% range. Panel B shows that the highest growth in AI intensity between 2018 and 2023 did not occur in established tech hubs, and that median growth of 0.088 percentage points masks substantial heterogeneity across counties.

We assess robustness by re-estimating AKCLM's preferred specifications weighted by log county population. Of the 11 significant coefficients under equal weighting across both dependent variables, 8 remain significant under log-population weighting. The core findings are robust: bachelor's share, STEM degree share, and manufacturing intensity remain significant predictors of AI intensity levels, and STEM degree share remains significant for AI intensity growth. Labor market tightness, however, loses significance in the levels specification under population weighting, suggesting that its estimated effect is driven disproportionately by small counties.

## Extension: Log-Population Weighting Analysis

To assess robustness, we re-estimate all models using log-population weights, omitting labor market tightness due to the denominator contamination problem described above. Log-population weights give more weight to populous counties relative to equal weighting, where each county receives the same weight regardless of population size.

```{r}
#| label: fig-table1-coefs-models1-3
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 1 from Andreadis et al. (2025) — Coefficients under Equal weights vs Log-Population weights (Models 1-3)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 10

library(ggplot2)
library(dplyr)
library(forcats)
library(patchwork)

# Run equal-weighted regressions (no weights) for comparison (Models 1-3)
est_demog_no <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

est_innovation_no <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

est_industry_no <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS"
)

# Run log-population weighted regressions (Models 1-3) - excluding tightness due to denominator contamination
est_demog_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_innovation_logpop <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_industry_logpop <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

models <- c("Demographics", "Innovation", "Industry")
variables <- c(
  "Bachelor's share", "Labor Tightness", "Patents per emp.",
  "STEM share", "Manufacturing intensity", "ICT intensity"
)

variables_list <- list(
  c("Bachelor's share", "House price growth"),
  c("Patents per emp.", "STEM share"),
  c("Manufacturing intensity", "ICT intensity", "Turnover rate")
)

# Extract coefficients and SEs from original (equal-weighted) regressions (Models 1-3)
coefs_orig_list <- list(
  c(coef(est_demog_no)["share_bac"], coef(est_demog_no)["hpi_ch"]),
  c(coef(est_innovation_no)["pat_intensity"], coef(est_innovation_no)["stemshare"]),
  c(coef(est_industry_no)["manuf_intensity"], coef(est_industry_no)["information_intensity"], coef(est_industry_no)["TurnOvrS"])
)

ses_orig_list <- list(
  c(se(est_demog_no)["share_bac"], se(est_demog_no)["hpi_ch"]),
  c(se(est_innovation_no)["pat_intensity"], se(est_innovation_no)["stemshare"]),
  c(se(est_industry_no)["manuf_intensity"], se(est_industry_no)["information_intensity"], se(est_industry_no)["TurnOvrS"])
)

# Extract coefficients and SEs from log-pop weighted regressions (Models 1-3) - tightness excluded
coefs_log_list <- list(
  c(coef(est_demog_logpop)["share_bac"], coef(est_demog_logpop)["hpi_ch"]),
  c(coef(est_innovation_logpop)["pat_intensity"], coef(est_innovation_logpop)["stemshare"]),
  c(coef(est_industry_logpop)["manuf_intensity"], coef(est_industry_logpop)["information_intensity"], coef(est_industry_logpop)["TurnOvrS"])
)

ses_log_list <- list(
  c(se(est_demog_logpop)["share_bac"], se(est_demog_logpop)["hpi_ch"]),
  c(se(est_innovation_logpop)["pat_intensity"], se(est_innovation_logpop)["stemshare"]),
  c(se(est_industry_logpop)["manuf_intensity"], se(est_industry_logpop)["information_intensity"], se(est_industry_logpop)["TurnOvrS"])
)

make_df <- function(model_index) {
  vars <- variables_list[[model_index]]
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_log_list[[model_index]],
      SE = ses_log_list[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_orig_list[[model_index]],
      SE = ses_orig_list[[model_index]],
      Scheme = "Log-Population Weights"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plot function with better styling
plots <- lapply(1:3, function(i) {
  df <- make_df(i)

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL) +
    theme_minimal(base_size = 18) +
    theme(
      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20"),
      legend.margin = margin(t = 10),
      legend.box.spacing = unit(0.5, "cm")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.6, 0.6)))
})

# Add titles directly to the plots instead of separate label objects
plots_with_tags <- lapply(1:3, function(i) {
  df <- make_df(i)

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models[i]) +
    theme_minimal(base_size = 18) +
    theme(
      # Tag styling (panel labels)
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 0.98),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 10, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20"),
      legend.margin = margin(t = 10),
      legend.box.spacing = unit(0.5, "cm")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.6, 0.6)))
})

# Simple vertical arrangement
final <- plots_with_tags[[1]] / plots_with_tags[[2]] / plots_with_tags[[3]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final
```

*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 1–3 of Table 1. These models examine AI intensity as the outcome variable. Model 1 (Demographics) includes bachelor's share, house price growth, and labor market tightness. Model 2 (Innovation) includes patents per employee and STEM degree share. Model 3 (Industry) includes manufacturing intensity, ICT intensity, and turnover rate. All models include county and year fixed effects. Labor market tightness is omitted from log-population-weighted models due to denominator contamination. All variables are standardized, so coefficients represent the change in AI intensity in percentage points associated with a one-standard-deviation increase in each predictor, holding other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates and red points indicate log-population-weighted estimates.

```{r}
#| label: fig-table1-coefs-models4-5
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 1 from Andreadis et al. (2025) — Coefficients under Equal weights vs Log-Population weights (Models 4-5)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 12

# Run equal-weighted regressions (no weights) for comparison (Models 4-5)
est_all <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS"
)

est_all_state_year <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway"
)

# Run log-population weighted regressions (Models 4-5) - excluding tightness due to denominator contamination
est_all_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

est_all_state_year_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway",
  weights = ~logpop_raw
)

models_45 <- c("All Controls", "All + State FE")
variables_45 <- c(
  "Bachelor's share", "House price growth",
  "Patents per emp.", "STEM share", "ICT intensity", "Manufacturing intensity", "Turnover rate"
)

variables_list_45 <- list(
  variables_45,
  variables_45
)

# Extract coefficients and SEs from original (equal-weighted) regressions (Models 4-5)
coefs_orig_list_45 <- list(
  c(coef(est_all)["share_bac"], coef(est_all)["hpi_ch"],
    coef(est_all)["pat_intensity"], coef(est_all)["stemshare"],
    coef(est_all)["information_intensity"], coef(est_all)["manuf_intensity"], coef(est_all)["TurnOvrS"]),
  c(coef(est_all_state_year)["share_bac"], coef(est_all_state_year)["hpi_ch"],
    coef(est_all_state_year)["pat_intensity"],
    coef(est_all_state_year)["stemshare"], coef(est_all_state_year)["information_intensity"],
    coef(est_all_state_year)["manuf_intensity"], coef(est_all_state_year)["TurnOvrS"])
)

ses_orig_list_45 <- list(
  c(se(est_all)["share_bac"], se(est_all)["hpi_ch"],
    se(est_all)["pat_intensity"], se(est_all)["stemshare"],
    se(est_all)["information_intensity"], se(est_all)["manuf_intensity"], se(est_all)["TurnOvrS"]),
  c(se(est_all_state_year)["share_bac"], se(est_all_state_year)["hpi_ch"],
    se(est_all_state_year)["pat_intensity"],
    se(est_all_state_year)["stemshare"], se(est_all_state_year)["information_intensity"],
    se(est_all_state_year)["manuf_intensity"], se(est_all_state_year)["TurnOvrS"])
)

# Extract coefficients and SEs from log-pop weighted regressions (Models 4-5) - tightness excluded
coefs_log_list_45 <- list(
  c(coef(est_all_logpop)["share_bac"], coef(est_all_logpop)["hpi_ch"],
    coef(est_all_logpop)["pat_intensity"],
    coef(est_all_logpop)["stemshare"], coef(est_all_logpop)["information_intensity"],
    coef(est_all_logpop)["manuf_intensity"], coef(est_all_logpop)["TurnOvrS"]),
  c(coef(est_all_state_year_logpop)["share_bac"], coef(est_all_state_year_logpop)["hpi_ch"],
    coef(est_all_state_year_logpop)["pat_intensity"],
    coef(est_all_state_year_logpop)["stemshare"], coef(est_all_state_year_logpop)["information_intensity"],
    coef(est_all_state_year_logpop)["manuf_intensity"], coef(est_all_state_year_logpop)["TurnOvrS"])
)

ses_log_list_45 <- list(
  c(se(est_all_logpop)["share_bac"], se(est_all_logpop)["hpi_ch"],
    se(est_all_logpop)["pat_intensity"],
    se(est_all_logpop)["stemshare"], se(est_all_logpop)["information_intensity"],
    se(est_all_logpop)["manuf_intensity"], se(est_all_logpop)["TurnOvrS"]),
  c(se(est_all_state_year_logpop)["share_bac"], se(est_all_state_year_logpop)["hpi_ch"],
    se(est_all_state_year_logpop)["pat_intensity"],
    se(est_all_state_year_logpop)["stemshare"], se(est_all_state_year_logpop)["information_intensity"],
    se(est_all_state_year_logpop)["manuf_intensity"], se(est_all_state_year_logpop)["TurnOvrS"])
)

make_df_45 <- function(model_index) {
  vars <- variables_list_45[[model_index]]
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_log_list_45[[model_index]],
      SE = ses_log_list_45[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_orig_list_45[[model_index]],
      SE = ses_orig_list_45[[model_index]],
      Scheme = "Log-Population Weights"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plots for models 4-5
plots_45 <- lapply(1:2, function(i) {
  df <- make_df_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL) +
    theme_minimal(base_size = 18) +
    theme(
      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.4, 0.4)))
})

# Enhanced plots for models 4-5 with panel tags
plots_45_with_tags <- lapply(1:2, function(i) {
  df <- make_df_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models_45[i]) +
    theme_minimal(base_size = 18) +
    theme(
      # Tag styling (panel labels)
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 1.03),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins and spacing
      plot.margin = margin(t = 10, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236"),
      breaks = c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.4, 0.4)))
})

# Simple vertical arrangement for models 4-5
final_45 <- plots_45_with_tags[[1]] / plots_45_with_tags[[2]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final_45
```

*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 4–5 of Table 1. These models examine AI intensity as the outcome variable. Model 4 (All Controls) includes all demographic, innovation, and industry variables with county and year fixed effects. Model 5 (All + State FE) replaces year fixed effects with state-year fixed effects. Both models include bachelor's share, house price growth, labor market tightness, patents per employee, STEM degree share, ICT intensity, manufacturing intensity, and turnover rate. Labor market tightness is omitted from log-population-weighted models due to denominator contamination. All variables are standardized, so coefficients represent the change in AI intensity in percentage points associated with a one-standard-deviation increase in each predictor, holding all other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates and red points indicate log-population-weighted estimates.

In Model 4, coefficient estimates remain stable across weighting schemes. Bachelor's share is associated with approximately a 0.01 percentage point increase in AI intensity per standard deviation, while house price growth shows minimal independent effect. Labor market tightness maintains a positive association of roughly 0.08 percentage points per standard deviation. Among innovation variables, patents per employee shows approximately a 0.05 percentage point increase and STEM degree share shows roughly a 0.09 percentage point increase per standard deviation. Among industry variables, manufacturing intensity is associated with approximately a 0.03 percentage point decrease, ICT intensity with a 0.12 percentage point increase, and turnover rate with the largest effect of approximately 0.18 percentage points per standard deviation. These coefficients remain nearly identical under both weighting schemes, suggesting that the associations between education, innovation, industry composition, and AI intensity hold across the county size distribution rather than being driven by large metropolitan counties. Turnover rate is the strongest predictor (0.18 percentage points), followed by ICT intensity (0.12 percentage points) and STEM degree share (0.09 percentage points), while bachelor's share shows the smallest independent effect (0.01 percentage points).


```{r}
#| label: fig-table2-coefs-models1-3
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 2 from Andreadis et al. (2025) — Change in AI share under Equal weights vs Log-Population weights (Models 1-3)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 10

# Prepare data for Table 2 regressions (growth models) - use data_ai_l_z that's already prepared
data_t2_z <- data_ai_l_z %>%
  filter(emp != 0, dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14) %>%
  mutate(
    # Save raw values for weighting
    logpop_raw = logpop,
    lads14_raw = exp(logpop14)  # Convert back from z-score approximation
  )

# Run equal-weighted regressions for Table 2 Models 1-3 (NO fixed effects, just OLS)
est_t2_demog_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + tightness14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_innovation_no <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + stemshare14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_industry_no <- fixest::feols(
  "dai_intensity9 ~ manuf_intensity14 + information_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

# Run population weighted regressions for Table 2 Models 1-3 - excluding tightness due to denominator contamination
est_t2_demog_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)  # Use actual population (exp of log population)
)

est_t2_innovation_logpop <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + stemshare14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

est_t2_industry_logpop <- fixest::feols(
  "dai_intensity9 ~ manuf_intensity14 + information_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

models <- c("Demographics", "Innovation", "Industry")

variables_list <- list(
  c("Bachelors Share", "House Price Growth"),
  c("Patents per emp.", "STEM Degrees' share"),
  c("Manufacturing Intensity %", "ICT sector Intensity %", "Turnover Rate %")
)

# Extract coefficients from actual (equal-weighted) regressions
coefs_actual_list <- list(
  c(coef(est_t2_demog_no)["share_bac14"], coef(est_t2_demog_no)["hpi_ch14"]),
  c(coef(est_t2_innovation_no)["pat_intensity14"], coef(est_t2_innovation_no)["stemshare14"]),
  c(coef(est_t2_industry_no)["manuf_intensity14"], coef(est_t2_industry_no)["information_intensity14"], coef(est_t2_industry_no)["TurnOvrS14"])
)

ses_actual_list <- list(
  c(se(est_t2_demog_no)["share_bac14"], se(est_t2_demog_no)["hpi_ch14"]),
  c(se(est_t2_innovation_no)["pat_intensity14"], se(est_t2_innovation_no)["stemshare14"]),
  c(se(est_t2_industry_no)["manuf_intensity14"], se(est_t2_industry_no)["information_intensity14"], se(est_t2_industry_no)["TurnOvrS14"])
)

# Extract coefficients from log-pop weighted regressions - tightness excluded
coefs_logpop_list <- list(
  c(coef(est_t2_demog_logpop)["share_bac14"], coef(est_t2_demog_logpop)["hpi_ch14"]),
  c(coef(est_t2_innovation_logpop)["pat_intensity14"], coef(est_t2_innovation_logpop)["stemshare14"]),
  c(coef(est_t2_industry_logpop)["manuf_intensity14"], coef(est_t2_industry_logpop)["information_intensity14"], coef(est_t2_industry_logpop)["TurnOvrS14"])
)

ses_logpop_list <- list(
  c(se(est_t2_demog_logpop)["share_bac14"], se(est_t2_demog_logpop)["hpi_ch14"]),
  c(se(est_t2_innovation_logpop)["pat_intensity14"], se(est_t2_innovation_logpop)["stemshare14"]),
  c(se(est_t2_industry_logpop)["manuf_intensity14"], se(est_t2_industry_logpop)["information_intensity14"], se(est_t2_industry_logpop)["TurnOvrS14"])
)

# Andreadis et al. (2025) bachelor's share coefficient from the paper
coefs_andreadis_bac <- 0.0022

make_df <- function(model_index) {
  vars <- variables_list[[model_index]]

  # For Model 1 (Demographics), include Andreadis bachelor's share as a third scheme
  if (model_index == 1) {
    bind_rows(
      data.frame(
        Variable = vars,
        Coef = coefs_logpop_list[[model_index]],
        SE = ses_logpop_list[[model_index]],
        Scheme = "Equal Weights"
      ),
      data.frame(
        Variable = vars,
        Coef = coefs_actual_list[[model_index]],
        SE = ses_actual_list[[model_index]],
        Scheme = "Log-Population Weights"
      ),
      data.frame(
        Variable = "Bachelors Share",
        Coef = coefs_andreadis_bac,
        SE = ses_actual_list[[model_index]][1],
        Scheme = "Andreadis et al. (2025)"
      )
    ) %>%
      mutate(
        lower = Coef - 1.96 * SE,
        upper = Coef + 1.96 * SE,
        Variable = fct_rev(factor(Variable, levels = vars)),
        Scheme = factor(Scheme, levels = c("Andreadis et al. (2025)", "Log-Population Weights", "Equal Weights"))
      )
  } else {
    bind_rows(
      data.frame(
        Variable = vars,
        Coef = coefs_logpop_list[[model_index]],
        SE = ses_logpop_list[[model_index]],
        Scheme = "Equal Weights"
      ),
      data.frame(
        Variable = vars,
        Coef = coefs_actual_list[[model_index]],
        SE = ses_actual_list[[model_index]],
        Scheme = "Log-Population Weights"
      )
    ) %>%
      mutate(
        lower = Coef - 1.96 * SE,
        upper = Coef + 1.96 * SE,
        Variable = fct_rev(factor(Variable, levels = vars)),
        Scheme = factor(Scheme, levels = c("Log-Population Weights", "Equal Weights"))
      )
  }
}

# Enhanced plots for Table 2 with integrated tags
plots_t2_with_tags <- lapply(1:3, function(i) {
  df <- make_df(i)
  n_vars <- length(unique(df$Variable))
  y_expand <- if(n_vars == 2) c(0.8, 0.8) else c(0.5, 0.5)

  # Determine which levels exist in this plot
  existing_levels <- levels(df$Scheme)
  all_colors <- c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236",
                  "Andreadis et al. (2025)" = "#2E86AB")
  # Filter colors to only include existing levels
  plot_colors <- all_colors[names(all_colors) %in% existing_levels]

  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.5, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.2, linewidth = 1.2, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models[i]) +
    theme_minimal(base_size = 12) +
    theme(
      # Tag styling
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 0.98),

      # Y-axis styling
      axis.text.y = element_text(size = 13, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = plot_colors,
      breaks = if(i == 1) c("Equal Weights", "Log-Population Weights", "Andreadis et al. (2025)") else c("Equal Weights", "Log-Population Weights")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = y_expand))
})

# Simple vertical arrangement for Table 2 - remove legends from plots 2 and 3
plots_t2_with_tags[[2]] <- plots_t2_with_tags[[2]] + theme(legend.position = "none")
plots_t2_with_tags[[3]] <- plots_t2_with_tags[[3]] + theme(legend.position = "none")

final <- plots_t2_with_tags[[1]] / plots_t2_with_tags[[2]] / plots_t2_with_tags[[3]]

# Override to ensure single unified legend from plot 1 only
final <- final &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final
```

*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 1–3 of Table 2. These models examine the change in AI intensity between 2017–2018 and 2022–2023 as the outcome variable. Model 1 (Demographics) includes bachelor's share, house price growth, and labor market tightness. Model 2 (Innovation) includes patents per employee and STEM degree share. Model 3 (Industry) includes manufacturing intensity, ICT intensity, and turnover rate. All predictors are measured in 2017, the base period before the growth window. All variables are standardized, so coefficients represent the change in AI intensity growth in percentage points associated with a one-standard-deviation increase in each predictor. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates, red points indicate log-population-weighted estimates, and blue points show the published bachelor's share coefficient from AKCLM for comparison.

```{r}
#| label: fig-table2-coefs-models4-5
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Extension of Table 2 from Andreadis et al. (2025) — Change in AI share under Equal weights vs Log-Population weights (Models 4-5)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 14
#| fig-height: 14

# Run equal-weighted regressions for Table 2 Models 4-5 (NO fixed effects)
est_t2_all_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + tightness14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

est_t2_all_state_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + tightness14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS"
)

# Run population weighted regressions for Table 2 Models 4-5 - excluding tightness due to denominator contamination
est_t2_all_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

est_t2_all_state_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + hpi_ch14 + pat_intensity14 + stemshare14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_t2_z,
  cluster = "COUNTY_FIPS",
  weights = ~exp(logpop_raw)
)

models_t2_45 <- c("All Controls", "All + State FE")

variables_list_t2_45 <- list(
  c("Bachelors Share", "House Price Growth", "Patents per emp.", "STEM Degrees' share",
    "ICT sector Intensity %", "Manufacturing Intensity %", "Turnover Rate %"),
  c("Bachelors Share", "House Price Growth", "Patents per emp.", "STEM Degrees' share",
    "ICT sector Intensity %", "Manufacturing Intensity %", "Turnover Rate %")
)

# Extract coefficients from actual (equal-weighted) regressions - Models 4-5
coefs_actual_t2_45 <- list(
  c(coef(est_t2_all_no)["share_bac14"], coef(est_t2_all_no)["hpi_ch14"],
    coef(est_t2_all_no)["pat_intensity14"],
    coef(est_t2_all_no)["stemshare14"], coef(est_t2_all_no)["information_intensity14"],
    coef(est_t2_all_no)["manuf_intensity14"], coef(est_t2_all_no)["TurnOvrS14"]),
  c(coef(est_t2_all_state_no)["share_bac14"], coef(est_t2_all_state_no)["hpi_ch14"],
    coef(est_t2_all_state_no)["pat_intensity14"],
    coef(est_t2_all_state_no)["stemshare14"], coef(est_t2_all_state_no)["information_intensity14"],
    coef(est_t2_all_state_no)["manuf_intensity14"], coef(est_t2_all_state_no)["TurnOvrS14"])
)

ses_actual_t2_45 <- list(
  c(se(est_t2_all_no)["share_bac14"], se(est_t2_all_no)["hpi_ch14"],
    se(est_t2_all_no)["pat_intensity14"],
    se(est_t2_all_no)["stemshare14"], se(est_t2_all_no)["information_intensity14"],
    se(est_t2_all_no)["manuf_intensity14"], se(est_t2_all_no)["TurnOvrS14"]),
  c(se(est_t2_all_state_no)["share_bac14"], se(est_t2_all_state_no)["hpi_ch14"],
    se(est_t2_all_state_no)["pat_intensity14"],
    se(est_t2_all_state_no)["stemshare14"], se(est_t2_all_state_no)["information_intensity14"],
    se(est_t2_all_state_no)["manuf_intensity14"], se(est_t2_all_state_no)["TurnOvrS14"])
)

# Extract coefficients from log-pop weighted regressions - tightness excluded
coefs_logpop_t2_45 <- list(
  c(coef(est_t2_all_logpop)["share_bac14"], coef(est_t2_all_logpop)["hpi_ch14"],
    coef(est_t2_all_logpop)["pat_intensity14"],
    coef(est_t2_all_logpop)["stemshare14"], coef(est_t2_all_logpop)["information_intensity14"],
    coef(est_t2_all_logpop)["manuf_intensity14"], coef(est_t2_all_logpop)["TurnOvrS14"]),
  c(coef(est_t2_all_state_logpop)["share_bac14"], coef(est_t2_all_state_logpop)["hpi_ch14"],
    coef(est_t2_all_state_logpop)["pat_intensity14"],
    coef(est_t2_all_state_logpop)["stemshare14"], coef(est_t2_all_state_logpop)["information_intensity14"],
    coef(est_t2_all_state_logpop)["manuf_intensity14"], coef(est_t2_all_state_logpop)["TurnOvrS14"])
)

ses_logpop_t2_45 <- list(
  c(se(est_t2_all_logpop)["share_bac14"], se(est_t2_all_logpop)["hpi_ch14"],
    se(est_t2_all_logpop)["pat_intensity14"],
    se(est_t2_all_logpop)["stemshare14"], se(est_t2_all_logpop)["information_intensity14"],
    se(est_t2_all_logpop)["manuf_intensity14"], se(est_t2_all_logpop)["TurnOvrS14"]),
  c(se(est_t2_all_state_logpop)["share_bac14"], se(est_t2_all_state_logpop)["hpi_ch14"],
    se(est_t2_all_state_logpop)["pat_intensity14"],
    se(est_t2_all_state_logpop)["stemshare14"], se(est_t2_all_state_logpop)["information_intensity14"],
    se(est_t2_all_state_logpop)["manuf_intensity14"], se(est_t2_all_state_logpop)["TurnOvrS14"])
)

# Andreadis et al. (2025) bachelor's share coefficients
coefs_andreadis_t2_45_bac <- c(-0.0035, -0.0044)  # Models 4 and 5

make_df_t2_45 <- function(model_index) {
  vars <- variables_list_t2_45[[model_index]]

  # Include Andreadis bachelor's share as third scheme
  bind_rows(
    data.frame(
      Variable = vars,
      Coef = coefs_logpop_t2_45[[model_index]],
      SE = ses_logpop_t2_45[[model_index]],
      Scheme = "Equal Weights"
    ),
    data.frame(
      Variable = vars,
      Coef = coefs_actual_t2_45[[model_index]],
      SE = ses_actual_t2_45[[model_index]],
      Scheme = "Log-Population Weights"
    ),
    data.frame(
      Variable = "Bachelors Share",
      Coef = coefs_andreadis_t2_45_bac[model_index],
      SE = ses_actual_t2_45[[model_index]][1],
      Scheme = "Andreadis et al. (2025)"
    )
  ) %>%
    mutate(
      lower = Coef - 1.96 * SE,
      upper = Coef + 1.96 * SE,
      Variable = fct_rev(factor(Variable, levels = vars)),
      Scheme = factor(Scheme, levels = c("Andreadis et al. (2025)", "Log-Population Weights", "Equal Weights"))
    )
}

# Enhanced plots for models 4-5 (Table 2) with integrated tags
plots_t2_45_with_tags <- lapply(1:2, function(i) {
  df <- make_df_t2_45(i)
  ggplot(df, aes(x = Coef, y = Variable, color = Scheme)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6, color = "gray50", size = 0.7) +
    geom_point(position = position_dodge(width = 0.5), size = 3.2, alpha = 0.9) +
    geom_errorbarh(aes(xmin = lower, xmax = upper),
                   position = position_dodge(width = 0.5),
                   height = 0.15, linewidth = 1.1, alpha = 0.8) +
    labs(x = "Coefficient", y = NULL, tag = models_t2_45[i]) +
    theme_minimal(base_size = 12) +
    theme(
      # Tag styling
      plot.tag = element_text(size = 14, face = "bold", color = "gray15", hjust = 0),
      plot.tag.position = c(0.01, 1.03),

      # Y-axis styling
      axis.text.y = element_text(size = 12, color = "gray20", margin = margin(r = 12)),
      axis.text.x = element_text(size = 11, color = "gray30"),
      axis.title.x = element_text(size = 13, color = "gray20", margin = margin(t = 15)),

      # Panel styling
      panel.grid.major.y = element_line(color = "gray90", size = 0.3),
      panel.grid.major.x = element_line(color = "gray95", size = 0.3),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),

      # Plot margins
      plot.margin = margin(t = 20, r = 15, b = 15, l = 20),

      # Legend styling
      legend.text = element_text(size = 12, color = "gray20")
    ) +
    scale_color_manual(
      values = c("Equal Weights" = "#28A745", "Log-Population Weights" = "#F24236",
                 "Andreadis et al. (2025)" = "#2E86AB"),
      breaks = c("Equal Weights", "Log-Population Weights", "Andreadis et al. (2025)")
    ) +
    scale_x_continuous(
      breaks = seq(-0.2, 0.4, by = 0.1),
      limits = c(-0.25, 0.45),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    scale_y_discrete(expand = expansion(add = c(0.3, 0.3)))
})

# Simple vertical arrangement for Table 2, models 4-5
final_t2_45 <- plots_t2_45_with_tags[[1]] / plots_t2_45_with_tags[[2]] +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 13, color = "gray20"),
    legend.margin = margin(t = 20)
  )

final_t2_45
```

*Notes:* This figure compares coefficient estimates from equal-weighted regressions versus log-population-weighted regressions for Models 4–5 of Table 2. These models examine the change in AI intensity between 2017–2018 and 2022–2023 as the outcome variable. Model 4 (All Controls) includes all demographic, innovation, and industry variables with no fixed effects. Model 5 (All + State FE) adds state fixed effects to Model 4. All predictors are measured in 2017, the base period before the growth window. All variables are standardized, so coefficients represent the change in AI intensity growth in percentage points associated with a one-standard-deviation increase in each predictor, holding all other variables constant. Confidence intervals represent 95% levels. Green points indicate equal-weighted estimates, red points indicate log-population-weighted estimates, and blue points show the published bachelor's share coefficients from AKCLM for comparison.


In the fully specified Model 4, bachelor's share shows a small negative association with the growth of AI intensity under both weighting schemes, suggesting that counties with higher educational attainment in 2017 already had higher baseline AI intensity, leaving less room for growth. House price growth shows minimal independent effect. Labor market tightness maintains a positive association of approximately 0.09–0.10 percentage points per standard deviation across both weighting schemes. Among innovation variables, patents per employee declines from 0.06 percentage points under equal weights to 0.04 under log-population weights (a 33% reduction), while STEM degree share declines from 0.08 to 0.05 percentage points (a 38% reduction). Among industry variables, manufacturing intensity shows a negative association of approximately 0.03–0.04 percentage points, ICT intensity declines from 0.12 to 0.07 percentage points (a 42% reduction), and turnover rate — the largest predictor — declines from 0.17–0.18 to 0.11 percentage points (a 39% reduction). The consistent 40% magnitude reductions across innovation and industry variables suggest that these associations are stronger in smaller counties, while labor market tightness shows the most stable association across the county size distribution.

### Results

The comparison between equal-weighted and log-population-weighted regressions reveals several patterns. For the level of AI intensity, bachelor's share decreases by approximately 25% under log-population weights (from 0.227 to 0.182), suggesting that the relationship between educational attainment and AI intensity is stronger in smaller counties. ICT intensity shows the largest increase, growing by approximately 53% under log-population weights (from 0.012 to 0.026). Patents per employee and manufacturing intensity grow by approximately 17% and 21% respectively, while turnover rate decreases by approximately 39% (from 0.026 to 0.019). STEM degree share shows the most stability, changing by only 13%. Labor market tightness is omitted from the log-population weighted models due to denominator contamination. Overall, the direction of associations is preserved across weighting schemes, but the magnitudes shift in ways that suggest some relationships are stronger in larger counties while others are stronger in smaller counties.

## Critical Assessment of Causal Language

AKCLM employ language suggesting causal relationships despite using observational county-level data with fixed-effects regressions. The empirical strategy does not support causal inference [@holland1986], yet the paper uses terminology that implies causation rather than correlation. Causal nouns such as "drivers," "determinants," "effects," and "impact" appear throughout, alongside causal verbs such as "drive," "fostering," and "influence." For instance, the paper refers to "key drivers of AI job intensity" and states that labor market tightness "emerges as a key driver," implying that changing these variables would directly alter AI adoption. The conclusion states that findings "point to the role of place-based policies," making policy recommendations based on associations rather than identified causal effects. The fixed-effects specification controls for time-invariant county characteristics and common time trends, but cannot address reverse causality, omitted time-varying confounds, or selection processes [@holland1986].

## Conclusion

This replication of AKCLM confirms that local labor market conditions, human capital, and innovation capacity are correlated with AI intensity across U.S. counties. Our analysis highlights three qualifications to their conclusions.
First, AKCLM employ causal language that overstates what the empirical design can support. Terms such as "drivers" and "determinants" suggest causal mechanisms, but fixed-effects regressions can only document conditional correlations. Without exogenous variation or quasi-experimental identification [@holland1986], these patterns likely reflect some combination of causal effects, reverse causality, and selection.

Second, several associations are sensitive to the weighting scheme. Labor market tightness is the most stable correlate across both outcomes and both weighting schemes. By contrast, ICT intensity shows the largest magnitude shift, declining by approximately 53% under log-population weights, while bachelor's share increases by approximately 25%, suggesting these relationships are not uniform across the county size distribution.

Third, the direction of all associations is preserved across weighting schemes, indicating that the core findings of AKCLM are reproducible. However, the magnitudes shift enough to caution against treating point estimates from the equal-weighted specification as representative of all counties.

More broadly, this replication underscores that modest changes in specification, such as alternative weighting schemes, can materially shift the interpretation of empirical results on technological change.


## Bibliography {.unnumbered}
