---
title: "Denominator Contamination in a Vacancy-Based Tightness Measure"
subtitle: "A Replication and Reanalysis of Andreadis et al. (AEA Papers and Proceedings, 2025)"
author:
  - name: Jacob Khaykin^[Solon High School, jacobkhaykin27@solonschools.net]
  - name: David Kane^[New College of Florida, dakane@ncf.edu]
bibliography: references.bib
csl: aea.csl
link-citations: true
nocite: '@*'
format:
  pdf:
    keep-tex: true
    number-sections: true
    documentclass: article
    geometry:
      - margin=1in
    include-in-header:
      - text: |
          \usepackage{url}
          \urlstyle{same}
          \def\UrlBreaks{\do/\do-\do.\do:}
          \usepackage{float}
          \usepackage{array}
          \usepackage{siunitx}
          \usepackage{dcolumn}
          \usepackage{tikz}
          \newcolumntype{d}[1]{D{.}{.}{#1}}
          % reset numbering after abstract
          \usepackage{etoolbox}
          \AtBeginEnvironment{abstract}{\setcounter{section}{0}}
          % Custom table row spacing
          \renewcommand{\arraystretch}{0.9}
          % Configure siunitx for modern versions (>=3)
          \sisetup{
            detect-all,
            input-symbols = (),
            input-signs = + -,
            table-align-text-pre = false,
            table-number-alignment = center,
            table-format = +1.4,
            group-digits = false,
            table-space-text-pre = ***,
            table-space-text-post = ***,
            mode = math
          }
---

```{r}
#| label: setup
#| include: false
# Load all required packages
library(tidyverse)
library(fixest)
library(modelsummary)
library(kableExtra)
library(scales)
library(ggplot2)
library(grid)
library(dplyr)
library(forcats)
library(dagitty)
```

*JEL: J24, O33, R11, C13*

*Keywords:* Artificial Intelligence, Regional Economics, Labor Markets

*Data Availability:* The R code and data to reproduce this replication are available in this repository.^[https://github.com/JacobKhay/Andreadis-Replication]

## Abstract {.unnumbered}

We identify denominator contamination in Andreadis et al. (2025)'s key labor-market tightness variable: total job postings appear in both the AI-intensity denominator and the tightness numerator. Denominator contamination occurs when a constructed regressor shares a numerator or denominator component with the dependent variable, creating mechanical correlation. In a calibrated simulation designed to mirror the panel’s dispersion, the contaminated specification produces a nonzero coefficient even when the AI rate is generated independently of unemployment. In the empirical reanalysis, the tightness coefficient is not separately identifiable from postings scale: once postings scale is separated from unemployment using decomposition or an offset-count model, the tightness signal largely disappears. We also compare alternative weighting schemes after removing tightness to assess sensitivity to the estimand. Our reanalysis indicates the associations are more modest than originally presented.

Declaration: There are no financial conflicts of interest to share.
\newpage

## Introduction

Artificial intelligence is reshaping labor demand and the geography of high-skill work, with county-level variation that matters for regional policy. Andreadis et al. (2025) provide one of the first systematic county-level accounts of AI job posting intensity and its growth over time, motivating place-based strategies and regional diagnostics.

Their headline results emphasize labor-market tightness and education. In the levels specification, tightness and bachelor's share are the largest positive correlates of AI job intensity. In the growth specification, STEM degree share and tightness are the strongest positive correlates. These patterns have been cited as evidence that AI posting intensity tends to be higher in counties with tighter labor markets and higher education.

However, the labor-market tightness variable suffers from denominator contamination [@kronmal1993spurious; @wooldridge2005]. Total postings appear in the denominator of AI intensity and the numerator of tightness, inducing mechanical correlation even under independence between AI postings and unemployment. As a result, the tightness coefficient partly reflects shared arithmetic structure rather than a purely economic relationship; because tightness is correlated with other covariates, its inclusion may also affect the remaining estimates.

We reproduce Tables 1 and 2, demonstrate the mechanical component using a DAG, a simple example, and a simulation, and then re-estimate the main specifications without the contaminated tightness variable. As a secondary check, we compare alternative weighting schemes (including log-population weights) after removing tightness to assess sensitivity to the estimand.
This is not a critique of tightness as a concept, but of using a tightness measure that reuses the dependent variable’s denominator, which mechanically inflates partial correlations.

## Data

AKCLM combine Lightcast postings data with county-level demographics from the American Community Survey, innovation measures from patents and STEM degree shares, industry composition from CBP and QWI, and house price growth. All explanatory variables are lagged by one year. The main outcome is AI job intensity, and the growth outcome is the change in AI intensity between pooled 2017-2018 and 2022-2023 averages.

The key variables are defined as follows. The AI intensity outcome is:
$$AI_{it} = \frac{\text{AI job postings}_{it}}{\text{Total job postings}_{it}} \times 100 \tag{1}$$
The tightness variable is:
$$Tightness_{it} = \frac{\text{Total postings}_{it}}{\text{Unemployed}_{it}} \tag{2}$$

Consider a library that reports the share of sci-fi books borrowed (sci-fi/total) and a "busyness" measure defined as total books borrowed divided by overdue books. Even if sci-fi borrowing is unrelated to overdue books, the shared total-borrowed term mechanically links the two ratios. The same arithmetic applies here: AI intensity divides by total postings while tightness multiplies by total postings.

This shared component can induce a mechanical correlation. Even if AI postings are generated independently of unemployment conditional on total postings, the shared total-postings term can generate nontrivial partial correlation between A/T and T/U once sampling noise and ratio variation interact with T. This is not universal (e.g., if A = pT with p independent, then A/T = p), so the magnitude and sign depend on the data-generating process. The corresponding construction diagram is:

```{r}
#| label: fig-dag
#| echo: false
#| fig-cap: "Construction diagram for denominator contamination"
#| fig-cap-location: top
#| fig-pos: "H"
dag <- dagitty("dag {
  AI_post -> AI_intensity [beta = 1]
  total_post -> AI_intensity [beta = -1]
  total_post -> tightness
  unemp -> tightness [beta = -1]
}")
coordinates(dag) <- list(
  x = c(AI_post = 0, total_post = 0, unemp = 0, AI_intensity = 1, tightness = 1),
  y = c(AI_post = 1, total_post = 0, unemp = -1, AI_intensity = 1, tightness = -1)
)
plot(dag)
```

## Replication

We reproduce Tables 1 and 2 using the authors' data.csv. Most coefficients and standard errors match the published tables exactly; one coefficient in Table 2 differs slightly, which likely reflects an undocumented preprocessing or default-setting difference. The denominator-contamination results do not depend on that discrepancy. The replication tables use the authors’ provided `data.csv`; Figure 1 uses an updated Lightcast extraction (`updated_lightcast_county.csv`) and Census shapefiles via `tigris` to reproduce the spatial visualization and is not required for the table replication. Connecticut has no county observations in the provided dataset, so it is shown as no data.

```{r}
#| label: tbl-table1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 1 from Andreadis et al. (2025) - The Correlates of the Share of Artificial Intelligence Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Load data
data_ai <- read_csv("data.csv") %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(ai_intensity = ai / nads)

# Prepare demographics
data_ai <- data_ai %>% 
  mutate(logincome = log(medhhincome), loghpi = log(hpi), logemp = log(pop_above18))

data_ai <- data_ai %>% 
  mutate(lads = log(1 + nads))

data_ai <- data_ai %>% 
  mutate(lads0 = log(nads))

# Log number of patents, inventors, etc.
data_ai <- data_ai %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai <- data_ai %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(pat_intensity = n_inventors / Employed, patai_intensity = ai_patents / n_patents) %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

# Industry structure
data_ai <- data_ai %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

data_ai <- data_ai %>% 
  mutate(information_intensity = replace_na(information_intensity, 0))

# Education variables
data_ai <- data_ai %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg),
    stemshare2 = (ustemdeg) / (udeg)
  )

data_ai <- data_ai %>%  
  mutate(stemshare = replace_na(stemshare, 0), stemshare2 = replace_na(stemshare2, 0))

# Labor market variables
data_ai <- data_ai %>%  
  mutate(tightness = nads / Unemployed)

data_ai <- data_ai %>%  
  mutate(hpi_ch = hpi_ch / 100)

# Z-scores - VERSION ROBUST with as.numeric()
data_ai_z <- data_ai %>%
  filter(emp != 0) %>%
  mutate(
    ai_raw = ai,         # Keep raw counts for count model
    nads_raw = nads,     # Keep raw postings for offset
    pop_raw = pop,        # Save raw population for weighting
    logpop_raw = logpop,  # Save raw log(pop) for weighting
    logemp_raw = logemp,  # Save raw log(employment) for weighting
    share_bac = as.numeric(scale(share_bac)),
    share_black = as.numeric(scale(share_black)),
    share_poverty = as.numeric(scale(share_poverty)),
    logpop = as.numeric(scale(logpop)),
    hpi_ch = as.numeric(scale(hpi_ch)),
    logincome = as.numeric(scale(logincome)),
    tightness = as.numeric(scale(tightness)),
    unrate = as.numeric(scale(unrate)),
    pat_intensity = as.numeric(scale(pat_intensity)),
    patai_intensity = as.numeric(scale(patai_intensity)),
    degshare = as.numeric(scale(degshare)),
    stemshare = as.numeric(scale(stemshare)),
    large_firms = as.numeric(scale(large_firms)),
    information_intensity = as.numeric(scale(information_intensity)),
    manuf_intensity = as.numeric(scale(manuf_intensity)),
    TurnOvrS = as.numeric(scale(TurnOvrS))
  ) %>%
  mutate(ai_intensity = ai_intensity * 100)

# Run regressions
est_demog_no <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_innovation_no <- fixest::feols(
  "ai_intensity ~ pat_intensity + patai_intensity + degshare + stemshare | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_industry_no <- fixest::feols(
  "ai_intensity ~ large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z %>% drop_na(share_bac, share_black, share_poverty, logpop, hpi_ch, logincome,
                        tightness, pat_intensity, patai_intensity, degshare, stemshare,
                        large_firms, information_intensity, manuf_intensity, TurnOvrS),
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

est_all_state_year <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | state_year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  vcov = "twoway",
  weights = ~lads
)

# Extract model statistics
models <- list(est_demog_no, est_innovation_no, est_industry_no, est_all, est_all_state_year)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.5f", r2(.x, "r2")))

# Create table footer
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, Year}", "{\\hspace{0.5em}County, state-year}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R²", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels
labels <- c(
  "share_bac" = "Bachelor's share",
  "hpi_ch" = "House price growth",
  "tightness" = "Labor tightness",
  "pat_intensity" = "Patents per employee",
  "stemshare" = "STEM degrees share",
  "information_intensity" = "ICT sector intensity",
  "manuf_intensity" = "Manufacturing",
  "TurnOvrS" = "Turnover rate"
)

# Create note text
table_notes <- paste(
  "This table examines the demographic, innovation, and industry determinants",
  "of the share of artificial intelligence jobs across U.S. counties from 2014 to 2023.",
  "The dependent variable is AI job intensity, defined as the ratio of AI job postings",
  "to total job postings in each county-year, multiplied by 100 to express in percentage terms.",
  "AI job postings are identified from Lightcast data using skills and keywords associated",
  "with artificial intelligence. All explanatory variables are standardized as z-scores",
  "to ensure comparability across predictors. The sample comprises county-year observations",
  "covering approximately 3,100 U.S. counties annually over the ten-year period.",
  "All coefficients represent percentage point changes in AI job share for a one standard",
  "deviation increase in the explanatory variable. Models are estimated using ordinary least",
  "squares with county and year fixed effects (columns 1-4) or county and state-year fixed",
  "effects (column 5). Standard errors are clustered at the county level. All explanatory",
  "variables are lagged by one year."
)

# Create the table
modelsummary(
  list(
    "(1)" = est_demog_no,
    "(2)" = est_innovation_no,
    "(3)" = est_industry_no,
    "(4)" = est_all,
    "(5)" = est_all_state_year
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = fmt_decimal(4),
  align = "lddddd",
  notes = table_notes
)

est_all_t1 <- est_all
est_demog_t1 <- est_demog_no
est_innovation_t1 <- est_innovation_no
est_industry_t1 <- est_industry_no
est_all_t1_full <- est_all
est_all_state_year_t1 <- est_all_state_year
```

### Table 1

Table 1 shows tightness as the largest correlate in standardized magnitude, followed by bachelor’s share. STEM share and patents per employee are positive but smaller, and manufacturing is reliably negative relative to ICT.

```{r}
#| label: tbl-table2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Replication of Table 2 from Andreadis et al. (2025) - The Correlates of the Percentage Point Change in the Share of AI Jobs"
#| tbl-cap-location: top
#| tbl-pos: "H"

# Follow EXACT original code structure
data_ai_2017_2022 <- read_csv("data.csv") %>% 
  filter(Year == 2017 | Year == 2018 | Year == 2022 | Year == 2023) %>% 
  mutate(state_year = paste0(state, Year)) %>% 
  mutate(new = 1 * (Year > 2020)) %>% 
  group_by(new, COUNTY_FIPS) %>% 
  mutate(ai = sum(ai), nads = sum(nads)) %>% 
  mutate(ai_intensity = ai / nads) %>% 
  filter(Year == 2017 | Year == 2022) %>% 
  group_by(COUNTY_FIPS) %>% 
  mutate(
    dai_intensity = ai_intensity - lag(ai_intensity),
    dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
  )

# Prepare demographics - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logincome = log(medhhincome),
    loghpi = log(hpi),
    logemp = log(pop_above18),
    logim = log(1)  # Note: original has logim=log(immigration) but no immigration variable
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    unrate14 = lag(unrate, 1),
    logincome14 = lag(logincome, 1),
    loghpi14 = lag(loghpi, 1),
    share_bac14 = lag(share_bac, 1),
    share_black14 = lag(share_black, 1),
    share_poverty14 = lag(share_poverty, 1),
    logemp14 = lag(logemp, 1),
    logim14 = lag(logim, 1),
    medage14 = lag(medage, 1),
    median_rent14 = lag(median_rent, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    gincome = logincome - lag(logincome, 1),
    ghpi = loghpi - lag(loghpi, 1),
    gemp = logemp - lag(logemp, 1),
    gim = logim - lag(logim, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    dunrate = unrate - lag(unrate, 1),
    dshare_bac = share_bac - lag(share_bac, 1),
    dshare_black = share_black - lag(share_black, 1),
    dmedage14 = medage - lag(medage, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads = log(1 + nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(lads0 = log(nads))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    information_intensity = manuf_emp / emp  # Note: this overwrites previous line in original
  )

# Log number of patents, inventors, etc. - EXACT as original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logemp = log(Employed)) %>% 
  mutate(logpop = log(pop))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_patents = log(1 + n_patents),
    logn_inventors = log(1 + n_inventors),
    logai_patents = log(1 + ai_patents),
    logai_inventors = log(1 + ai_inventors)
  ) %>%
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

# Duplicate line in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    small_firms = small / est,
    large_firms = 1 - (small + medium) / est,
    management_intensity = management_emp / emp,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp
  )

# Another duplicate section in original
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(patai_intensity = replace_na(patai_intensity, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    logn_inventors14 = lag(logn_inventors, 1),
    logai_inventors14 = lag(logai_inventors, 1),
    lads14 = lag(lads, 1)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  ungroup() %>%  
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg)
  )

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(stemshare = replace_na(stemshare, 0))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(stemshare14 = lag(stemshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(degshare14 = lag(degshare, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(tightness = nads / Unemployed)

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(tightness14 = lag(tightness, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(hpi_ch14 = lag(hpi_ch, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logpop14 = lag(logpop, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(logincome14 = lag(logincome, 1))

data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(gpop = (logpop - lag(logpop, 1)) / 5)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch = hpi_ch / 100)

data_ai_2017_2022 <- data_ai_2017_2022 %>%  
  mutate(hpi_ch14 = hpi_ch14 / 100)

# Industry structure
data_ai_2017_2022 <- data_ai_2017_2022 %>% 
  mutate(
    large_firms14 = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14 = lag(manuf_intensity, 1),
    TurnOvrS14 = lag(TurnOvrS, 1)
  )

# Z-scores - EXACT as original
data_ai_l_z <- data_ai_2017_2022 %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)

# Run FULL models with ALL variables (not condensed)
est_demog_no <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_innovation_no <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_industry_no <- fixest::feols(
  "dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_large <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_ai_l_z %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

# Save as-provided replication models for Appendix A
est_demog_t2_as <- est_demog_no
est_innovation_t2_as <- est_innovation_no
est_industry_t2_as <- est_industry_no
est_all_t2_as <- est_all
est_all_large_t2_as <- est_all_large

# --- Cleaned replication (main table) ---
data_ai_2017_2022_clean <- read_csv("data.csv") %>% 
  filter(Year %in% c(2017, 2018, 2022, 2023)) %>% 
  mutate(new = 1 * (Year > 2020)) %>% 
  group_by(new, COUNTY_FIPS) %>% 
  mutate(ai = sum(ai), nads = sum(nads)) %>% 
  mutate(ai_intensity = ai / nads) %>% 
  filter(Year %in% c(2017, 2022)) %>% 
  group_by(COUNTY_FIPS) %>% 
  mutate(
    dai_intensity = ai_intensity - lag(ai_intensity),
    dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
  ) %>%
  ungroup() %>%
  mutate(
    logincome = log(medhhincome),
    loghpi = log(hpi),
    logemp = log(pop_above18),
    logpop = log(pop),
    unrate14 = lag(unrate, 1),
    logincome14 = lag(logincome, 1),
    loghpi14 = lag(loghpi, 1),
    share_bac14 = lag(share_bac, 1),
    share_black14 = lag(share_black, 1),
    share_poverty14 = lag(share_poverty, 1),
    logpop14 = lag(logpop, 1),
    hpi_ch14 = lag(hpi_ch, 1),
    gpop = (logpop - lag(logpop, 1)) / 5,
    lads = log(1 + nads),
    lads14 = lag(lads, 1)
  ) %>%
  mutate(
    pat_intensity = n_inventors / Employed,
    patai_intensity = ai_patents / n_patents,
    pat_intensity14 = lag(pat_intensity, 1),
    patai_intensity14 = lag(patai_intensity, 1),
    patai_intensity = replace_na(patai_intensity, 0)
  ) %>%
  mutate(
    degshare = (udeg + mdeg) / Employed,
    stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg),
    stemshare = replace_na(stemshare, 0),
    degshare14 = lag(degshare, 1),
    stemshare14 = lag(stemshare, 1)
  ) %>%
  mutate(
    large_firms = 1 - (small + medium) / est,
    information_intensity = information_emp / emp,
    manuf_intensity = manuf_emp / emp,
    TurnOvrS14 = lag(TurnOvrS, 1),
    large_firms14 = lag(large_firms, 1),
    information_intensity14 = lag(information_intensity, 1),
    manuf_intensity14 = lag(manuf_intensity, 1)
  ) %>%
  mutate(
    tightness = nads / Unemployed,
    tightness14 = lag(tightness, 1),
    hpi_ch = hpi_ch / 100,
    hpi_ch14 = hpi_ch14 / 100
  )

data_ai_l_z_clean <- data_ai_2017_2022_clean %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)

est_demog_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_innovation_clean <- fixest::feols(
  "dai_intensity9 ~ pat_intensity14 + patai_intensity14 + degshare14 + stemshare14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_industry_clean <- fixest::feols(
  "dai_intensity9 ~ large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

est_all_large_clean <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14 | state" %>% as.formula(),
  data_ai_l_z_clean %>%
    filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
    drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
            tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
            large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14),
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)

# Extract model statistics (cleaned)
models <- list(est_demog_clean, est_innovation_clean, est_industry_clean, est_all_clean, est_all_large_clean)
obs <- map_chr(models, ~scales::comma(nobs(.x)))
r2_vals <- map_chr(models, ~sprintf("%.4f", r2(.x, "r2")))

# Create extra rows for table footer - add spacing before values to shift right
extra_rows <- tribble(
  ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`,
  "Fixed effects", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}None}", "{\\hspace{0.5em}State}",
  "Observations", paste0("{\\hspace{0.5em}", obs[1], "}"), paste0("{\\hspace{0.5em}", obs[2], "}"), paste0("{\\hspace{0.5em}", obs[3], "}"), paste0("{\\hspace{0.5em}", obs[4], "}"), paste0("{\\hspace{0.5em}", obs[5], "}"),
  "R²", paste0("{\\hspace{0.5em}", r2_vals[1], "}"), paste0("{\\hspace{0.5em}", r2_vals[2], "}"), paste0("{\\hspace{0.5em}", r2_vals[3], "}"), paste0("{\\hspace{0.5em}", r2_vals[4], "}"), paste0("{\\hspace{0.5em}", r2_vals[5], "}")
)

# Variable labels - condensed to only the 8 key variables
labels <- c(
  "share_bac14" = "Bachelors Share",
  "logincome14" = "Income, Log", 
  "tightness14" = "Tightness",
  "stemshare14" = "Stem Degrees' share",
  "large_firms14" = "Large Firms",
  "information_intensity14" = "ICT sector Intensity",
  "manuf_intensity14" = "Manufacturing",
  "TurnOvrS14" = "Turnover Rate"
)

# Create the table with modelsummary - use d for decimal alignment
modelsummary(
  list(
    "(1)" = est_demog_clean,
    "(2)" = est_innovation_clean,
    "(3)" = est_industry_clean,
    "(4)" = est_all_clean,
    "(5)" = est_all_large_clean
  ),
  coef_map = labels,
  stars = FALSE,
  gof_omit = ".*",
  add_rows = extra_rows,
  escape = FALSE,
  statistic = "({std.error})",
  fmt = 4,
  align = "lddddd",
  notes = "This table examines the demographic, innovation, and industry determinants of the percentage point change in AI job share between two pooled periods: 2017-2018 and 2022-2023. The dependent variable measures the change in AI intensity (multiplied by 100 to express in percentage points), capturing dynamic shifts rather than static levels. All explanatory variables are measured in 2017 (before the growth period) and standardized as z-scores. The sample includes 2,473 counties with sufficient data across both periods. All coefficients represent percentage point changes in the growth of AI job share for a one standard deviation increase in the 2017 explanatory variable. Models are estimated using ordinary least squares with no fixed effects (columns 1-4) or state fixed effects (column 5). Standard errors are clustered at the county level. "
)

est_all_t2 <- est_all_clean
est_demog_t2 <- est_demog_clean
est_innovation_t2 <- est_innovation_clean
est_industry_t2 <- est_industry_clean
est_all_t2_full <- est_all_clean
est_all_large_t2 <- est_all_large_clean
```


### Table 2

In the growth specification, tightness and STEM degree share are among the largest positive correlates, while several industry variables are small and imprecise. Table 2 reports a cleaned replication that removes redundant steps and intermediate overwrites while preserving the published specification and sample construction. For transparency, the as-provided replication (including the intermediate overwrite in the posted script and the missing immigration series) is reported in Appendix A.

```{r}
#| label: fig-map
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "Spatial heterogeneity in AI job share across US counties. Panel A shows the average share of AI-related job postings from 2014 to 2023. Panel B shows percentage-point changes between 2018 and 2023. Connecticut has no county observations in the provided dataset, so it is shown as no data."
#| fig-cap-location: bottom
#| fig-pos: "H"
#| fig-width: 18
#| fig-height: 9

library(tidyverse)
library(sf)
library(tigris)
library(patchwork)

# Read the updated Lightcast data
data <- read_csv("updated_lightcast_county.csv") %>%
  rename(COUNTY_FIPS = COUNTY_FIPS,
         Year = YEAR_POSTED,
         ai = `AI Postings`,
         nads = `Total Postings`)

# Remove Connecticut state-level data (FIPS 9999) and Planning Region entries
data_complete <- data %>%
  filter(COUNTY_FIPS != 9999) %>%
  filter(!(COUNTY_FIPS >= 9110 & COUNTY_FIPS <= 9190))

# ---- PANEL A ----
data_levels <- data_complete %>%
  mutate(aiInt = if_else(nads > 0, ai/nads, NA_real_)) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(aiInt = mean(aiInt, na.rm = TRUE), .groups = "drop")

# ---- PANEL B ----
data_for_change <- data_complete %>%
  mutate(
    year_group = case_when(
      Year %in% c(2017, 2018) ~ "2017-2018",
      Year %in% c(2022, 2023) ~ "2022-2023",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(year_group))

data_pooled <- data_for_change %>%
  group_by(COUNTY_FIPS, year_group) %>%
  summarise(
    ai_sum = sum(ai, na.rm = TRUE),
    nads_sum = sum(nads, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(aiInt = if_else(nads_sum > 0, ai_sum / nads_sum, NA_real_))

data_ch <- data_pooled %>%
  pivot_wider(
    id_cols = COUNTY_FIPS,
    names_from = year_group,
    values_from = aiInt
  ) %>%
  mutate(aiIntch = `2022-2023` - `2017-2018`) %>%
  select(COUNTY_FIPS, aiIntch)

# ---- FIPS FORMATTING ----
merged_data_lev <- data_levels %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

merged_data_ch <- data_ch %>%
  mutate(fips = COUNTY_FIPS %>% as.character() %>% str_pad(5, "0", side = "left"))

# ---- PANEL A BINNING ----
merged_data_lev <- merged_data_lev %>%
  mutate(ai_share = aiInt * 100) %>%
  mutate(caseai = case_when(
    ai_share >= 0 & ai_share < 0.06 ~ 1,
    ai_share > 0.06 & ai_share < 0.14 ~ 2,
    ai_share > 0.14 & ai_share < 0.23 ~ 3,
    ai_share > 0.23 & ai_share < 0.37 ~ 4,
    ai_share > 0.37 & ai_share < 0.7 ~ 5,
    ai_share > 0.7 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- PANEL B BINNING ----
merged_data_ch <- merged_data_ch %>%
  mutate(change_in_share = aiIntch * 100) %>%
  mutate(caseaich = case_when(
    change_in_share < -0.12 ~ 1,
    change_in_share > -0.12 & change_in_share <= 0 ~ 2,
    change_in_share > 0 & change_in_share < 0.09 ~ 3,
    change_in_share > 0.09 & change_in_share < 0.24 ~ 4,
    change_in_share > 0.24 & change_in_share < 0.57 ~ 5,
    change_in_share > 0.57 ~ 6,
    TRUE ~ NA_real_
  ))

# ---- COUNTY SHAPEFILES ----
options(tigris_use_cache = TRUE)
counties <- suppressMessages(
  tigris::counties(cb = TRUE, year = 2020, class = "sf")
) %>%
  mutate(COUNTY_FIPS = GEOID) %>%
  filter(!str_starts(COUNTY_FIPS, "72")) %>%
  st_transform(crs = 4326)

# ---- PANEL A MAP JOIN ----
map_data_a <- counties %>%
  left_join(merged_data_lev, by = c("COUNTY_FIPS" = "fips")) %>%
  tigris::shift_geometry()

# ---- PANEL B MAP JOIN (with Alaska color fix) ----
# Fix Alaska merge issue before shifting
ak_data <- merged_data_ch %>%
  filter(str_starts(fips, "02")) %>%
  distinct(fips, .keep_all = TRUE)

map_data_b <- counties %>%
  left_join(merged_data_ch, by = c("COUNTY_FIPS" = "fips"))

map_data_b[map_data_b$STATEFP == "02", names(ak_data)[-1]] <-
  ak_data[match(map_data_b$COUNTY_FIPS[map_data_b$STATEFP == "02"], ak_data$fips),
          names(ak_data)[-1]]

# Shift after joining (fixes Alaska colors)
map_data_b <- tigris::shift_geometry(map_data_b)

# ---- LABELS AND COLORS ----
map_data_a <- map_data_a %>%
  mutate(
    avg_bin = case_when(
      caseai == 1 ~ "0 – 0.06",
      caseai == 2 ~ "0.06 – 0.14",
      caseai == 3 ~ "0.14 – 0.23",
      caseai == 4 ~ "0.23 – 0.37",
      caseai == 5 ~ "0.37 – 0.71",
      caseai == 6 ~ "0.71 – 10",
      TRUE ~ "No data"
    )
  )

map_data_b <- map_data_b %>%
  mutate(
    chg_bin = case_when(
      caseaich == 1 ~ "−5.56 – −0.12",
      caseaich == 2 ~ "−0.12 – 0",
      caseaich == 3 ~ "0 – 0.09",
      caseaich == 4 ~ "0.09 – 0.24",
      caseaich == 5 ~ "0.24 – 0.57",
      caseaich == 6 ~ "0.57 – 12.35",
      TRUE ~ "No data"
    )
  )

levels_avg_display <- c("0.71 – 10", "0.37 – 0.71", "0.23 – 0.37",
                        "0.14 – 0.23", "0.06 – 0.14", "0 – 0.06", "No data")
levels_chg_display <- c("0.57 – 12.35", "0.24 – 0.57", "0.09 – 0.24",
                        "0 – 0.09", "−0.12 – 0", "−5.56 – −0.12", "No data")

colors_avg_display <- c("#800026", "#e31a1c", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")
colors_chg_display <- c("#800026", "#fc4e2a", "#fd8d3c", "#fed976", "#ffeda0", "#ffffcc", "gray90")

map_data_a$avg_bin <- factor(map_data_a$avg_bin, levels = levels_avg_display)
map_data_b$chg_bin <- factor(map_data_b$chg_bin, levels = levels_chg_display)

# ---- THEME ----
map_theme <- theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 20, margin = margin(t = 3, b = 3, l = 1, r = 1)),
    legend.title = element_blank(),
    legend.key.width = unit(1.8, "cm"),
    legend.key.height = unit(0.6, "cm"),
    legend.spacing.x = unit(0.2, "cm"),
    legend.spacing.y = unit(0.1, "cm"),
    legend.margin = margin(t = 10, b = 5),
    legend.key = element_rect(color = "black", size = 0.5),
    plot.margin = margin(10, 10, 25, 10, "pt"),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.border = element_rect(color = "black", fill = NA, size = 0.5)
  )

# ---- PLOTS ----
p1 <- ggplot(map_data_a) +
  geom_sf(aes(fill = avg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_avg_display, levels_avg_display),
                    breaks = levels_avg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_a), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel A. Percent share of AI jobs (2014–2023 average)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

p2 <- ggplot(map_data_b) +
  geom_sf(aes(fill = chg_bin), color = "white", size = 0.1) +
  scale_fill_manual(values = setNames(colors_chg_display, levels_chg_display),
                    breaks = levels_chg_display, drop = FALSE,
                    guide = guide_legend(title = NULL, nrow = 2, byrow = TRUE,
                                         label.position = "bottom",
                                         keywidth = unit(1.8, "cm"), keyheight = unit(0.6, "cm"),
                                         label.hjust = 0.5,
                                         override.aes = list(color = "black", size = 0.5))) +
  coord_sf(crs = st_crs(map_data_b), expand = FALSE, clip = "off",
           xlim = c(-2800000, 2500000), ylim = c(-2300000, 1600000)) +
  labs(title = "Panel B. Percentage-point change in AI share (2018–2023)") +
  map_theme +
  theme(plot.title = element_text(size = 24, hjust = 0, margin = margin(b = 12)))

# ---- FINAL COMBINED PLOT ----
final_plot <- (p1 | p2) +
  plot_layout(widths = c(1, 1)) &
  theme(plot.background = element_rect(fill = "white", color = NA))

# Add overall title
final_plot <- final_plot +
  plot_annotation(
    title = "Figure 1: Replication of Andreadis et al. (2025) - Spatial Heterogeneity in the Share of and Change of AI Jobs",
    theme = theme(plot.title = element_text(size = 26, hjust = 0.5, margin = margin(b = 15)))
  )

final_plot
```

## The Problem of Denominator Contamination

Consider a gym that reports the share of protein smoothies among all drinks sold and a separate measure of "thirstiness" defined as total drinks sold divided by the number of gym members. Even if smoothie orders are unrelated to membership, the shared total-drinks term mechanically links the two ratios. Counties face the same arithmetic: AI intensity divides AI postings by total postings, while tightness divides total postings by unemployment. The shared denominator can create correlation even absent a causal link between the underlying economic quantities.

Let AI intensity be \(A/T\) and tightness be \(T/U\), where \(A\) is AI postings, \(T\) is total postings, and \(U\) is unemployment. The shared \(T\) term can induce mechanical correlation, but the magnitude and sign depend on the data-generating process and on how ratio variability interacts with \(T\). This motivates the simulation below, which shows that the contaminated specification can produce nonzero coefficients even when the AI rate is generated independently of unemployment. In that setting, tightness should be interpreted as a partial correlation with a mechanical component rather than a causal effect.

### Simulation

We calibrate the simulation to match the empirical distributions of total postings and unemployment in the data. We generate AI postings independently of total postings and unemployment (matched to the empirical AI-postings distribution), and then construct AI intensity by dividing by total postings. This keeps the mechanical illustration close to the scale and dispersion observed in the county-year panel while ensuring that any correlation between AI intensity and tightness is driven by shared construction rather than an imposed relationship.
The sign and magnitude of the mechanical component depend on the distributions of the shared denominator and the regressor. The simulation isolates the mechanical component by generating AI postings and unemployment independently, then showing that the contaminated regressor still loads nontrivially because T appears in both constructed variables.

```{r}
#| label: fig-simulation
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Simulation: Mechanical correlation from denominator contamination. AI postings are generated independently of total postings and unemployment (matched to the empirical AI-postings distribution). Contaminated tightness uses the same total postings as the AI intensity denominator (T/U), while the clean proxy uses an independent postings draw (T*/U)."
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 8
#| fig-height: 4.5
#| cache: true
set.seed(42)
n_counties <- 3000
n_years <- 10
n_obs <- n_counties * n_years

ads_emp <- data_ai %>% filter(is.finite(nads), nads > 0) %>% pull(nads)
unemp_emp <- data_ai %>% filter(is.finite(Unemployed), Unemployed > 0) %>% pull(Unemployed)
ai_share_emp <- data_ai %>%
  filter(is.finite(ai), is.finite(nads), nads > 0) %>%
  mutate(share = ai / nads) %>%
  filter(share >= 0, share <= 1) %>%
  pull(share)

meanlog_ads <- mean(log(ads_emp))
sdlog_ads <- max(sd(log(ads_emp)), 1e-6)
meanlog_unemp <- mean(log(unemp_emp))
sdlog_unemp <- max(sd(log(unemp_emp)), 1e-6)

ai_emp <- data_ai %>% filter(is.finite(ai), ai > 0) %>% pull(ai)
meanlog_ai <- mean(log(ai_emp))
sdlog_ai <- max(sd(log(ai_emp)), 1e-6)

run_single_sim <- function(seed, sd_mult = 1) {
  for (k in 0:4) {
    set.seed(seed + k * 10000)
    total_postings <- pmax(1, round(exp(rnorm(n_obs, mean = meanlog_ads, sd = sdlog_ads * sd_mult))))
    unemployed <- exp(rnorm(n_obs, mean = meanlog_unemp, sd = sdlog_unemp))
    lambda_a <- exp(rnorm(n_obs, mean = meanlog_ai, sd = sdlog_ai))
    ai_postings <- rpois(n_obs, lambda = lambda_a)
    ai_intensity <- (ai_postings / total_postings) * 100
    tightness <- total_postings / unemployed
    other_postings <- pmax(1, round(exp(rnorm(n_obs, mean = meanlog_ads, sd = sdlog_ads * sd_mult))))
    tightness_clean <- other_postings / unemployed
    tight_z <- as.numeric(scale(tightness))
    tight_clean_z <- as.numeric(scale(tightness_clean))
    if (all(!is.finite(tight_z))) tight_z <- rnorm(length(tight_z))
    if (all(!is.finite(tight_clean_z))) tight_clean_z <- rnorm(length(tight_clean_z))
    sim_data <- data.frame(
      ai_intensity = ai_intensity,
      tightness = tight_z,
      tightness_clean = tight_clean_z,
      county = rep(1:n_counties, each = n_years),
      year = rep(1:n_years, n_counties),
      w = log(1 + total_postings)
    )
    m1 <- tryCatch(
      fixest::feols(ai_intensity ~ tightness | county + year, data = sim_data, weights = ~w, warn = FALSE),
      error = function(e) NULL
    )
    m2 <- tryCatch(
      fixest::feols(ai_intensity ~ tightness_clean | county + year, data = sim_data, weights = ~w, warn = FALSE),
      error = function(e) NULL
    )
    b1 <- if (!is.null(m1)) coef(m1)["tightness"] else NA_real_
    b2 <- if (!is.null(m2)) coef(m2)["tightness_clean"] else NA_real_
    if (is.finite(b1) && is.finite(b2)) {
      return(c(contaminated = b1, clean = b2))
    }
  }
  c(contaminated = NA_real_, clean = NA_real_)
}

n_boot <- 2000
boot_results <- t(vapply(1:n_boot, function(s) run_single_sim(s, sd_mult = 1), numeric(2)))
colnames(boot_results) <- c("contaminated", "clean")
boot_contam_mean <- mean(boot_results[, "contaminated"])
boot_contam_ci <- quantile(boot_results[, "contaminated"], c(0.025, 0.975))
boot_clean_mean <- mean(boot_results[, "clean"])
boot_clean_ci <- quantile(boot_results[, "clean"], c(0.025, 0.975))

# Generate primary simulation for display
total_postings <- pmax(1, round(exp(rnorm(n_obs, mean = meanlog_ads, sd = sdlog_ads))))
unemployed <- exp(rnorm(n_obs, mean = meanlog_unemp, sd = sdlog_unemp))
lambda_a <- exp(rnorm(n_obs, mean = meanlog_ai, sd = sdlog_ai))
ai_postings <- rpois(n_obs, lambda = lambda_a)
ai_intensity <- (ai_postings / total_postings) * 100
tightness <- total_postings / unemployed
other_postings <- pmax(1, round(exp(rnorm(n_obs, mean = meanlog_ads, sd = sdlog_ads))))
tightness_clean <- other_postings / unemployed
sim_data <- data.frame(
  ai_intensity = ai_intensity,
  tightness = as.numeric(scale(tightness)),
  tightness_clean = as.numeric(scale(tightness_clean)),
  county = rep(1:n_counties, each = n_years),
  year = rep(1:n_years, n_counties),
  w = log(1 + total_postings)
)
if (all(!is.finite(sim_data$tightness))) sim_data$tightness <- rnorm(n_obs)
if (all(!is.finite(sim_data$tightness_clean))) sim_data$tightness_clean <- rnorm(n_obs)
model_contaminated <- fixest::feols(ai_intensity ~ tightness | county + year, data = sim_data, weights = ~w)
model_clean <- fixest::feols(ai_intensity ~ tightness_clean | county + year, data = sim_data, weights = ~w)

results_df <- data.frame(
  Variable = c("Contaminated Tightness \n(shared denominator)",
               "Uncontaminated Tightness \n(independent denominator)"),
  Coef = c(boot_contam_mean, boot_clean_mean),
  lower = c(boot_contam_ci[1], boot_clean_ci[1]),
  upper = c(boot_contam_ci[2], boot_clean_ci[2])
) %>%
  mutate(
    Variable = factor(Variable, levels = rev(Variable))
  )

range_x <- max(abs(c(results_df$lower, results_df$upper, results_df$Coef)), na.rm = TRUE)
range_x <- if (is.finite(range_x) && range_x > 0) range_x else 0.05
limit_x <- max(0.05, range_x * 1.5)

ggplot(results_df, aes(x = Coef, y = Variable)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", size = 0.8) +
  geom_point(size = 3.6, color = "#E63946") +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.15, linewidth = 1.0, color = "#E63946") +
  labs(
    x = "Coefficient on Tightness (z-scored)",
    y = NULL,
    title = "Denominator Contamination Creates Spurious Correlation",
    subtitle = "AI postings independent of unemployment and total postings; AI intensity divides by total postings"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(size = 13, face = "bold", margin = margin(b = 5)),
    plot.subtitle = element_text(size = 10, color = "gray40", margin = margin(b = 10)),
    axis.text.y = element_text(size = 10, color = "gray20"),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 10, margin = margin(t = 8)),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(
    limits = c(-limit_x, limit_x),
    breaks = pretty(c(-limit_x, limit_x), n = 5)
  )
```

```{r}
#| label: tbl-simulation
#| echo: false
#| warning: false
#| message: false
sim_tbl <- data.frame(
  Specification = c("Contaminated tightness", "Uncontaminated tightness"),
  Mean = c(
    sprintf("%.4f", boot_contam_mean),
    sprintf("%.4f", boot_clean_mean)
  ),
  CI_95 = c(
    sprintf("[%.4f, %.4f]", boot_contam_ci[1], boot_contam_ci[2]),
    sprintf("[%.4f, %.4f]", boot_clean_ci[1], boot_clean_ci[2])
  )
)
knitr::kable(sim_tbl, col.names = c("Specification", "Mean", "95% CI"), align = "lcc")
```


```{r}
#| label: fig-diagnostic-scatter
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Diagnostic scatter: total postings vs. AI intensity and tightness (clipped at 99th percentile; loess smoother shown)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 6.5
#| fig-height: 3.8
set.seed(42)
scatter_df <- data_ai %>%
  mutate(ai_intensity_pct = (ai / nads) * 100,
         tightness_raw = nads / Unemployed) %>%
  filter(is.finite(ai_intensity_pct), is.finite(tightness_raw), nads > 0, Unemployed > 0) %>%
  sample_n(min(20000, n())) %>%
  pivot_longer(cols = c(ai_intensity_pct, tightness_raw), names_to = "series", values_to = "value") %>%
  group_by(series) %>%
  mutate(p99 = quantile(value, 0.99, na.rm = TRUE),
         value_clip = pmin(value, p99)) %>%
  ungroup()

ggplot(scatter_df, aes(x = log(1 + nads), y = value_clip)) +
  geom_point(alpha = 0.25, size = 0.6, color = "#2E86AB") +
  geom_smooth(method = "loess", se = FALSE, color = "#E63946", linewidth = 0.9) +
  facet_wrap(~series, scales = "free_y", ncol = 2,
             labeller = as_labeller(c(ai_intensity_pct = "AI intensity (%)", tightness_raw = "Tightness"))) +
  labs(x = "log(1 + total postings)", y = NULL) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank())
```
The diagnostic scatter shows strong dependence on total postings in both series, consistent with a shared arithmetic component.
*Notes:* Simulation calibrated to the empirical distributions of postings and unemployment. AI postings are generated independently of total postings and unemployment (matched to the empirical AI-postings distribution), and AI intensity is constructed by dividing by total postings. The contaminated specification produces a mechanical coefficient of approximately `r sprintf("%.3f", boot_contam_mean)` (95% CI [`r sprintf("%.3f", boot_contam_ci[1])`, `r sprintf("%.3f", boot_contam_ci[2])`]) even under this independence (2,000 replications). The uncontaminated specification is near zero (`r sprintf("%.3f", boot_clean_mean)`).

To preserve the economic meaning of tightness while isolating the problematic component, we report three complementary checks: (i) omitting tightness, (ii) decomposing tightness into log(postings) and log(unemployment) and residualizing tightness on those components, and (iii) a count model with a postings offset.

### Reanalysis Excluding Tightness (Table 1, Column 4)

```{r}
#| label: tbl-no-tightness-t1
#| echo: false
#| warning: false
#| message: false
est_all_t1 <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
est_all_t1_no_tightness <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
vars_core_t1 <- c("share_bac", "hpi_ch", "pat_intensity", "stemshare", "information_intensity", "manuf_intensity", "TurnOvrS")
labels_core_t1 <- c("Bachelor's share", "House price growth", "Patents per employee", "STEM degrees share", "ICT sector intensity", "Manufacturing intensity", "Turnover rate")
no_tight_tbl_t1 <- data.frame(
  Variable = labels_core_t1,
  `Baseline (replicated)` = sprintf("%.4f (%.4f)", coef(est_all_t1)[vars_core_t1], se(est_all_t1)[vars_core_t1]),
  `No Tightness` = sprintf("%.4f (%.4f)", coef(est_all_t1_no_tightness)[vars_core_t1], se(est_all_t1_no_tightness)[vars_core_t1]),
  `% Change` = sprintf("%+.0f%%", (coef(est_all_t1_no_tightness)[vars_core_t1] - coef(est_all_t1)[vars_core_t1]) / coef(est_all_t1)[vars_core_t1] * 100)
)
knitr::kable(no_tight_tbl_t1, align = "lccc", col.names = c("Variable", "Baseline (replicated)", "No Tightness", "% Change"))
```

*Notes:* This table compares Table 1's baseline specification (column 4) to the same model estimated without labor-market tightness.

### Reanalysis Excluding Tightness (Table 2, Column 4)

```{r}
#| label: prep-t2-data
#| echo: false
#| warning: false
#| message: false
if (!exists("data_ai_l_z")) {
  data_ai_2017_2022 <- read_csv("data.csv") %>% 
    filter(Year == 2017 | Year == 2018 | Year == 2022 | Year == 2023) %>% 
    mutate(state_year = paste0(state, Year)) %>% 
    mutate(new = 1 * (Year > 2020)) %>% 
    group_by(new, COUNTY_FIPS) %>% 
    mutate(ai = sum(ai), nads = sum(nads)) %>% 
    mutate(ai_intensity = ai / nads) %>% 
    filter(Year == 2017 | Year == 2022) %>% 
    group_by(COUNTY_FIPS) %>% 
    mutate(
      dai_intensity = ai_intensity - lag(ai_intensity),
      dai_intensity9 = ai_intensity - lag(ai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logincome = log(medhhincome),
      loghpi = log(hpi),
      logemp = log(pop_above18),
      logim = log(1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      unrate14 = lag(unrate, 1),
      logincome14 = lag(logincome, 1),
      loghpi14 = lag(loghpi, 1),
      share_bac14 = lag(share_bac, 1),
      share_black14 = lag(share_black, 1),
      share_poverty14 = lag(share_poverty, 1),
      logemp14 = lag(logemp, 1),
      logim14 = lag(logim, 1),
      medage14 = lag(medage, 1),
      median_rent14 = lag(median_rent, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      gincome = logincome - lag(logincome, 1),
      ghpi = loghpi - lag(loghpi, 1),
      gemp = logemp - lag(logemp, 1),
      gim = logim - lag(logim, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      dunrate = unrate - lag(unrate, 1),
      dshare_bac = share_bac - lag(share_bac, 1),
      dshare_black = share_black - lag(share_black, 1),
      dmedage14 = medage - lag(medage, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(lads = log(1 + nads))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(lads0 = log(nads))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      large_firms = 1 - (small + medium) / est,
      management_intensity = management_emp / emp,
      information_intensity = information_emp / emp,
      information_intensity = manuf_emp / emp
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logemp = log(Employed)) %>% 
    mutate(logpop = log(pop))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logn_patents = log(1 + n_patents),
      logn_inventors = log(1 + n_inventors),
      logai_patents = log(1 + ai_patents),
      logai_inventors = log(1 + ai_inventors)
    ) %>%
    mutate(
      pat_intensity = n_inventors / Employed,
      patai_intensity = ai_patents / n_patents
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      small_firms = small / est,
      large_firms = 1 - (small + medium) / est,
      management_intensity = management_emp / emp,
      information_intensity = information_emp / emp,
      manuf_intensity = manuf_emp / emp
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity = n_inventors / Employed,
      patai_intensity = ai_patents / n_patents
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(patai_intensity = replace_na(patai_intensity, 0))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      pat_intensity14 = lag(pat_intensity, 1),
      patai_intensity14 = lag(patai_intensity, 1),
      lads14 = lag(lads, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      logn_inventors14 = lag(logn_inventors, 1),
      logai_inventors14 = lag(logai_inventors, 1),
      lads14 = lag(lads, 1)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    ungroup() %>%  
    mutate(
      degshare = (udeg + mdeg) / Employed,
      stemshare = (ustemdeg + mstemdeg) / (udeg + mdeg)
    )

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(stemshare = replace_na(stemshare, 0))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(stemshare14 = lag(stemshare, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(degshare14 = lag(degshare, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(tightness = nads / Unemployed)

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(tightness14 = lag(tightness, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(hpi_ch14 = lag(hpi_ch, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logpop14 = lag(logpop, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(logincome14 = lag(logincome, 1))

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(gpop = (logpop - lag(logpop, 1)) / 5)

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(hpi_ch = hpi_ch / 100)

  data_ai_2017_2022 <- data_ai_2017_2022 %>%  
    mutate(hpi_ch14 = hpi_ch14 / 100)

  data_ai_2017_2022 <- data_ai_2017_2022 %>% 
    mutate(
      large_firms14 = lag(large_firms, 1),
      information_intensity14 = lag(information_intensity, 1),
      manuf_intensity14 = lag(manuf_intensity, 1),
      TurnOvrS14 = lag(TurnOvrS, 1)
    )

data_ai_l_z <- data_ai_2017_2022 %>% 
  filter(emp != 0) %>% 
  drop_na(share_bac14) %>%
  mutate(
    share_bac14 = as.numeric(scale(share_bac14)),
    share_black14 = as.numeric(scale(share_black14)),
    share_poverty14 = as.numeric(scale(share_poverty14)),
    logpop14 = as.numeric(scale(logpop14)),
    hpi_ch14 = as.numeric(scale(hpi_ch14)),
    logincome14 = as.numeric(scale(logincome14)),
    tightness14 = as.numeric(scale(tightness14)),
    pat_intensity14 = as.numeric(scale(pat_intensity14)),
    patai_intensity14 = as.numeric(scale(patai_intensity14)),
    degshare14 = as.numeric(scale(degshare14)),
    stemshare14 = as.numeric(scale(stemshare14)),
    large_firms14 = as.numeric(scale(large_firms14)),
    information_intensity14 = as.numeric(scale(information_intensity14)),
    manuf_intensity14 = as.numeric(scale(manuf_intensity14)),
    TurnOvrS14 = as.numeric(scale(TurnOvrS14)),
    unrate14 = as.numeric(scale(unrate14))
  ) %>% 
  mutate(dai_intensity9 = dai_intensity9 * 100)
}
```

```{r}
#| label: tbl-no-tightness-t2
#| echo: false
#| warning: false
#| message: false
data_t2_z_nt <- data_ai_l_z %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2 <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
vars_core_t2 <- c("share_bac14", "hpi_ch14", "pat_intensity14", "stemshare14", "information_intensity14", "manuf_intensity14", "TurnOvrS14")
labels_core_t2 <- c("Bachelor's share", "House price growth", "Patents per employee", "STEM degrees share", "ICT sector intensity", "Manufacturing intensity", "Turnover rate")
no_tight_tbl_t2 <- data.frame(
  Variable = labels_core_t2,
  `Baseline (replicated)` = sprintf("%.4f (%.4f)", coef(est_all_t2)[vars_core_t2], se(est_all_t2)[vars_core_t2]),
  `No Tightness` = sprintf("%.4f (%.4f)", coef(est_all_t2_no_tightness)[vars_core_t2], se(est_all_t2_no_tightness)[vars_core_t2]),
  `% Change` = sprintf("%+.0f%%", (coef(est_all_t2_no_tightness)[vars_core_t2] - coef(est_all_t2)[vars_core_t2]) / coef(est_all_t2)[vars_core_t2] * 100)
)
knitr::kable(no_tight_tbl_t2, align = "lccc", col.names = c("Variable", "Baseline (replicated)", "No Tightness", "% Change"))
```

*Notes:* This table compares Table 2's baseline specification (column 4) to the same model estimated without labor-market tightness.

### Decomposing Tightness: Log(Postings) and Log(Unemployment)

As a direct check on the contaminated regressor, we replace tightness $T/U$ with its components, \mbox{$\\log(T)$} and \mbox{$\\log(U)$}, in the levels specification. This tests whether the tightness signal is primarily loading on postings scale rather than unemployment.

```{r}
#| label: tbl-tightness-decomp
#| echo: false
#| warning: false
#| message: false
data_ai_decomp <- data_ai_z %>%
  mutate(
    log_nads = as.numeric(scale(log(pmax(nads, 1)))),
    log_unemp = as.numeric(scale(log(pmax(Unemployed, 1))))
  )

est_all_t1_decomp <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + log_nads + log_unemp + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_decomp,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

decomp_tbl <- data.frame(
  Term = c("Tightness (baseline)", "Log total postings", "Log unemployment"),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_nads"], se(est_all_t1_decomp)["log_nads"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_unemp"], se(est_all_t1_decomp)["log_unemp"])
  )
)
knitr::kable(decomp_tbl, align = "lc", col.names = c("Term", "Estimate"))
```

*Notes:* Decomposition uses the same controls and fixed effects as Table 1, column 4.

### Empirical Decomposition: Residualized Tightness (Levels)

To quantify how much of the tightness signal is tied to the postings component in the empirical specification, we residualize tightness on \mbox{$\\log(T)$} and \mbox{$\\log(U)$} using the same fixed effects and weights, and then re-estimate the baseline model with the residualized tightness. This keeps the original controls and weighting while removing the variation in tightness that is mechanically aligned with postings scale.

```{r}
#| label: tbl-tightness-resid
#| echo: false
#| warning: false
#| message: false
tight_resid_model <- fixest::feols(
  tightness ~ log_nads + log_unemp | Year + COUNTY_FIPS,
  data_ai_decomp,
  weights = ~lads
)
used_idx <- fixest::obs(tight_resid_model)
data_ai_decomp_used <- data_ai_decomp
data_ai_decomp_used$tightness_resid <- NA_real_
data_ai_decomp_used$tightness_resid[used_idx] <- as.numeric(resid(tight_resid_model))

est_all_t1_resid <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness_resid + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_decomp_used,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)

resid_tbl <- data.frame(
  Term = c("Tightness (baseline)", "Tightness (residualized)"),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_resid)["tightness_resid"], se(est_all_t1_resid)["tightness_resid"])
  )
)
knitr::kable(resid_tbl, align = "lc", col.names = c("Term", "Estimate"))
```

*Notes:* Residualization uses the same fixed effects and posting weights as Table 1, column 4.

To quantify how much tightness is driven by postings scale in the empirical specification, we compute the within-FE R² from the residualization regression above. In this sample, log(postings) and log(unemployment) explain `r sprintf("%.1f%%", 100 * r2(tight_resid_model, "r2"))` of tightness variation.

### Tightness Horse Race (Levels)

```{r}
#| label: tbl-tightness-horserace
#| echo: false
#| warning: false
#| message: false
horse_tbl <- data.frame(
  Specification = c(
    "Baseline: Tightness (T/U)",
    "Decomposition: log(T)",
    "Decomposition: log(U)",
    "Residualized Tightness",
    "Unemployment Rate Proxy",
    "Poisson Offset Model"
  ),
  Estimate = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_nads"], se(est_all_t1_decomp)["log_nads"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_decomp)["log_unemp"], se(est_all_t1_decomp)["log_unemp"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_resid)["tightness_resid"], se(est_all_t1_resid)["tightness_resid"]),
    {
      if (!exists("est_all_t1_unrate")) {
        est_all_t1_unrate <- fixest::feols(
          "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + unrate + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
          data_ai_z,
          cluster = "COUNTY_FIPS",
          weights = ~lads
        )
      }
      sprintf("%.4f (%.4f)", coef(est_all_t1_unrate)["unrate"], se(est_all_t1_unrate)["unrate"])
    },
    {
      if (!exists("est_all_t1_pois")) {
        data_ai_count <- data_ai_z %>% filter(nads_raw > 0)
        est_all_t1_pois <- fixest::fepois(
          ai_raw ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS,
          data = data_ai_count,
          offset = log(data_ai_count$nads_raw),
          cluster = "COUNTY_FIPS"
        )
      }
      sprintf("%.4f (%.4f)", coef(est_all_t1_pois)["tightness"], se(est_all_t1_pois)["tightness"])
    }
  )
)
knitr::kable(horse_tbl, align = "lc", col.names = c("Specification", "Estimate"))
```

*Notes:* All specifications use the full set of controls and county/year fixed effects. The Poisson model uses a log(total postings) offset.

### Count Model with Offset (Levels)

As a second alternative, we model AI postings counts with an offset for total postings. This specification avoids ratio outcomes while preserving the scale of postings in the likelihood.

```{r}
#| label: tbl-offset-poisson
#| echo: false
#| warning: false
#| message: false
data_ai_count <- data_ai_z %>% filter(nads_raw > 0)

est_all_t1_pois <- fixest::fepois(
  ai_raw ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + tightness + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS,
  data = data_ai_count,
  offset = log(data_ai_count$nads_raw),
  cluster = "COUNTY_FIPS"
)

offset_tbl <- data.frame(
  Model = c("OLS ratio (Table 1, Col. 4)", "Poisson w/ offset"),
  Tightness = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t1_pois)["tightness"], se(est_all_t1_pois)["tightness"])
  )
)
knitr::kable(offset_tbl, align = "lc")
```

*Notes:* Offset is \mbox{$\\log(T)$}, where $T$ is total postings.

### Alternative Tightness Proxy: Unemployment Rate

As a practical alternative that avoids sharing the postings denominator, we replace tightness with the unemployment rate. This keeps the labor-market dimension while removing the mechanical overlap with AI intensity.

```{r}
#| label: tbl-unrate-proxy
#| echo: false
#| warning: false
#| message: false
est_all_t1_unrate <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + unrate + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~lads
)
est_all_t2_unrate <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + unrate14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_z_nt,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
proxy_tbl <- data.frame(
  Outcome = c("Table 1 (levels, col. 4)", "Table 2 (growth, col. 4)"),
  `Tightness` = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1)["tightness"], se(est_all_t1)["tightness"]),
    sprintf("%.4f (%.4f)", coef(est_all_t2)["tightness14"], se(est_all_t2)["tightness14"])
  ),
  `Unemployment rate` = c(
    sprintf("%.4f (%.4f)", coef(est_all_t1_unrate)["unrate"], se(est_all_t1_unrate)["unrate"]),
    sprintf("%.4f (%.4f)", coef(est_all_t2_unrate)["unrate14"], se(est_all_t2_unrate)["unrate14"])
  )
)
knitr::kable(proxy_tbl, align = "lcc")
```

*Notes:* Tightness and unemployment rate are both standardized. The unemployment-rate proxy avoids the shared denominator with AI intensity while retaining a labor-market signal.

## Conclusion

Denominator contamination in labor-market tightness creates a mechanical component in the estimated relationship. Because total postings appear in both the AI-intensity denominator and the tightness numerator, the tightness coefficient partly reflects shared arithmetic structure even when the AI rate is generated independently of unemployment. The DAG and simulation show that this component is not merely theoretical: under this calibrated DGP, the contaminated specification yields a nonzero mechanical coefficient, while the uncontaminated specification centers near zero.

Re-estimating the main specification after removing tightness reduces the magnitudes of the remaining correlates and weakens several associations. As a secondary check, we compare alternative weighting schemes after removing tightness; coefficients attenuate on average, indicating sensitivity to how county-year relationships are aggregated.

These results do not overturn AKCLM's descriptive contribution, but they suggest a more nuanced interpretation. The headline tightness result partly reflects shared arithmetic structure, and the remaining associations are more modest in magnitude once the contaminated variable is removed and alternative weighting schemes are considered. Researchers using similar ratio-based labor-market variables should avoid shared components or explicitly test for mechanical correlation.


## Bibliography {.unnumbered}
::: {#refs}
:::

\newpage

## Appendix A: Weighting Sensitivity {.unnumbered}

### Log-Population Weights (Table 1, Column 4) {.unnumbered}

After removing the contaminated tightness variable, we test whether remaining associations are sensitive to alternative aggregation schemes by comparing unweighted, population-weighted, and log-population-weighted estimates. Population weights correspond to a person-weighted relationship; log(population) is an intermediate, concave reweighting that tilts toward larger counties without letting a few very large counties dominate. This provides a transparent sensitivity check relative to the original posting-weighted estimand. Coefficient magnitudes attenuate on average (see Figure 4).

```{r}
#| label: tbl-weights-robust
#| echo: false
#| warning: false
#| message: false
est_all_t1_no_tightness_unw <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS"
)
est_all_t1_no_tightness_pop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~pop_raw
)
est_all_t1_no_tightness_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

data_t2_logpop <- data_ai_2017_2022 %>%
  filter(emp != 0) %>%
  drop_na(share_bac14) %>%
  mutate(
    logpop_raw = logpop14,
    share_bac14 = scale(share_bac14),
    share_black14 = scale(share_black14),
    share_poverty14 = scale(share_poverty14),
    logpop14 = scale(logpop14),
    hpi_ch14 = scale(hpi_ch14),
    logincome14 = scale(logincome14),
    tightness14 = scale(tightness14),
    pat_intensity14 = scale(pat_intensity14),
    patai_intensity14 = scale(patai_intensity14),
    degshare14 = scale(degshare14),
    stemshare14 = scale(stemshare14),
    large_firms14 = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14 = scale(manuf_intensity14),
    TurnOvrS14 = scale(TurnOvrS14),
    unrate14 = scale(unrate14),
    pop_raw = exp(logpop_raw)
  ) %>%
  mutate(dai_intensity9 = dai_intensity9 * 100) %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2_no_tightness_unw <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS"
)
est_all_t2_no_tightness_pop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~pop_raw
)
est_all_t2_no_tightness_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)

med_change <- function(est_ref, est_new, vars) {
  median(abs((coef(est_new)[vars] - coef(est_ref)[vars]) / coef(est_ref)[vars]) * 100, na.rm = TRUE)
}

weights_tbl <- data.frame(
  Scheme = c("Unweighted", "Population-weighted", "Log-population weighted"),
  `Table 1 median abs change` = sprintf(
    "%.0f%%",
    c(
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_unw, vars_core_t1),
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_pop, vars_core_t1),
      med_change(est_all_t1_no_tightness, est_all_t1_no_tightness_logpop, vars_core_t1)
    )
  ),
  `Table 2 median abs change` = sprintf(
    "%.0f%%",
    c(
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_unw, vars_core_t2),
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_pop, vars_core_t2),
      med_change(est_all_t2_no_tightness, est_all_t2_no_tightness_logpop, vars_core_t2)
    )
  ),
  check.names = FALSE
)
knitr::kable(weights_tbl, align = "lcc")
```

*Notes:* Median absolute changes are computed relative to the no-tightness baseline with log(1+ads) weights.

```{r}
#| label: fig-logpop-compact-t1
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Coefficient sensitivity after removing tightness using log-population weights (Table 1, Col. 4)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 6
#| fig-height: 4
est_all_t1_no_tightness_logpop <- fixest::feols(
  "ai_intensity ~ share_bac + share_black + share_poverty + logpop + hpi_ch + logincome + pat_intensity + patai_intensity + degshare + stemshare + large_firms + information_intensity + manuf_intensity + TurnOvrS | Year + COUNTY_FIPS" %>% as.formula(),
  data_ai_z,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)
plot_df_t1 <- bind_rows(
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1)[vars_core_t1], SE = se(est_all_t1)[vars_core_t1], Scheme = "Original"),
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1_no_tightness)[vars_core_t1], SE = se(est_all_t1_no_tightness)[vars_core_t1], Scheme = "No Tightness"),
  data.frame(Variable = labels_core_t1, Coef = coef(est_all_t1_no_tightness_logpop)[vars_core_t1], SE = se(est_all_t1_no_tightness_logpop)[vars_core_t1], Scheme = "No Tightness + Log-Pop")
) %>%
  mutate(
    lower = Coef - 1.96 * SE,
    upper = Coef + 1.96 * SE,
    Variable = factor(Variable, levels = rev(labels_core_t1)),
    Scheme = factor(Scheme, levels = c("Original", "No Tightness", "No Tightness + Log-Pop"))
  )
logpop_t1_median <- median(abs((coef(est_all_t1_no_tightness_logpop)[vars_core_t1] - coef(est_all_t1)[vars_core_t1]) / coef(est_all_t1)[vars_core_t1]) * 100, na.rm = TRUE)
min_lp <- min(plot_df_t1$lower, na.rm = TRUE)
max_lp <- max(plot_df_t1$upper, na.rm = TRUE)
pad_lp <- (max_lp - min_lp) * 0.1
if (!is.finite(pad_lp) || pad_lp == 0) {
  pad_lp <- abs(min_lp) * 0.2 + 0.01
}

ggplot(plot_df_t1, aes(x = Coef, y = Variable, color = Scheme, shape = Scheme)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", size = 0.6) +
  geom_point(position = position_dodge(width = 0.6), size = 2.6) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),
                 position = position_dodge(width = 0.6),
                 height = 0.2, linewidth = 0.8) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  labs(x = "Coefficient", y = NULL) +
  scale_color_manual(
    values = c("Original" = "#28A745", "No Tightness" = "#6C757D", "No Tightness + Log-Pop" = "#F24236"),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_shape_manual(
    values = c("Original" = 16, "No Tightness" = 15, "No Tightness + Log-Pop" = 17),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(min_lp - pad_lp, max_lp + pad_lp),
    breaks = pretty(c(min_lp - pad_lp, max_lp + pad_lp), n = 4)
  )
```

Median absolute change across coefficients in Figure 4: `r sprintf('%.0f%%', logpop_t1_median)`.

### Log-Population Weights (Table 2, Column 4) {.unnumbered}

We repeat the same exercise for the Table 2 baseline (column 4). Coefficient magnitudes again attenuate under log(population) weights (see Figure 5).

```{r}
#| label: fig-logpop-compact-t2
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Coefficient sensitivity after removing tightness using log-population weights (Table 2, Col. 4)"
#| fig-cap-location: top
#| fig-pos: "H"
#| fig-width: 6
#| fig-height: 4
# Rebuild z-scored growth dataset with raw log(pop) for weights
data_t2_logpop <- data_ai_2017_2022 %>%
  filter(emp != 0) %>%
  drop_na(share_bac14) %>%
  mutate(
    logpop_raw = logpop14,
    share_bac14 = scale(share_bac14),
    share_black14 = scale(share_black14),
    share_poverty14 = scale(share_poverty14),
    logpop14 = scale(logpop14),
    hpi_ch14 = scale(hpi_ch14),
    logincome14 = scale(logincome14),
    tightness14 = scale(tightness14),
    pat_intensity14 = scale(pat_intensity14),
    patai_intensity14 = scale(patai_intensity14),
    degshare14 = scale(degshare14),
    stemshare14 = scale(stemshare14),
    large_firms14 = scale(large_firms14),
    information_intensity14 = scale(information_intensity14),
    manuf_intensity14 = scale(manuf_intensity14),
    TurnOvrS14 = scale(TurnOvrS14),
    unrate14 = scale(unrate14)
  ) %>%
  mutate(dai_intensity9 = dai_intensity9 * 100) %>%
  filter(dai_intensity9 > -5, dai_intensity9 < 10) %>%
  drop_na(share_bac14, share_black14, share_poverty14, logpop14, hpi_ch14, logincome14,
          tightness14, pat_intensity14, patai_intensity14, degshare14, stemshare14,
          large_firms14, information_intensity14, manuf_intensity14, TurnOvrS14)

est_all_t2_lp <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + tightness14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness_lp <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~lads14
)
est_all_t2_no_tightness_logpop <- fixest::feols(
  "dai_intensity9 ~ share_bac14 + share_black14 + share_poverty14 + gpop + hpi_ch14 + logincome14 + pat_intensity14 + patai_intensity14 + degshare14 + stemshare14 + large_firms14 + information_intensity14 + manuf_intensity14 + TurnOvrS14" %>% as.formula(),
  data_t2_logpop,
  cluster = "COUNTY_FIPS",
  weights = ~logpop_raw
)
plot_df_t2 <- bind_rows(
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_lp)[vars_core_t2], SE = se(est_all_t2_lp)[vars_core_t2], Scheme = "Original"),
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_no_tightness_lp)[vars_core_t2], SE = se(est_all_t2_no_tightness_lp)[vars_core_t2], Scheme = "No Tightness"),
  data.frame(Variable = labels_core_t2, Coef = coef(est_all_t2_no_tightness_logpop)[vars_core_t2], SE = se(est_all_t2_no_tightness_logpop)[vars_core_t2], Scheme = "No Tightness + Log-Pop")
) %>%
  mutate(
    lower = Coef - 1.96 * SE,
    upper = Coef + 1.96 * SE,
    Variable = factor(Variable, levels = rev(labels_core_t2)),
    Scheme = factor(Scheme, levels = c("Original", "No Tightness", "No Tightness + Log-Pop"))
  )
logpop_t2_median <- median(abs((coef(est_all_t2_no_tightness_logpop)[vars_core_t2] - coef(est_all_t2_lp)[vars_core_t2]) / coef(est_all_t2_lp)[vars_core_t2]) * 100, na.rm = TRUE)
min_lp <- min(plot_df_t2$lower, na.rm = TRUE)
max_lp <- max(plot_df_t2$upper, na.rm = TRUE)
pad_lp <- (max_lp - min_lp) * 0.1
if (!is.finite(pad_lp) || pad_lp == 0) {
  pad_lp <- abs(min_lp) * 0.2 + 0.01
}

ggplot(plot_df_t2, aes(x = Coef, y = Variable, color = Scheme, shape = Scheme)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", size = 0.6) +
  geom_point(position = position_dodge(width = 0.6), size = 2.6) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),
                 position = position_dodge(width = 0.6),
                 height = 0.2, linewidth = 0.8) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  labs(x = "Coefficient", y = NULL) +
  scale_color_manual(
    values = c("Original" = "#28A745", "No Tightness" = "#6C757D", "No Tightness + Log-Pop" = "#F24236"),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_shape_manual(
    values = c("Original" = 16, "No Tightness" = 15, "No Tightness + Log-Pop" = 17),
    breaks = c("Original", "No Tightness", "No Tightness + Log-Pop"),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(min_lp - pad_lp, max_lp + pad_lp),
    breaks = pretty(c(min_lp - pad_lp, max_lp + pad_lp), n = 4)
  )
```

Median absolute change across coefficients in Figure 5: `r sprintf('%.0f%%', logpop_t2_median)`.


